### 2015-04-15 paper/frontiers.tex
Added Frontiers LaTeX template

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% This is just an example/guide for you to refer to when submitting manuscripts to Frontiers, it is not mandatory to use frontiers.cls nor frontiers.tex  %
% This will only generate the Manuscript, the final article will be typeset by Frontier after acceptance.                                                 %
%                                                                                                                                                         %
% When submitting your files, remember to upload this *tex file, the pdf generated with it, the *bib file (if bibliography is not within the *tex) and all the figures.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%% Version 3.0 Generated 2014/12/19 %%%
%%% You will need to have the following packages installed: datetime, fmtcount, etoolbox, fcprefix, which are normally inlcuded in WinEdt. %%%
%%% In http://www.ctan.org/ you can find the packages and how to install them, if necessary. %%%

\documentclass{frontiersSCNS} % for Science, Engineering and Humanities and Social Sciences articles
%\documentclass{frontiersHLTH} % for Health articles
%\documentclass{frontiersFPHY} % for Physics articles

%\setcitestyle{square}
\usepackage{url,lineno}
\linenumbers

% Leave a blank line between paragraphs instead of using \\

\def\keyFont{\fontsize{8}{11}\helveticabold }
\def\firstAuthorLast{Sample {et~al.}} %use et al only if is more than 1 author
\def\Authors{First Author\,$^{1,*}$, Co-Author\,$^{2}$ and Co-Author\,$^2$}
% Affiliations should be keyed to the author's name with superscript numbers and be listed as follows: Laboratory, Institute, Department, Organization, City, State abbreviation (USA, Canada, Australia), and Country (without detailed address information such as city zip codes or street names).
% If one of the authors has a change of address, list the new address below the correspondence details using a superscript symbol and use the same symbol to indicate the author in the author list.
\def\Address{$^{1}$Laboratory X, Institute X, Department X, Organization X, City X , State XX (only USA, Canada and Australia), Country X \\
$^{2}$Laboratory X, Institute X, Department X, Organization X, City X , State XX (only USA, Canada and Australia), Country X  }
% The Corresponding Author should be marked with an asterisk
% Provide the exact contact address (this time including street name and city zip code) and email of the corresponding author
\def\corrAuthor{corresponding Author}
\def\corrAddress{Laboratory X, Institute X, Department X, Organization X, Street X, City X , State XX (only USA, Canada and Australia), Zip Code, X Country X}
\def\corrEmail{email@uni.edu}

\begin{document}
\onecolumn
\firstpage{1}

\title[Running Title]{Article Title}
\author[\firstAuthorLast ]{\Authors}
\address{}
\correspondance{}
\extraAuth{}% If there are more than 1 corresponding author, comment this line and uncomment the next one.
%\extraAuth{corresponding Author2 \\ Laboratory X2, Institute X2, Department X2, Organization X2, Street X2, City X2 , State XX2 (only USA, Canada and Australia), Zip Code2, X2 Country X2, email2@uni2.edu}
\topic{}% If your article is part of a Research Topic, please indicate here which.

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% The sections below are for reference only.
%%%
%%% For Original Research Articles, Clinical Trial Articles, and Technology Reports the section headings should be those appropriate for your field and the research itself. It is recommended to organize your manuscript in the
%%% following sections or their equivalents for your field:
%%% Abstract, Introduction, Material and Methods, Results, and Discussion.
%%% Please note that the Material and Methods section can be placed in any of the following ways: before Results, before Discussion or after Discussion.
%%%
%%%For information about Clinical Trial Registration, please go to http://www.frontiersin.org/about/AuthorGuidelines#ClinicalTrialRegistration
%%%
%%% For Clinical Case Studies the following sections are mandatory: Abstract, Introduction, Background, Discussion, and Concluding Remarks.
%%%
%%% For all other article types there are no mandatory sections.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{abstract}

%%% Leave the Abstract empty if your article falls under any of the following categories: Editorial Book Review, Commentary, Field Grand Challenge, Opinion or specialty Grand Challenge.
\section{}
%As a primary goal, the abstract should render the general significance and conceptual advance of the work clearly accessible to a broad readership. References should not be cited in the abstract.
Refer to \url{http://www.frontiersin.org/about/AuthorGuidelines} \\ or \textbf{Table\ref{Tab:01}} for abstract requirement and length according to article type.

\tiny
 \keyFont{ \section{Keywords:} Text Text Text Text Text Text Text Text } %All article types: you may provide up to 8 keywords; at least 5 are mandatory.
\end{abstract}

\section{Introduction}

% For Original Research Articles, Clinical Trial Articles, and Technology Reports the introduction should be succinct, with no subheadings.
%
% For Clinical Case Studies the Introduction should include symptoms at presentation, physical exams and lab results.
%
Text Text Text Text Text Text  Text Text Text Text Text Text Text Text Text  Text Text Text Text Text Text. Text Text Text Text Text Text  Text Text Text Text Text Text Text Text Text  Text Text Text Text Text Text. Text Text Text Text Text Text  Text Text Text Text Text Text Text Text Text  Text Text Text Text Text Text.Text Text Text Text Text Text  Text Text Text Text Text Text Text Text Text  Text Text Text Text Text Text.

%\begin{methods}
\section{Material \& Methods}

Text Text Text Text Text Text  Text Text Text Text Text Text Text Text Text  Text Text Text Text Text Text Text Text Text Text  Text Text Text Text Text Text  Text Text.  \cite{Neuro2013} might want to know about  text text text text Text Text Text Text  Text Text Text Text Text Text  Text Text. \citep{Gene2012} might want to know about  text text text text
Text Text Text Text Text Text  Text Text Text Text Text Text Text Text Text  Text Text Text Text Text Text Text Text Text Text  Text Text Text Text Text Text  Text Text.  \cite{Neurobot2013} might want to know about  text text text text

\begin{table}[!t]
\textbf{\refstepcounter{table}\label{Tab:01} Table \arabic{table}.}{ Maximum size of the Manuscript }

\processtable{ }
{\begin{tabular}{lllll}\toprule
 & Abstract max. legth (incl. spaces) & Figures or tables & Manuscript max. length & Final PDF length\\\midrule
Clinical Case Study & & & &\\
Clinical Trial & & & &\\
Hypothesis and Theory & & & &\\
Methods & 2000 characters  & 15 & 12000 words & 12 pages\\
Original Research & & & &\\
Review & & & &\\
Technology Report & & & &\\
Focused Review & 2000 characters & 5 & 5000 words & 5 pages\\
CPC &  1250 characters& 6 & 2500 words & 4 pages\\
Perspective & 1250 characters & 2 & 3000 words & 3 pages\\
Mini Review & & & &\\
Classification & 1250 characters & 10 & 2000 words & 12 pages\\
Editorial & none & none & 1000 words & 1 page \\
Book review & & & &\\
Frontiers Commentary & none & 1 & 1000 words & 1 page\\
General Commentary & & & &\\
Field Grand Challenge & & & &\\
Opinion & none & 1 & 2000 words & 2 pages\\
Specialty Grand Challenge& & & &\\\botrule
\end{tabular}}{}
\end{table}

Please note that very large tables (covering several pages) cannot be included in the final PDF for reasons of space. These tables will be published as supplementary material on the online article abstract page at the time of acceptance. The author will notified during the typesetting of the final article if this is the case. A link in the final PDF will direct to the online material.

\subsection{Original Research Articles, Clinical Trial Articles, and Technology Reports}

For Original Research Articles, Clinical Trial Articles, and Technology Reports the section headings should be those appropriate for your field and the research itself. It is recommended to organize your manuscript in the following sections or their equivalents for your field:

\begin{itemize}
%for bulleted list, use itemize
\item Introduction: Succinct, with no subheadings.
\item Materials and Methods: This section may be divided by subheadings. This section should contain sufficient detail so that when read in conjunction with cited references, all procedures can be repeated.
\item Results: This section may be divided by subheadings. Footnotes should not be used and have to be transferred into the main text.
\item Discussion: This section may be divided by subheadings. Discussions should cover the key findings of the study: discuss any prior art related to the subject so to place the novelty of the discovery in the appropriate context; discuss the potential short-comings and limitations on their interpretations; discuss their integration into the current understanding of the problem and how this advances the current views; speculate on the future direction of the research and freely postulate theories that could be tested in the future.
\end{itemize}

Please note that the Material and Methods section can be placed in any of the following ways: before Results, before Discussion or after Discussion.

\subsection{Clinical Case Studies}

For Clinical Case Studies the following sections are mandatory:

\begin{itemize}
%for bulleted list, use itemize
\item Introduction: Include symptoms at presentation, physical exams and lab results.
\item Background: This section may be divided by subheadings. Include history and review of similar cases.
\item Results: This section may be divided by subheadings. Include diagnosis and treatment.
\item Concluding Remarks
\end{itemize}

%\end{methods}

\section{Results}

Frontiers requires figures to be submitted individually, in the same order as they are referred to in the manuscript. Figures will then be automatically embedded at the bottom of the submitted manuscript. Kindly ensure that each table and figure is mentioned in the text and in numerical order. Permission must be obtained for use of copyrighted material from other sources (including the web). Please note that it is compulsory to follow figure instructions. Figures which are not according to the guidelines will cause substantial delay during the production process.

\begin{table}[!t]
\textbf{\refstepcounter{table}\label{Tab:02} Table \arabic{table}.}{ Resolution Requirements for the figures}

\processtable{}
{\begin{tabular}{lllll}\toprule
Image Type & Description & Format & Color Mode & Resolution\\\midrule
Line Art & An image composed of lines and text,  & TIFF, JPEG & RGB, Bitmap & 900 - 1200 dpi\\
           & which does not contain tonal or shaded areas.& & &\\
           Halftone & A continuous tone photograph, which contains no text. & TIFF, EPS, JPEG & RGB, Grayscale & 300 dpi\\
Combination & Image contains halftone + text or line art elements. & TIFF, JPEG & RGB,Grayscale & 600 - 900 dpi\\\botrule
\end{tabular}}{}
\end{table}

\begin{equation}
\sum x+ y =Z\label{eq:01}
\end{equation}

\textbf{Table\ref{Tab:02}} shows the resolution requirements for the figures. The figures must be legible:
\begin{enumerate}
\item The smallest visible text is no less than 8 points in height, when viewed at actual size.
\item Solid lines are not broken up.
\item Image areas are not pixelated or stair stepped.
\item Text is legible and of high quality.
\item Any lines in the graphic are no smaller than 2 points width.
\item The actual size of the figure must be of at least 8.5 cm.
\end{enumerate}

\section{Discussion}

Text Text Text Text Text Text  Text Text Text Text Text Text Text Text Text  Text Text Text Text Text Text Text Text Text Text.
Additional Requirements:
\subsection{Corrections}

If you need to communicate important changes to a published article please submit a General Commentary. Submit the article with the title “Corrigendum: Original Title of Article”.

\subsection{Commentaries on Articles}

At the beginning of your manuscript provide the citation of the article commented on.

\subsection{Focused Reviews}

For Tier 2 invited Focused Reviews the sections Introduction, Material and Methods, Results, and Discussion are recommended. In addition the authors must submit a short biography of the corresponding author(s). This short biography has a maximum of 600 characters, including spaces.

A picture (5 x 5 cm, in *.tif or *.jpg, min 300 dpi) must be submitted along with the biography in the manuscript and separately during figure upload.
Focused Reviews highlight and explain key concepts of your work. Please highlight a minimum of four and a maximum of ten key concepts in bold in your manuscript and provide the definitions/explanations at the end of your manuscript under “Key Concepts”. Each definition has a maximum of 400 characters, including spaces.

\subsection{Human Search and Animal Research}

All experiments on live vertebrates or higher invertebrates must be performed in accordance with relevant institutional and national guidelines and regulations. In the manuscript, authors must identify the committee approving the experiments and must confirm that all experiments conform to the relevant regulatory standards. For manuscripts reporting experiments on human subjects, authors must identify the committee approving the experiments and must also include a statement confirming that informed consent was obtained from all subjects. In Original Research Articles and Clinical Trial Articles these statements should appear in the Materials and Methods section.

\subsection{Clinical Trial Registration}

Clinical trials should be registered in a public trials registry in order to become the object of a publication at Frontiers. Trials must be registered at or before the start of patient enrollment. A clinical trial is defined as"any research study that prospectively assigns human participants or groups of humans to one or more health-related interventions to evaluate the effects on health outcomes."(\url{www.who.int/ictrp/en}). A list of acceptable registries can be found at \url{www.who.int/ictrp/en and www.icmje.org}.

\subsection{Inclusion of Proteomics Data}

Authors should provide relevant information relating to how the peptide/protein matches were undertaken, including methods used to process and analyze data, false discovery rates (FDR) for large-scale studies and threshold or cut-off rates for peptide and protein matches. Further information could include software used, mass spectrometer type, sequence database and version, number of sequences in database, processing methods, mass tolerances used for matching, variable/fixed modifications, allowable missed cleavages, etc.

Authors should provide as supplementary material information used to identify proteins and/or peptides. This should include information such as accession numbers, observed mass (m/z), charge, delta mass, matched mass, peptide/protein scores, peptide modification, miscleavages, peptide sequence, match rank, matched species (for cross species matching), number of peptide matches, ambiguous protein/peptide matches should be indicated, etc.
For quantitative proteomics analyses authors should provide information to justify the statistical significance including biological replicates, statistical methods, estimates of uncertainty and the methods used for calculating error.

For peptide matches with biologically relevant post-translational modifications (PTM) and for any protein match that has occurred using a single mass spectrum, authors should include this information as raw data, annotated spectra or submit data to an online repository (recommended option).
Authors are encouraged to submit raw or matched data and 2-DE images to public proteomics repositories. Submission codes and/or links to data should be provided within the manuscript.

\subsection{Data Sharing}

Frontiers supports the policy of data sharing, and authors are advised to make freely available any materials and information described in their article, and any data relevant to the article (while not compromising confidentiality in the context of human-subject research) that may be reasonably requested by others for the purpose of academic and non-commercial research. In regards to deposition of data and data sharing through databases, Frontiers urges authors to comply with the current best practices within their discipline.

\section*{Disclosure/Conflict-of-Interest Statement}
%Frontiers follows the recommendations by the International Committee of Medical Journal Editors (http://www.icmje.org/ethical_4conflicts.html) which require that all financial, commercial or other relationships that might be perceived by the academic community as representing a potential conflict of interest must be disclosed. If no such relationship exists, authors will be asked to declare that the research was conducted in the absence of any commercial or financial relationships that could be construed as a potential conflict of interest. When disclosing the potential conflict of interest, the authors need to address the following points:
%•	Did you or your institution at any time receive payment or services from a third party for any aspect of the submitted work?
%•	Please declare financial relationships with entities that could be perceived to influence, or that give the appearance of potentially influencing, what you wrote in the submitted work.
%•	Please declare patents and copyrights, whether pending, issued, licensed and/or receiving royalties relevant to the work.
%•	Please state other relationships or activities that readers could perceive to have influenced, or that give the appearance of potentially influencing, what you wrote in the submitted work.

The authors declare that the research was conducted in the absence of any commercial or financial relationships that could be construed as a potential conflict of interest.

\section*{Author Contributions}
%When determining authorship the following criteria should be observed:
%•	Substantial contributions to the conception or design of the work; or the acquisition, analysis, or interpretation of data for the work; AND
%•	Drafting the work or revising it critically for important intellectual content; AND
%•	Final approval of the version to be published ; AND
%•	Agreement to be accountable for all aspects of the work in ensuring that questions related to the accuracy or integrity of any part of the work are appropriately investigated and resolved.
%Contributors who meet fewer than all 4 of the above criteria for authorship should not be listed as authors, but they should be acknowledged. (http://www.icmje.org/roles_a.html)

The statement about the authors and contributors can be up to several sentences long, describing the tasks of individual authors referred to by their initials and should be included at the end of the manuscript before the References section.

\section*{Acknowledgments}
Text Text Text Text Text Text  Text Text Text Text Text Text Text Text  Text Text Text Text Text Text Text Text Text  Text Text Text. Text Text Text Text Text Text  Text Text Text Text Text Text Text Text  Text Text Text Text Text Text Text Text Text  Text Text Text.

\paragraph{Funding\textcolon} Text Text Text Text Text Text  Text Text.

\section*{Supplemental Data}
Supplementary Material should be uploaded separately on submission, if there are Supplementary Figures, please include the caption in the same file as the figure. LaTeX Supplementary Material templates can be found in the Frontiers LaTeX folder

Text Text Text Text Text Text  Text Text Text Text Text Text Text Text  Text Text Text Text Text Text Text Text Text  Text Text Text.

%\bibliographystyle{frontiersinSCNS} % for Science, Engineering and Humanities and Social Sciences articles, for Humanities and Social Sciences articles please include page numbers in the in-text citations
\bibliographystyle{frontiersinHLTH&FPHY} % for Health and Physics articles
\bibliography{test}

%%% Upload the *bib file along with the *tex file and PDF on submission if the bibliography is not in the main *tex file

\section*{Figures}

%%% Use this if adding the figures directly in the mansucript, if so, please remember to also upload the files when submitting your article
%%% There is no need for adding the file termination, as long as you indicate where the file is saved. In the examples below the files (logo1.jpg and logo2.eps) are in the Frontiers LaTeX folder
%%% If using *.tif files convert them to .jpg or .png

\begin{figure}[h!]
\begin{center}
\includegraphics[width=10cm]{logo1}% This is a *.jpg file
\end{center}
 \textbf{\refstepcounter{figure}\label{fig:01} Figure \arabic{figure}.}{ Enter the caption for your figure here.  Repeat as  necessary for each of your figures }
\end{figure}

%\begin{figure}
%\begin{center}
%\includegraphics[width=10cm]{logo2}% This is an *.eps file
%\end{center}
%\textbf{\refstepcounter{figure}\label{fig:02} Figure \arabic{figure}.}{ Enter the caption for your figure here.  Repeat as  necessary for each of your figures }
%\end{figure}

%%% If you don't add the figures in the LaTeX files, please upload them when submitting the article.

%%% Frontiers will add the figures at the end of the provisional pdf automatically %%%

%%% The use of LaTeX coding to draw Diagrams/Figures/Structures should be avoided. They should be external callouts including graphics.

\end{document}

### 2015-04-15 paper/frontiers_SupplementaryMaterial.tex
Added Frontiers LaTeX template

--- 2015-04-15 paper/frontiers.tex
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% This is just an example/guide for you to refer to when submitting manuscripts to Frontiers, it is not mandatory to use frontiers.cls nor frontiers.tex  %
-% This will only generate the Manuscript, the final article will be typeset by Frontier after acceptance.                                                 %
-%                                                                                                                                                         %
-% When submitting your files, remember to upload this *tex file, the pdf generated with it, the *bib file (if bibliography is not within the *tex) and all the figures.
+% This is just an example/guide for you to refer to when producing your supplementary material for your Frontiers article.                                 %
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-%%% Version 3.0 Generated 2014/12/19 %%%
+%%% Version 2.0 Generated 2014/01/08 %%%
 %%% You will need to have the following packages installed: datetime, fmtcount, etoolbox, fcprefix, which are normally inlcuded in WinEdt. %%%
@@
 
-\documentclass{frontiersSCNS} % for Science, Engineering and Humanities and Social Sciences articles
-%\documentclass{frontiersHLTH} % for Health articles
-%\documentclass{frontiersFPHY} % for Physics articles
+\documentclass{frontiers_suppmat} % for all articles
 
-%\setcitestyle{square}
-\usepackage{url,lineno}
-\linenumbers
+\usepackage{url}
 
-% Leave a blank line between paragraphs instead of using \\
+% Leave a blank line between paragraphs in stead of using \\
 
+\def\articleType{Supplementary Material}
 \def\keyFont{\fontsize{8}{11}\helveticabold }
-\def\firstAuthorLast{Sample {et~al.}} %use et al only if is more than 1 author
+\def\firstAuthorLast{Frontiers} 
 \def\Authors{First Author\,$^{1,*}$, Co-Author\,$^{2}$ and Co-Author\,$^2$}
@@
 
+% \color{FrontiersColor} Is the color used in the Journal name, in the title, and the names of the sections.
+
 \begin{document}
@@
 
-\title[Running Title]{Article Title}
+\title[Supplementary Material]{{\helveticaitalic{Supplementary Material}}:\\ \helvetica{ Article Title}}
 \author[\firstAuthorLast ]{\Authors}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%% The sections below are for reference only.
-%%%
-%%% For Original Research Articles, Clinical Trial Articles, and Technology Reports the section headings should be those appropriate for your field and the research itself.
-It is recommended to organize your manuscript in the
-%%% following sections or their equivalents for your field:
-%%% Abstract, Introduction, Material and Methods, Results, and Discussion.
-%%% Please note that the Material and Methods section can be placed in any of the following ways: before Results, before Discussion or after Discussion.
-%%%
-%%%For information about Clinical Trial Registration, please go to http://www.frontiersin.org/about/AuthorGuidelines#ClinicalTrialRegistration
-%%%
-%%% For Clinical Case Studies the following sections are mandatory: Abstract, Introduction, Background, Discussion, and Concluding Remarks.
-%%%
-%%% For all other article types there are no mandatory sections.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Supplementary Data}
 
-\begin{abstract}
-
-%%% Leave the Abstract empty if your article falls under any of the following categories: Editorial Book Review, Commentary, Field Grand Challenge, Opinion or specialty Grand Challenge.
-\section{}
-%As a primary goal, the abstract should render the general significance and conceptual advance of the work clearly accessible to a broad readership. References should not be cited in the abstract.
-Refer to \url{http://www.frontiersin.org/about/AuthorGuidelines} \\ or \textbf{Table\ref{Tab:01}} for abstract requirement and length according to article type.
-
-\tiny
- \keyFont{ \section{Keywords:} Text Text Text Text Text Text Text Text } %All article types: you may provide up to 8 keywords; at least 5 are mandatory.
-\end{abstract}
-
-\section{Introduction}
-
-% For Original Research Articles, Clinical Trial Articles, and Technology Reports the introduction should be succinct, with no subheadings.
-%
-% For Clinical Case Studies the Introduction should include symptoms at presentation, physical exams and lab results.
 %
@@
 
-%\begin{methods}
-\section{Material \& Methods}
+Text Text Text Text Text Text  Text Text Text Text Text Text Text Text Text  Text Text Text Text Text Text.
+Text Text Text Text Text Text  Text Text Text Text Text Text Text Text Text  Text Text Text Text Text Text.
+Text Text Text Text Text Text  Text Text Text Text Text Text Text Text Text  Text Text Text Text Text Text.Text Text Text Text Text Text  Text Text Text Text Text Text Text Text Text  Text Text Text Text Text Text.
 
-Text Text Text Text Text Text  Text Text Text Text Text Text Text Text Text  Text Text Text Text Text Text Text Text Text Text  Text Text Text Text Text Text  Text Text.
-\cite{Neuro2013} might want to know about  text text text text Text Text Text Text  Text Text Text Text Text Text  Text Text.
-\citep{Gene2012} might want to know about  text text text text
-Text Text Text Text Text Text  Text Text Text Text Text Text Text Text Text  Text Text Text Text Text Text Text Text Text Text  Text Text Text Text Text Text  Text Text.
-\cite{Neurobot2013} might want to know about  text text text text
+\section{Supplementary Tables and Figures}
+
+Text Text Text Text Text Text  Text Text Text Text Text Text Text Text Text  Text Text Text Text Text Text.
+Text Text Text Text Text Text  Text Text Text Text Text Text Text Text Text  Text Text Text Text Text Text.
+Text Text Text Text Text Text  Text Text Text Text Text Text Text Text Text  Text Text Text Text Text Text.Text Text Text Text Text Text  Text Text Text Text Text Text Text Text Text  Text Text Text Text Text Text.
+
+Text Text Text Text Text Text  Text Text Text Text Text Text Text Text Text  Text Text Text Text Text Text.
+Text Text Text Text Text Text  Text Text Text Text Text Text Text Text Text  Text Text Text Text Text Text.
+Text Text Text Text Text Text  Text Text Text Text Text Text Text Text Text  Text Text Text Text Text Text.Text Text Text Text Text Text  Text Text Text Text Text Text Text Text Text  Text Text Text Text Text Text.
 
 \begin{table}[!t]
-\textbf{\refstepcounter{table}\label{Tab:01} Table \arabic{table}.}{ Maximum size of the Manuscript }
+\textbf{\refstepcounter{table}\label{Tab:01} Supplementary Table \arabic{table}.}{ Enter the caption for your table here.  Repeat as  necessary for each of your tables }
 
@@
 
-Please note that very large tables (covering several pages) cannot be included in the final PDF for reasons of space.
-These tables will be published as supplementary material on the online article abstract page at the time of acceptance.
-The author will notified during the typesetting of the final article if this is the case.
-A link in the final PDF will direct to the online material.
-
-\subsection{Original Research Articles, Clinical Trial Articles, and Technology Reports}
-
-For Original Research Articles, Clinical Trial Articles, and Technology Reports the section headings should be those appropriate for your field and the research itself.
-It is recommended to organize your manuscript in the following sections or their equivalents for your field:
-
-\begin{itemize}
-%for bulleted list, use itemize
-\item Introduction: Succinct, with no subheadings.
-\item Materials and Methods: This section may be divided by subheadings.
-This section should contain sufficient detail so that when read in conjunction with cited references, all procedures can be repeated.
-\item Results: This section may be divided by subheadings. Footnotes should not be used and have to be transferred into the main text.
-\item Discussion: This section may be divided by subheadings.
-Discussions should cover the key findings of the study: discuss any prior art related to the subject so to place the novelty of the discovery in the appropriate context; discuss the potential short-comings and limitations on their interpretations; discuss their integration into the current understanding of the problem and how this advances the current views; speculate on the future direction of the research and freely postulate theories that could be tested in the future.
-\end{itemize}
-
-Please note that the Material and Methods section can be placed in any of the following ways: before Results, before Discussion or after Discussion.
-
-\subsection{Clinical Case Studies}
-
-For Clinical Case Studies the following sections are mandatory:
-
-\begin{itemize}
-%for bulleted list, use itemize
-\item Introduction: Include symptoms at presentation, physical exams and lab results.
-\item Background: This section may be divided by subheadings. Include history and review of similar cases.
-\item Results: This section may be divided by subheadings. Include diagnosis and treatment.
-\item Concluding Remarks
-\end{itemize}
-
-%\end{methods}
-
-\section{Results}
-
-Frontiers requires figures to be submitted individually, in the same order as they are referred to in the manuscript.
-Figures will then be automatically embedded at the bottom of the submitted manuscript.
-Kindly ensure that each table and figure is mentioned in the text and in numerical order.
-Permission must be obtained for use of copyrighted material from other sources (including the web).
-Please note that it is compulsory to follow figure instructions.
-Figures which are not according to the guidelines will cause substantial delay during the production process.
-
-\begin{table}[!t]
-\textbf{\refstepcounter{table}\label{Tab:02} Table \arabic{table}.}{ Resolution Requirements for the figures}
-
-\processtable{}
-{\begin{tabular}{lllll}\toprule
-Image Type & Description & Format & Color Mode & Resolution\\\midrule
-Line Art & An image composed of lines and text,  & TIFF, JPEG & RGB, Bitmap & 900 - 1200 dpi\\
-           & which does not contain tonal or shaded areas.& & &\\
-           Halftone & A continuous tone photograph, which contains no text. & TIFF, EPS, JPEG & RGB, Grayscale & 300 dpi\\
-Combination & Image contains halftone + text or line art elements. & TIFF, JPEG & RGB,Grayscale & 600 - 900 dpi\\\botrule
-\end{tabular}}{}
-\end{table}
-
-\begin{equation}
-\sum x+ y =Z\label{eq:01}
-\end{equation}
-
-\textbf{Table\ref{Tab:02}} shows the resolution requirements for the figures. The figures must be legible:
-\begin{enumerate}
-\item The smallest visible text is no less than 8 points in height, when viewed at actual size.
-\item Solid lines are not broken up.
-\item Image areas are not pixelated or stair stepped.
-\item Text is legible and of high quality.
-\item Any lines in the graphic are no smaller than 2 points width.
-\item The actual size of the figure must be of at least 8.5 cm.
-\end{enumerate}
-
-\section{Discussion}
-
-Text Text Text Text Text Text  Text Text Text Text Text Text Text Text Text  Text Text Text Text Text Text Text Text Text Text.
-Additional Requirements:
-\subsection{Corrections}
-
-If you need to communicate important changes to a published article please submit a General Commentary. Submit the article with the title “Corrigendum: Original Title of Article”.
-
-\subsection{Commentaries on Articles}
-
-At the beginning of your manuscript provide the citation of the article commented on.
-
-\subsection{Focused Reviews}
-
-For Tier 2 invited Focused Reviews the sections Introduction, Material and Methods, Results, and Discussion are recommended.
-In addition the authors must submit a short biography of the corresponding author(s).
-This short biography has a maximum of 600 characters, including spaces.
-
-A picture (5 x 5 cm, in *.tif or *.jpg, min 300 dpi) must be submitted along with the biography in the manuscript and separately during figure upload.
-Focused Reviews highlight and explain key concepts of your work.
-Please highlight a minimum of four and a maximum of ten key concepts in bold in your manuscript and provide the definitions/explanations at the end of your manuscript under “Key Concepts”.
-Each definition has a maximum of 400 characters, including spaces.
-
-\subsection{Human Search and Animal Research}
-
-All experiments on live vertebrates or higher invertebrates must be performed in accordance with relevant institutional and national guidelines and regulations.
-In the manuscript, authors must identify the committee approving the experiments and must confirm that all experiments conform to the relevant regulatory standards.
-For manuscripts reporting experiments on human subjects, authors must identify the committee approving the experiments and must also include a statement confirming that informed consent was obtained from all subjects.
-In Original Research Articles and Clinical Trial Articles these statements should appear in the Materials and Methods section.
-
-\subsection{Clinical Trial Registration}
-
-Clinical trials should be registered in a public trials registry in order to become the object of a publication at Frontiers.
-Trials must be registered at or before the start of patient enrollment.
-A clinical trial is defined as"any research study that prospectively assigns human participants or groups of humans to one or more health-related interventions to evaluate the effects on health outcomes."(\url{www.who.int/ictrp/en}).
-A list of acceptable registries can be found at \url{www.who.int/ictrp/en and www.icmje.org}.
-
-\subsection{Inclusion of Proteomics Data}
-
-Authors should provide relevant information relating to how the peptide/protein matches were undertaken, including methods used to process and analyze data, false discovery rates (FDR) for large-scale studies and threshold or cut-off rates for peptide and protein matches.
-Further information could include software used, mass spectrometer type, sequence database and version, number of sequences in database, processing methods, mass tolerances used for matching, variable/fixed modifications, allowable missed cleavages, etc.
-
-Authors should provide as supplementary material information used to identify proteins and/or peptides.
-This should include information such as accession numbers, observed mass (m/z), charge, delta mass, matched mass, peptide/protein scores, peptide modification, miscleavages, peptide sequence, match rank, matched species (for cross species matching), number of peptide matches, ambiguous protein/peptide matches should be indicated, etc.
-For quantitative proteomics analyses authors should provide information to justify the statistical significance including biological replicates, statistical methods, estimates of uncertainty and the methods used for calculating error.
-
-For peptide matches with biologically relevant post-translational modifications (PTM) and for any protein match that has occurred using a single mass spectrum, authors should include this information as raw data, annotated spectra or submit data to an online repository (recommended option).
-Authors are encouraged to submit raw or matched data and 2-DE images to public proteomics repositories. Submission codes and/or links to data should be provided within the manuscript.
-
-\subsection{Data Sharing}
-
-Frontiers supports the policy of data sharing, and authors are advised to make freely available any materials and information described in their article, and any data relevant to the article (while not compromising confidentiality in the context of human-subject research) that may be reasonably requested by others for the purpose of academic and non-commercial research.
-In regards to deposition of data and data sharing through databases, Frontiers urges authors to comply with the current best practices within their discipline.
-
-\section*{Disclosure/Conflict-of-Interest Statement}
-%Frontiers follows the recommendations by the International Committee of Medical Journal Editors (http://www.icmje.org/ethical_4conflicts.html) which require that all financial, commercial or other relationships that might be perceived by the academic community as representing a potential conflict of interest must be disclosed.
-If no such relationship exists, authors will be asked to declare that the research was conducted in the absence of any commercial or financial relationships that could be construed as a potential conflict of interest.
-When disclosing the potential conflict of interest, the authors need to address the following points:
-%•	Did you or your institution at any time receive payment or services from a third party for any aspect of the submitted work?
-%•	Please declare financial relationships with entities that could be perceived to influence, or that give the appearance of potentially influencing, what you wrote in the submitted work.
-%•	Please declare patents and copyrights, whether pending, issued, licensed and/or receiving royalties relevant to the work.
-%•	Please state other relationships or activities that readers could perceive to have influenced, or that give the appearance of potentially influencing, what you wrote in the submitted work.
-
-The authors declare that the research was conducted in the absence of any commercial or financial relationships that could be construed as a potential conflict of interest.
-
-\section*{Author Contributions}
-%When determining authorship the following criteria should be observed:
-%•	Substantial contributions to the conception or design of the work; or the acquisition, analysis, or interpretation of data for the work; AND
-%•	Drafting the work or revising it critically for important intellectual content; AND
-%•	Final approval of the version to be published ; AND
-%•	Agreement to be accountable for all aspects of the work in ensuring that questions related to the accuracy or integrity of any part of the work are appropriately investigated and resolved.
-%Contributors who meet fewer than all 4 of the above criteria for authorship should not be listed as authors, but they should be acknowledged. (http://www.icmje.org/roles_a.html)
-
-The statement about the authors and contributors can be up to several sentences long, describing the tasks of individual authors referred to by their initials and should be included at the end of the manuscript before the References section.
-
-\section*{Acknowledgments}
-Text Text Text Text Text Text  Text Text Text Text Text Text Text Text  Text Text Text Text Text Text Text Text Text  Text Text Text.
-Text Text Text Text Text Text  Text Text Text Text Text Text Text Text  Text Text Text Text Text Text Text Text Text  Text Text Text.
-
-\paragraph{Funding\textcolon} Text Text Text Text Text Text  Text Text.
-
-\section*{Supplemental Data}
-Supplementary Material should be uploaded separately on submission, if there are Supplementary Figures, please include the caption in the same file as the figure.
-LaTeX Supplementary Material templates can be found in the Frontiers LaTeX folder
-
-Text Text Text Text Text Text  Text Text Text Text Text Text Text Text  Text Text Text Text Text Text Text Text Text  Text Text Text.
-
-%\bibliographystyle{frontiersinSCNS} % for Science, Engineering and Humanities and Social Sciences articles, for Humanities and Social Sciences articles please include page numbers in the in-text citations
-\bibliographystyle{frontiersinHLTH&FPHY} % for Health and Physics articles
-\bibliography{test}
-
-%%% Upload the *bib file along with the *tex file and PDF on submission if the bibliography is not in the main *tex file
-
-\section*{Figures}
-
-%%% Use this if adding the figures directly in the mansucript, if so, please remember to also upload the files when submitting your article
 %%% There is no need for adding the file termination, as long as you indicate where the file is saved. In the examples below the files (logo1.jpg and logo2.eps) are in the Frontiers LaTeX folder
@@
 
-\begin{figure}[h!]
+\begin{figure}
 \begin{center}
-\includegraphics[width=10cm]{logo1}% This is a *.jpg file
+\includegraphics[width=15cm]{logo1}% This is a *.jpg file
 \end{center}
- \textbf{\refstepcounter{figure}\label{fig:01} Figure \arabic{figure}.}{ Enter the caption for your figure here.  Repeat as  necessary for each of your figures }
+\textbf{\refstepcounter{figure}\label{fig:01} Supplementary Figure \arabic{figure}.}{ Enter the caption for your figure here.  Repeat as  necessary for each of your figures }
 \end{figure}
@@
 %\begin{center}
-%\includegraphics[width=10cm]{logo2}% This is an *.eps file
+%\includegraphics[width=3.5cm]{logo2}% This is an *.eps file
 %\end{center}
-%\textbf{\refstepcounter{figure}\label{fig:02} Figure \arabic{figure}.}{ Enter the caption for your figure here.  Repeat as  necessary for each of your figures }
+% \textbf{\refstepcounter{figure}\label{fig:02} Figure \arabic{figure}.}{ Enter the caption for your figure here.  Repeat as  necessary for each of your figures }
 %\end{figure}
 
-%%% If you don't add the figures in the LaTeX files, please upload them when submitting the article.
-
-%%% Frontiers will add the figures at the end of the provisional pdf automatically %%%
-
-%%% The use of LaTeX coding to draw Diagrams/Figures/Structures should be avoided. They should be external callouts including graphics.
+%\bibliographystyle{frontiersinSCNS&ENG} % for Science and Engineering articles
+%\bibliographystyle{frontiersinHLTH&FPHY} % for Health and Physics articles
+%\bibliography{test}
 

### 2015-04-15 paper/paper.tex
First day of writing
Transferred most of the outline to the LaTeX template,
and started filling in sections.

\documentclass{frontiersSCNS}

\usepackage{url,lineno}
\linenumbers

\def\keyFont{\fontsize{8}{11}\helveticabold }
\def\firstAuthorLast{Bekolay {et~al.}}
\def\Authors{Trevor Bekolay\,$^{1,*}$,
  Terrence C. Stewart\,$^{1}$,
  Eric Hunsberger\,$^1$,
  Andrew Mundy\,$^2$ and
  Chris Eliasmith\,$^1$}
\def\Address{$^{1}$Centre for Theoretical Neuroscience,
  University of Waterloo,
  Waterloo, ON, Canada\\
  $^{2}$ Advanced Processors Technologies Research Group,
  School of Computer Science,
  University of Manchester,
  Manchester, UK}
\def\corrAuthor{Trevor Bekolay}
\def\corrAddress{Centre for Theoretical Neuroscience,
  David R. Cheriton School of Computer Science,
  University of Waterloo,
  200 University Avenue West,
  Waterloo, ON  N2L~3G1, Canada}
\def\corrEmail{tbekolay@uwaterloo.ca}

\begin{document}
\onecolumn
\firstpage{1}

\title[Benchmarking neuromorphic systems with Nengo]{Benchmarking neuromorphic systems with Nengo}
\author[\firstAuthorLast ]{\Authors}
\address{}
\correspondance{}
\extraAuth{}
\topic{Benchmarks and Challenges for Neuromorphic Engineering}

\maketitle

\begin{abstract}

  Abstract

  \tiny
  % 5--8 keywords
  \keyFont{ \section{Keywords:}  }
\end{abstract}

\section{Introduction}

Benchmarking is a notoriously difficult task...

Nengo is a rigorously tested software package
for building and simulating
large-scale neural models
that can perform cognitively relevant tasks.
It provides a high-level API (frontend)
that can express large-scale models concisely
and in a platform-independent manner.
Several Nengo-compatible simulators (backends)
have been developed that can
run Nengo models on diverse platforms,
including neuromorphic hardware.
Nengo's separation between frontend and backend
and rigorous test suite
provide standardized comparisons
between different neuromorphic implementations
that are geared toward (???) functional performance,
rather than artificial metrics
that may or may not contribute to functional performance.

Other software that do similar things:
many neural simulators exist, and have tests,
but don't have the high-level API
that Nengo has.
On the other hand, some simulators
have high-level APIs
(Topographica?) but a) aren't functional
and b) can't use diverse backends.

??? In the subsequent sections,
we detail the architecture of Nengo's
frontend and backend,
and describe what each backend
is required to implement.
We explain Nengo's testing framework,
including descriptions of the testing fixtures
used to collect and visualize benchmarks.
We then list the metrics that will be collected,
and the backends on which we will collect metrics.
Finally, we will show and discuss
the results of collecting those metrics
for each backend.

\section{Background}

There are two key features of Nengo 2.0
that enable rapid benchmarking of neuromorphic systems.
The first is a decoupling of model creation and simulation,
resulting in a platform independent frontend interface
to any backend that implements a certain set of requirements.
The second is a ``fuzzy'' test suite ensuring that
Nengo can be used to create models that solve cognitive tasks.
This test suite makes ample use of test fixtures
to enable data collection while testing on arbitrary backends.

\subsection{Nengo architecture}

Nengo has a strict separation between
the frontend and backend.
The frontend exposes a modelling interface
that uses Python and NumPy \cite{???}
to define models concisely.
Backends are responsible for transforming
those frontend objects into code that
can be run on the target platform.
While each backend must be exposed
through Python, this requirement
does not significantly limit
flexibility in the backend.
A backend can be implemented in C and exposed
through Python bindings,
or can be run as a separate process
managed by the Python backend,
with data transmitted to Python through sockets
or other inter-process communication protocols.

\subsubsection{Frontend interface}

Go over the nengo objects

Unlike other programming models,
it's not like... for sure.
Go over symbolic dists.

Some things are suggestions.
Go over backend hints.

\subsubsection{Backend requirements}

Go over the Simulator object, and required methods.

Go over (briefly) translation of frontend to backend.
Needed: some kind of neuron model; takes current,
produces output (rates, spikes, whatever).
Needed: Ops (look at all ops)

\subsection{Fuzzy testing}

As of version 2.0.1, Nengo's test suite contains 618 tests.
Some test are unit tests though; how many?
In all, ??? can be considered ``functional'' tests,
as they construct a model,
build a simulator object (see previous sec???)
and test that the output of that model
matches the desired output,
to a certain tolerance.

Unlike traditional software testing,
there can be significant variability
in many aspects of a Nengo model.
Many model parameters, for example,
can be randomly generated;
other aspects of a model,
such as injected noise,
are necessarily random.
Noise is a fundamental property
of neuromorphic systems.
The accuracy of any large-scale model
is dependent on many factors,
including the number of neurons used
to implement a particular task.
For this reason,
functional tests can only
ensure that the backend implements
the system described by the frontend
well enough.
Each test must determine what
``well enough'' means for that particular network.
While this introduces some subjectivity
to these benchmarks,
it is nearly impossible to create
completely objective benchmarks.
??? more or remove last bit

Nengo's test suite employs the \texttt{pytest}
testing framework \cite{???}.
??? introduce test fixtures

\subsubsection{Test fixtures}

\paragraph{\texttt{rng} \& \texttt{seed}} to manage random factors

\paragraph{\texttt{Simulator}} to switch backend

\paragraph{\texttt{nl}} to switch neuron type

\paragraph{\texttt{plt}} to save plots

\paragraph{\texttt{analytics}} to save data

\paragraph{\texttt{logger}} to save text

\section{Methods}

\subsection{Metrics collected}

\subsubsection{Compliance}

\subsubsection{Accuracy}

\subsubsection{Speed}

\subsection{Backends tested}

\paragraph{Reference}

\paragraph{Simplified reference}

\paragraph{OpenCL}

\paragraph{SpiNNaker hardware}

\paragraph{Neurogrid simulation}

\section{Results}

\section{Discussion}

\subsection{Data Sharing}

%% Frontiers supports the policy of data sharing, and authors are advised
%% to make freely available any materials and information described in
%% their article, and any data relevant to the article (while not
%% compromising confidentiality in the context of human-subject research)
%% that may be reasonably requested by others for the purpose of academic
%% and non-commercial research. In regards to deposition of data and data
%% sharing through databases, Frontiers urges authors to comply with the
%% current best practices within their discipline.

\section*{Disclosure/Conflict-of-Interest Statement}

%Frontiers follows the recommendations by the International Committee
%of Medical Journal Editors
%(http://www.icmje.org/ethical_4conflicts.html) which require that all
%financial, commercial or other relationships that might be perceived
%by the academic community as representing a potential conflict of
%interest must be disclosed. If no such relationship exists, authors
%will be asked to declare that the research was conducted in the
%absence of any commercial or financial relationships that could be
%construed as a potential conflict of interest. When disclosing the
%potential conflict of interest, the authors need to address the
%following points: • Did you or your institution at any time receive
%payment or services from a third party for any aspect of the
%submitted work?  • Please declare financial relationships with
%entities that could be perceived to influence, or that give the
%appearance of potentially influencing, what you wrote in the
%submitted work.  • Please declare patents and copyrights, whether
%pending, issued, licensed and/or receiving royalties relevant to the
%work.  • Please state other relationships or activities that readers
%could perceive to have influenced, or that give the appearance of
%potentially influencing, what you wrote in the submitted work.

%% The authors declare that the research was conducted in the absence of
%% any commercial or financial relationships that could be construed as a
%% potential conflict of interest.

\section*{Author Contributions}

%When determining authorship the following criteria should be observed:
%• Substantial contributions to the conception or design of the work; or the acquisition, analysis, or interpretation of data for the work; AND
%• Drafting the work or revising it critically for important intellectual content; AND
%• Final approval of the version to be published ; AND
%• Agreement to be accountable for all aspects of the work in ensuring that questions related to the accuracy or integrity of any part of the work are appropriately investigated and resolved.
%Contributors who meet fewer than all 4 of the above criteria for authorship should not be listed as authors, but they should be acknowledged. (http://www.icmje.org/roles_a.html)

%% The statement about the authors and contributors can be up to several
%% sentences long, describing the tasks of individual authors referred to
%% by their initials and should be included at the end of the manuscript
%% before the References section.

\section*{Acknowledgments}
%% Acknowledgments

\paragraph{Funding\textcolon} %% Funding

\section*{Supplemental Data}
%% Supplementary Material should be uploaded separately on submission, if
%% there are Supplementary Figures, please include the caption in the
%% same file as the figure. LaTeX Supplementary Material templates can be
%% found in the Frontiers LaTeX folder

\bibliographystyle{frontiersinSCNS}
\bibliography{paper}

\section*{Figures}

\end{document}

%% \begin{table}[!t]
%% \textbf{\refstepcounter{table}\label{Tab:01} Table \arabic{table}.}{
%%   Maximum size of the Manuscript }

%% \processtable{ }
%% {\begin{tabular}{lllll}\toprule
%%  & Abstract max. legth (incl. spaces) & Figures or tables & Manuscript max. length & Final PDF length\\\midrule
%%  Clinical Case Study & & & &\\
%%  Clinical Trial & & & &\\
%%  Hypothesis and Theory & & & &\\
%%  Methods & 2000 characters  & 15 & 12000 words & 12 pages\\
%%  Original Research & & & &\\
%%  Review & & & &\\
%%  Technology Report & & & &\\
%%  Focused Review & 2000 characters & 5 & 5000 words & 5 pages\\
%%  CPC &  1250 characters& 6 & 2500 words & 4 pages\\
%%  Perspective & 1250 characters & 2 & 3000 words & 3 pages\\
%%  Mini Review & & & &\\
%%  Classification & 1250 characters & 10 & 2000 words & 12 pages\\
%%  Editorial & none & none & 1000 words & 1 page \\
%%  Book review & & & &\\
%%  Frontiers Commentary & none & 1 & 1000 words & 1 page\\
%%  General Commentary & & & &\\
%%  Field Grand Challenge & & & &\\
%%  Opinion & none & 1 & 2000 words & 2 pages\\
%%  Specialty Grand Challenge& & & &\\\botrule
%% \end{tabular}}{}
%% \end{table}

%% \begin{figure}[h!]
%% \begin{center}
%% \includegraphics[width=10cm]{logo1}
%% \end{center}
%% \textbf{\refstepcounter{figure}\label{fig:01} Figure \arabic{figure}.}
%%        { Enter the caption for your figure here.  Repeat as necessary
%%          for each of your figures }
%% \end{figure}

### 2015-04-16 paper/paper.tex
Second day of writing done
I think it's a good first draft up to the results section.
Will now turn my attention to gathering results
to write about.

@@
 
-Benchmarking is a notoriously difficult task...
+Benchmarking is a notoriously difficult task.
+Benchmarks are often created by
+the creators of the tools being benchmarked,
+resulting in biased comparisons favoring their tool.
+Benchmarking can be an inefficient process,
+as the tool being benchmarked
+may need changes to collect
+certain performance metrics.
+Even once that effort is undertaken,
+benchmarks often are run a few times
+and then forgotten,
+quickly becoming obsolete.
+We propose that the Nengo test suite
+can serve as an unbiased, efficient, and future-proof
+set of benchmarks for neuromorphic systems.
 
@@
 that may or may not contribute to functional performance.
+
+The end result is a set of benchmarks that
+are written once but run on all backends,
+making new benchmarks easy to implement.
+Nengo's primary goal is to
+build large-scale functional models,
+and contains tests of functional performance;
+it is therefore not intentionally
+biased in favor of any particular backend.
+While there is effort involved in creating
+a Nengo backend for a particular neuromorphic system,
+the reason to build such a backend
+is to leverage the large-scale modelling interface
+provided by Nengo;
+the ability to collect benchmarks
+is provided essentially for free.
+Finally, since the test suite exists
+to ensure that Nengo continues to function
+correctly, and is run frequently using
+continuous integration systems,
+it will continue to grow and be run frequently,
+rather than becoming obsolete in the future.
 
@@
 
-Go over the nengo objects
+Nengo contains five frontend objects
+that validate and store symbolic information
+about the neural model that will be simulated.
+A lot of reasoning can be done at this symbolic level,
+which takes significant burdens off of each backend.
 
-Unlike other programming models,
-it's not like... for sure.
-Go over symbolic dists.
+The primary abstraction in Nengo is the \textit{Ensemble},
+which is a group of neurons (or neuron-like functions)
+that collectively represent a time-varying vector of numbers.
+Two parameters are mandatory: the number of neurons,
+and the dimensionality of the vector being represented.
+There are several optional parameters that
+affect how the neurons represent the vector space;
+encoders map the vector space into currents
+to be injected in the neurons,
+maximum firing rates can be specified for each neuron,
+the type of neuron model can be specified,
+and so on.
 
-Some things are suggestions.
-Go over backend hints.
+The \textit{Node} plays a similar role of representing
+time-varying vectors of numbers,
+but does so directly, without simulating a group of neurons.
+As such, the only mandatory parameter
+is what vector should be represented;
+this can be specified as a constant vector,
+or as a function of time.
+
+The \textit{Connection} connects two objects
+(e.g., \textit{Ensembles} or \textit{Nodes}) together.
+The two objects being connected are the only mandatory parameters;
+the synapse model filtering the connection
+and a function applied to the vector
+communicated across the connection
+can optionally be specified.
+
+The \textit{Probe} denotes that a particular
+quantity in the simulation should be recorded
+at a particular rate.
+The object to be probed must be specified;
+the attribute of that object,
+a sampling rate, and a synapse model for filtering
+can optionally be specified.
+
+An important distinction between typical
+parameters and those specified in Nengo
+is that many are stochastic,
+and not necessarily guaranteed
+to be supported by every backend.
+The vast majority of numeric parameters,
+for example,
+are most often specified as probability distributions;
+an ensemble's maximum firing rate defaults to
+a uniform distribution between 200 and 400 Hz,
+but this could be set to a Gaussian distribution
+or a discrete set of options and associated
+probabilities.
+Other parameters,
+most notably an ensemble's neuron model,
+may not be supported by a particular backend,
+which may raise an error.
+Even if a particular neuron model is supported,
+it may be implemented differently by each backend;
+Nengo does its best to approximate
+the high-level specification regardless of
+the neuron model that is actually used.
+
+Finally, the \textit{Network} is a
+container for the other four objects.
+The only parameter on the network
+is an optional integer seed;
+setting this should make
+all of the random factors
+in the model deterministic.
+Aside from managing the random seed,
+the network is responsible for maintaining
+a network-specific set of default parameters
+for the four other objects.
+This results in much shorter and less error-prone
+model creation scripts.
+
+An example script showing how Nengo can
+express a functional network
+with ??? neurons and ??? connections
+(representing ??? connection weights)
+in ??? lines of code can be seen
+in Figure~\ref{???}.
 
@@
 
-Go over the Simulator object, and required methods.
+The role of the backend is to take
+a single network, which contains
+ensembles, nodes, connections, and probes,
+and construct the underlying objects necessary
+to implement the model specified by that network.
+That implementation is exposed to Python
+through a \textit{Simulator} object,
+which has three required methods
+and one required attribute.
 
-Go over (briefly) translation of frontend to backend.
-Needed: some kind of neuron model; takes current,
-produces output (rates, spikes, whatever).
-Needed: Ops (look at all ops)
+The first method is \texttt{\_\_init\_\_},
+which is a special Python method for initializing objects.
+This method must accept a network as its first argument.
+It can then accept optional arguments depending on
+the capabilities and requirements of the backend;
+the reference backend, for example,
+accepts \texttt{dt},
+which is the length of each timestep.
+The purpose of \texttt{\_\_init\_\_} is to
+set up the low-level system
+that implements the high-level objects
+contained in the provided network.
+When parts of the model must be
+randomly sampled, the random factors
+should be identical when a network
+In the reference backend,
+this involves sampling from the distributions
+in all of the parameters of all objects,
+solving for decoding weights and connection weights,
+setting up data structures for probed data,
+and so on.
+
+The second method is \texttt{run},
+which advances the simulation
+by the number of seconds
+passed in as a required argument.
+Whatever low-level structure was created
+in \texttt{\_\_init\_\_} advances forward
+for that many real or simulated seconds,
+and importantly, any probed data is sampled
+according to its sample rate.
+In the reference backend,
+this advances the simulation
+by \texttt{time / dt} timesteps,
+where \texttt{dt} is fixed at the start of the simulation
+and cannot change;
+other backends may have variable-length timesteps,
+or may not explicitly track timesteps.
+
+The third method is \texttt{trange},
+which returns a sequence of times that correspond
+to the times at which data was probed.
+In the reference backend, this will be
+a straightforward sequence of increasing
+multiples of \texttt{dt};
+other backends may simulate at variable rates.
+
+Finally, the simulator object exposed by each backend
+must have an attribute called \texttt{data},
+which exposes a dictionary-like interface
+to the data being probed over the course
+of the simulation.
+The data dictionary should,
+at a minimum, provide a mapping from
+probe instances to the probed data;
+in other words, probe instances are keys
+and the probed data are values.
+
+These three methods and one attribute
+make up the public interface
+that Nengo tests expect from backends;
+it is an example
+of the adapter pattern \cite{???}. % Maybe lose?
+While the existence of the methods
+and attribute are necessary
+for every Nengo model,
+they are not sufficient;
+backends are not required
+to implement all of the neuron models
+or advanced features that
+are available in all other backends.
+Backends are responsible for informing
+the user when model cannot be implemented
+on that backend.
+The compliance metric (see section ???)
+explicitly tracks the details of what
+types of models can be implemented
+by each backend.
+The details of how each backend
+implements high-level frontend model
+are out of the scope of this paper.
 
@@
 as they construct a model,
-build a simulator object (see previous sec???)
+build a simulator object (see previous sec???),
+run that object,
 and test that the output of that model
+(as exposed through \texttt{trange}
+and \texttt{data})
 matches the desired output,
@@
 testing framework \cite{???}.
-??? introduce test fixtures
+\texttt{pytest} enables
+expressive testing of pluggable components
+(such as backends)
+through what are called ``test fixtures.''
+Fixtures are exposed to the test suite
+as arguments that can be provided
+to any test function.
+\texttt{pytest} inspects the function signature,
+and passes an appropriate value
+to the function.
+This allows for boilerplate code
+to be specified once,
+and run for any test that might use it.
+The example script in Figure~\ref{???}
+demonstrates how these fixtures
+look in test scripts.
 
@@
 
-\paragraph{\texttt{rng} \& \texttt{seed}} to manage random factors
+Nengo's test suite defines several test fixtures
+to enable fuzzy testing
+that collects and visualizes performance metrics
+on multiple backends.
 
-\paragraph{\texttt{Simulator}} to switch backend
+\paragraph{\texttt{rng} \& \texttt{seed}}
+enable deterministic testing despite
+all of the random factors that affect a model.
+Test functions that generate random values
+(as inputs to a model, for example)
+generate those values using \texttt{rng},
+which is a random number generator
+with an interface identical to
+NumPy's random module.
+When a test function creates a network,
+it passes in \texttt{seed} to make
+the random components
+of the frontend-to-backend translation deterministic.
+Importantly, these random components
+are seeded by hashing a string uniquely
+identifying each test function,
+ensuring that tolerances must be set
+wide enough that changing the seed
+should only rarely result in test failures.
+The hash function is also seeded
+with a global integer,
+which is changed periodically to ensure
+that tests have good tolerances.
 
-\paragraph{\texttt{nl}} to switch neuron type
+\paragraph{\texttt{Simulator}}
+allows for tests to be run with multiple backends.
+As detailed in section ???,
+each backend must expose a simulator class
+that accepts a network.
+Every test uses this test fixture rather than
+an actual class so that
+the backend-specific simulator class is used
+when the test is run.
+Each backend's test suite loads
+the tests defined in Nengo,
+but replaces the implementation of
+this fixture with their own fixture
+returning that particular backend's simulator class.
 
-\paragraph{\texttt{plt}} to save plots
+\paragraph{\texttt{plt}, \texttt{logger}, \& \texttt{analytics}}
+allow tests to save artifacts from test runs.
+These artifacts are how accuracy and speed metrics
+are collected, and how the figures
+in this paper are generated.
+The \texttt{plt} fixture exposes the Matplotlib \cite{???}
+\texttt{pyplot} interface to a test function.
+These functions can then analyze and plot
+the data generated in a simulation
+(exposed from a simulator's \texttt{data} attribute)
+to visualize the activity in a network.
+Figures are saved in a specified or backend-specific directory.
+The \texttt{logger} fixture exposes a logging interface
+to save arbitrary text to a specified
+or backend-specific directory;
+these are useful for summary statistics
+that can inspected manually.
+For large amounts of data that
+requires more analysis,
+\texttt{analytics} fixture exposes an interface
+to save arbitrary data (in the form of NumPy arrays)
+to specified or backend-specific directories.
 
-\paragraph{\texttt{analytics}} to save data
-
-\paragraph{\texttt{logger}} to save text
+\paragraph{\texttt{analytics\_data}}
+enables comparative testing between
+two runs of the same test.
+The two runs might represent two versions
+of the same backend---one before a
+speedup and one after---or two
+entirely different backends.
+The \texttt{analytics\_data} fixture
+provides the results from those two
+test runs to a single test function,
+allowing for comparisons
+between the two results saved
+with the \texttt{analytics} fixture.
+See Figure~\ref{???} for a
+concrete example of this.
 
@@
 
+Benchmarking involves collecting performance metrics
+for two or more comparable systems.
+Currently, the Nengo test suite collects
+three types of performance metrics
+across five backends.
+
 \subsection{Metrics collected}
 
-\subsubsection{Compliance}
+\paragraph{Compliance\textcolon}
 
-\subsubsection{Accuracy}
+\paragraph{Accuracy\textcolon}
 
-\subsubsection{Speed}
+\paragraph{Speed\textcolon}
 
@@
 
-\paragraph{Reference}
+\paragraph{Reference\textcolon}
 
-\paragraph{Simplified reference}
+\paragraph{Simplified reference\textcolon}
 
-\paragraph{OpenCL}
+\paragraph{OpenCL\textcolon}
 
-\paragraph{SpiNNaker hardware}
+\paragraph{SpiNNaker hardware\textcolon}
 
-\paragraph{Neurogrid simulation}
+\paragraph{Neurogrid simulation\textcolon}
 

### 2015-06-28 paper/paper.tex
First draft of paper done!
Needs work though.

@@
 
+\graphicspath{{../figures/}}
+
 \def\keyFont{\fontsize{8}{11}\helveticabold }
@@
 \def\Authors{Trevor Bekolay\,$^{1,*}$,
-  Terrence C. Stewart\,$^{1}$,
-  Eric Hunsberger\,$^1$,
-  Andrew Mundy\,$^2$ and
+  Terrence C. Stewart\,$^{1}$, and
   Chris Eliasmith\,$^1$}
@@
   University of Waterloo,
-  Waterloo, ON, Canada\\
-  $^{2}$ Advanced Processors Technologies Research Group,
-  School of Computer Science,
-  University of Manchester,
-  Manchester, UK}
+  Waterloo, ON, Canada}
 \def\corrAuthor{Trevor Bekolay}
@@
 for two or more comparable systems.
-Currently, the Nengo test suite collects
-three types of performance metrics
-across five backends.
+We collect three metrics in this study,
+as a proof of concept that the Nengo test suite
+can be used to collect meaningful benchmarks
+for neural simulators and neuromorphic hardware.
 
@@
 
-\paragraph{Compliance\textcolon}
+\paragraph{Compliance}
+is the number of tests that a particular backend
+passes successfully, relative to the reference
+backend, which must pass all tests.
+While this metric can give an indication
+of how many features a particular backend supports,
+it does not take into account how commonly used
+a particular feature is;
+for this reason, a backend that has relatively
+low compliance can still be very useful
+in many situations.
 
-\paragraph{Accuracy\textcolon}
+\paragraph{Accuracy}
+measures how well a particular backend
+implements a desired model.
+The actual accuracy metric depends
+on the desired model,
+but in simple cases can be
+the root mean squared error (RMSE)
+between a desired signal
+and the actual signal decoded
+from an ensemble.
 
-\paragraph{Speed\textcolon}
+\paragraph{Speed}
+measures the amount of time it takes
+for a backend to run a model.
+Primarily, we are concerned with
+the amount of time taken
+in \texttt{run} calls;
+however, we also separately measure how long
+each backend spends building each model
+(i.e., the time spent in \texttt{\_\_init\_\_}),
+as models must be built before being run.
+
+\subsection{Test models}
+
+Unlike the compliance metric,
+accuracy and speed are only collected
+for tests that define an an accuracy metric
+(i.e., those that use the \texttt{analytics} fixture).
+In this study, we focus on four such tests,
+which we claim are all necessary components
+of large-scale cognitive brain models,
+though they are by no means a sufficient set
+for all complex cognitive behaviors.
+
+\paragraph{1. Communication channel chain.}
+In this model,
+five ensembles,
+comprised of 500 leaky integrate-and-fire (LIF) neurons total,
+are connected in series,
+with a communication channel
+(i.e., the identity function)
+computed across each connection.
+This model, therefore, attempts to faithfully
+communicate an input signal to
+the last ensemble in the chain.
+The input signal used is a static vector.
+This model tests how
+robust each backend is to noise introduced
+by representing a vector space
+in the activity of spiking neurons.
+
+\paragraph{2. Two-dimensional product.}
+In this model,
+the scalar product is computed
+from a two-dimensional ensemble
+comprised of 100 LIF neurons.
+Since the product is nonlinear,
+we use a space-filling curve
+(the Hilbert curve \cite{???})
+as the input signal to ensure that
+we sample the entire two-dimensional space.
+This model tests each backend's
+ability to compute a nonlinear function,
+albeit a low-dimensional one.
+Despite the low dimensionality,
+two-dimensional products are frequently used
+in large-scale models;
+it is the primary operation used to
+bind semantic pointers, for example
+\cite{???}.
+
+\paragraph{3. Controlled oscillator.}
+In this model,
+a three-dimensional ensemble is recurrently connected
+such that the first two dimensions continuously
+traverse a limit cycle
+(i.e., they implement a cyclic attractor),
+and the third dimension controls the speed
+and direction of the oscillation.
+As input, we provide an initial stimulus
+to start the oscillation,
+and provide a control signal
+to cause oscillation at
+2Hz, 1Hz, 0Hz, -1Hz, and -2Hz.
+In total, the model is comprised of 600 LIF neurons.
+This model tests each backend's ability
+to stably implement a dynamical system,
+which is required for many cognitive functions
+like working memory and motor control.
+
+\paragraph{4. Basal Ganglia sequence.}
+In this model, comprised of 4900 LIF neurons,
+a basal ganglia is created (as described in \cite{???})
+that runs through a fixed sequence of actions.
+Stewart et al. \cite{???} have showed that
+these simple action sequences should
+switch at a rate of ???.
+This model tests that each backend can
+build this basal ganglia model,
+which is commonly used for action selection,
+and that actions can be selected at the
+hypothesized rate.
 
@@
 
-\paragraph{Reference\textcolon}
+We collected the three benchmark metrics
+on five Nengo backends.
 
-\paragraph{Simplified reference\textcolon}
+\paragraph{1. Reference (\texttt{nengo}).}
+The reference backend is designed to run quickly
+on any general purpose computer
+by using NumPy \cite{???}
+for fast vectorized computations.
+It is included with the \texttt{nengo} frontend
+as \texttt{nengo.Simulator}.
+When appropriate, other backends will be benchmarked
+relative to the reference backend,
+which has the most features but does not target
+specialized hardware.
 
-\paragraph{OpenCL\textcolon}
+\paragraph{2. Distilled (\texttt{nengo\_distilled}).}
+The distilled backend is intended as a teaching tool,
+and as a template for building new backends.
+It can also run on any general purpose computer,
+and also uses NumPy for fast vectorized computations,
+but does not aim to implement all of the features
+implemented by the reference backend,
+and omits some optimizations that obfuscate code.
+Therefore, the distilled backend is easier to read
+and suitable for learning about Nengo
+or as a starting point for new backends.
 
-\paragraph{SpiNNaker hardware\textcolon}
+\paragraph{3. OpenCL (\texttt{nengo\_ocl}).}
+The OpenCL backend uses the Open Computing Language
+(OpenCL; \cite{???})
+to run Nengo models on many different computing devices,
+including graphical processing units (GPUs),
+and field-programmable gate arrays (FPGAs).
+In contrast to the distilled backend,
+it is designed to run Nengo models
+as quickly as possible,
+using fast general purpose computing devices
+like GPUs and any optimizations available,
+at the cost of code readability.
 
-\paragraph{Neurogrid simulation\textcolon}
+\paragraph{4. Neurogrid software (\texttt{nengo\_brainstorm}).}
+The Neurogrid backend is a software implementation
+of a potential neuromorphic chip being developed
+by Boahen et al. \cite{???}.
+It does not aim for speed;
+instead, it attempts to emulate the hardware
+in order to test its applicability
+to large-scale neural models.
+If the emulated hardware can perform well,
+then it follows that actual hardware
+will also perform well,
+but will be much faster.
+
+\paragraph{5. SpiNNaker hardware (\texttt{nengo\_spinnaker}).}
+The SpiNNaker backend targets
+the eponymous neuromorphic hardware
+developed by Furber et al. \cite{???}.
+In contrast to the Neurogrid backend,
+this backend targets physical neuromorphic hardware,
+and therefore is concerned
+both with accuracy and speed.
+
+\subsection{Hardware used for running benchmarks}
+
+??? ask Xuan
+
+SpiNN-5 board
 
@@
 
+\subsection{Compliance}
+
+Table~\ref{Tab:01} gives compliance results for
+all backends except the SpiNNaker backend,
+which is not yet set up to run the Nengo test suite.
+Of the four currently running unit tests,
+the OpenCL backend has the highest compliance
+(other than the reference backend).
+The distilled backend has lower compliance
+than OpenCL, which follows from its stated goal
+of being simple but not necessarily feature-rich.
+The Neurogrid backend is the least compliant,
+but it is still an early experimental test bed;
+this is not necessarily indicative of the
+final Neurogrid hardware backend being
+less compliant than other backends.
+
+\subsection{Accuracy}
+
+Figure~\ref{fig:01} gives accuracy results
+for each backend on the chained communication channel model.
+The boxplot shows that all five backends can
+implement this model accurately,
+despite five sources of potential noise.
+
+Figure~\ref{fig:02} gives accuracy results
+for the two-dimensional product model.
+In this case, while all of the backends
+perform well, the SpiNNaker backend
+performs significantly worse than the
+other four backends.
+Its performance, however, is still well within
+acceptable ranges for the two-dimensional product model.
+
+Figure~\ref{fig:03} gives accuracy results
+for the controlled oscillator model.
+The reference and OpenCL backends perform well here,
+as do the distilled and Neurogrid backends.
+The SpiNNaker backend performs well in most cases,
+but some instances of the model
+are significantly less accurate
+than the majority of instances.
+
+Figure~\ref{fig:04} gives accuracy results
+for the basal ganglia sequence model.
+Again, all of the backends perform similarly,
+except for the SpiNNaker backend.
+All other backends have a transition time
+around 43 milliseconds, which matches
+the results from Stewart et al. 2010 \cite{???}
+for simple actions.
+The SpiNNaker backend has a transition time
+around 55 milliseconds, which is slower
+than the time reported by Stewart et al.
+for simple actions, but faster than the
+time reported for complex actions.
+
+\subsection{Speed}
+
+Figures~\ref{fig:05} and \ref{fig:06} show
+the build and run speeds for all backends, respectively.
+While build time is not critical to optimize,
+it is worth noting that the reference backend
+has consistently fast builds.
+The OpenCL backend is also usually fast,
+but can be slow for certain types of networks
+(e.g., the chained communication channel model).
+The distilled and Neurogrid backends---which
+have a very similar build process---become
+slow when dealing with moderately sized models
+(e.g., the basal ganglia sequence model,
+which contains 4900 neurons).
+The SpiNNaker backend incurs an unavoidable cost
+in setting up the hardware,
+though it builds the largest model faster than
+the distilled and Neurogrid backends.
+
+The run time results are of the utmost importance
+when evaluating backends for different applications,
+especially those that require real-time interaction,
+such as robotics. In general, all backends
+perform adequately for the three smaller models.
+The OpenCL backend is significantly slower for small
+models, like the product and controlled oscillator models.
+SpiNNaker, on the other hand, is slower than other backends
+for these models, but only because its goal
+is to run in real-time even if it is possible to run faster.
+(??? Andrew is this true?)
+The most important result is for the largest model,
+the basal ganglia sequence.
+In this model, the distilled and Neurogrid backends
+performed very poorly
+(though neither has speed as a primary goal).
+The reference backend also did not perform well,
+operating at nearly eight times slower than real-time.
+The OpenCL backend performed well, operating at around
+four times slower than real-time.
+The best performance was seen by the SpiNNaker backend,
+however, which operated at around 1.5 times real-time
+on this moderately-sized model.
+
+Despite the fast run times for
+the OpenCL and SpiNNaker backends,
+we also investigated the possibility
+that probes were slowing these backend down,
+since probes require moving data from
+their native platform (GPU or SpiNNaker board)
+to the CPU. However, we found that
+removing probes from these models
+made almost no impact on their run time
+(see Figure~\ref{Fig:07}).
+
 \section{Discussion}
+
+The most important finding from these benchmarks
+is that specialized hardware (including GPUs)
+can result in significantly faster run times
+for certain models,
+with little to no cost in accuracy.
+The conditions under which the OpenCL backend
+performs slower than the reference backend
+(e.g., the product and controlled oscillator models)
+bear closer inspection to determine the source
+of the slowdown.
+Similarly, we should investigate
+the model instances in which the SpiNNaker backend
+is less accurate (e.g., in the controlled oscillator model)
+or different from other backends
+(e.g., in the basal ganglia sequence model).
+
+Above and beyond the benchmarking results,
+however, we assert that the primary contribution
+of this study is to provide evidence that Nengo
+has a tested, stable, productive frontend
+that can target multiple backends,
+and therefore provides a platform
+for benchmarking neuromorphic backends,
+and other neural simulators.
+While this is similar to the goal
+of similar projects, such a PyNN \cite{???},
+Nengo is unique in focusing on large-scale simulations,
+rather than attempting to support
+detailed single-neuron models
+(though this capability is still possible in Nengo;
+see \cite{???}).
+
+While we cannot claim that Nengo
+solves all of complications that arise
+in benchmarking,
+we believe that it improves upon
+the three major issues identified in the introduction.
+First, benchmarking neuromorphic hardware
+with Nengo is less biased than
+hardware-specific benchmarks,
+because the purpose of Nengo is
+to make functionally interesting large-scale models.
+These models are typically build and tested
+in the reference backend,
+leaving little opportunity to introduce
+hardware-specific optimizations
+that can bias benchmarks.
+
+Second, there is less wasted effort
+in using Nengo for benchmarking,
+as the only requirement for using
+Nengo is to develop a backend.
+Building a Nengo backend for
+a piece of neuromorphic hardware
+gives access to all of the models
+already developed for it,
+which is reason enough to develop a backend.
+The ability to collect functionally relevant benchmarks
+comes ``for free'' once the backend exists.
+
+Third, these benchmarks are more likely to
+remain up-to-date because backend developers
+themselves do not have to implement or update
+these benchmarks;
+they will be implemented to test Nengo's
+capabilities as a neural simulator,
+as an extension of the existing test suite.
+Once implemented, backends that implement
+the features that are used in a particular benchmark
+should not have to modify their own code
+to run those benchmarks on their own hardware.
+
+???concluding remarks
 
@@
 
-%% Frontiers supports the policy of data sharing, and authors are advised
-%% to make freely available any materials and information described in
-%% their article, and any data relevant to the article (while not
-%% compromising confidentiality in the context of human-subject research)
-%% that may be reasonably requested by others for the purpose of academic
-%% and non-commercial research. In regards to deposition of data and data
-%% sharing through databases, Frontiers urges authors to comply with the
-%% current best practices within their discipline.
+???put results.zip on figshare
+
+???link to Github
 
@@
 
-%Frontiers follows the recommendations by the International Committee
-%of Medical Journal Editors
-%(http://www.icmje.org/ethical_4conflicts.html) which require that all
-%financial, commercial or other relationships that might be perceived
-%by the academic community as representing a potential conflict of
-%interest must be disclosed. If no such relationship exists, authors
-%will be asked to declare that the research was conducted in the
-%absence of any commercial or financial relationships that could be
-%construed as a potential conflict of interest. When disclosing the
-%potential conflict of interest, the authors need to address the
-%following points: • Did you or your institution at any time receive
-%payment or services from a third party for any aspect of the
-%submitted work?  • Please declare financial relationships with
-%entities that could be perceived to influence, or that give the
-%appearance of potentially influencing, what you wrote in the
-%submitted work.  • Please declare patents and copyrights, whether
-%pending, issued, licensed and/or receiving royalties relevant to the
-%work.  • Please state other relationships or activities that readers
-%could perceive to have influenced, or that give the appearance of
-%potentially influencing, what you wrote in the submitted work.
-
-%% The authors declare that the research was conducted in the absence of
-%% any commercial or financial relationships that could be construed as a
-%% potential conflict of interest.
+???probably something about ABR here?
 
@@
 
-%When determining authorship the following criteria should be observed:
-%• Substantial contributions to the conception or design of the work; or the acquisition, analysis, or interpretation of data for the work; AND
-%• Drafting the work or revising it critically for important intellectual content; AND
-%• Final approval of the version to be published ; AND
-%• Agreement to be accountable for all aspects of the work in ensuring that questions related to the accuracy or integrity of any part of the work are appropriately investigated and resolved.
-%Contributors who meet fewer than all 4 of the above criteria for authorship should not be listed as authors, but they should be acknowledged. (http://www.icmje.org/roles_a.html)
-
-%% The statement about the authors and contributors can be up to several
-%% sentences long, describing the tasks of individual authors referred to
-%% by their initials and should be included at the end of the manuscript
-%% before the References section.
+???todo
 
 \section*{Acknowledgments}
-%% Acknowledgments
+
+???todo
+(Andrew Mundy for SpiNNaker help, feedback on first draft,
+Xuan for GPU server, Eric for help in getting OCL benchmarks running,
+James for implementing most of OCL, Jan for product benchmark)
 
 \paragraph{Funding\textcolon} %% Funding
-
-\section*{Supplemental Data}
-%% Supplementary Material should be uploaded separately on submission, if
-%% there are Supplementary Figures, please include the caption in the
-%% same file as the figure. LaTeX Supplementary Material templates can be
-%% found in the Frontiers LaTeX folder
 
@@
 
+\begin{table}[!ht]
+\textbf{\refstepcounter{table}\label{Tab:01} Table \arabic{table}.}{
+  Compliance of four backends.}
+
+\processtable{ }
+{\begin{tabular}{lcc}\toprule
+ Backend & Number of tests passed & Percentage of tests passed\\\midrule
+ Reference (\texttt{nengo}) & 212 & 100\% \\
+ Distilled (\texttt{nengo\_distilled}) & 129 & 60.8\% \\
+ OpenCL (\texttt{nengo\_ocl}) & 187 & 88.2\% \\
+ Neurogrid (\texttt{nengo\_brainstorm}) & 107 & 50.4\% \\\botrule
+\end{tabular}}{}
+\end{table}
+
+\begin{figure}[!ht]
+\begin{center}
+  \includegraphics[width=85mm]{fig1}
+\end{center}
+\textbf{\refstepcounter{figure}\label{fig:01} Figure \arabic{figure}.}
+       {Chained communication channel model. (Top) One example instance
+         of the model run on the reference backend; the decoded output
+         of the five chained two-dimensional ensembles during the first
+         12 milliseconds of the simulation are shown.
+         Each ensemble reaches approximately the correct value of
+         $[-0.6, 0.6]$ (indicated with the solid black line)
+         but with slight delays depending on their position in the chain.
+         (Bottom) The aggregated accuracy results for each backend on the
+         chained communication channel model. The observed metric is the root
+         mean-squared error (RMSE) between the decoded output of the last
+         ensemble in the chain and the correct value (which is randomly
+         selected on each trial), during the last 100 milliseconds of the
+         500 millisecond simulation. The box shows the median and
+         inter-quartile range, while the whiskers extend to 1.5 times the
+         inter-quartile range; outliers are not shown.}
+\end{figure}
+
+\begin{figure}[!ht]
+\begin{center}
+  \includegraphics[width=85mm]{fig2}
+\end{center}
+\textbf{\refstepcounter{figure}\label{fig:02} Figure \arabic{figure}.}
+       {Two-dimensional product model. (Top) One example instance of the model
+         run on the reference backend; the decoded input represented
+         by the two-dimensional ensemble is shown. The input signal is
+         designed to fully explore the two-dimensional vector space
+         in the range $[-1, 1]$.
+         (Middle) The decoded product represented by an ensemble downstream
+         of the ensemble representing the input. It closely matches the
+         correct product (indicated with the solid black line).
+         (Bottom) The aggregated accuracy results for each backend on the
+         two-dimensional product model. The measured metric is the root
+         mean-squared error (RMSE) between the decoded output of the ensemble
+         representing the product and the correct product, during the whole
+         range of inputs provided over 5 simulated seconds (after a 500
+         millisecond wait period to allow the input ensemble to reach the
+         correct initial state). The box shows the median and
+         inter-quartile range, while the whiskers extend to 1.5 times the
+         inter-quartile range; outliers are not shown.}
+\end{figure}
+
+\begin{figure}[!ht]
+\begin{center}
+  \includegraphics[width=180mm]{fig3}
+\end{center}
+\textbf{\refstepcounter{figure}\label{fig:03} Figure \arabic{figure}.}
+       {Controlled two-dimensional oscillator model. (Left) One example
+         instance of the model run on the reference backend; the decoded
+         value represented by one of the two dimensions in the oscillatory
+         ensemble is shown. The control signal dictating the frequency of
+         oscillation changes every two seconds; in this plot each two second
+         period is overlaid. Each signal oscillates at approximately the
+         correct frequency (see middle for legend).
+         (Middle) The power spectrum of each two second period.
+         High power is seen only at the frequency we attempt to induce,
+         for each of the five test frequencies.
+         (Right) The aggregated accuracy results for each backend on the
+         two-dimensional product model. The measured metric is the similarity
+         between the power spectrum (calculated using the Fast Fourier
+         Transform or FFT) of the decoded output of one of the two oscillatory
+         dimensions in the ensemble, and the ideal power spectrum,
+         computed on a pure sine wave oscillating at the induced frequency.
+         Similarity is computed using a normalized dot product across
+         all frequencies. The box shows the median and
+         inter-quartile range, while the whiskers extend to 1.5 times the
+         inter-quartile range; outliers are not shown.}
+\end{figure}
+
+\begin{figure}[!ht]
+\begin{center}
+  \includegraphics[width=85mm]{fig4}
+\end{center}
+\textbf{\refstepcounter{figure}\label{fig:04} Figure \arabic{figure}.}
+       {Basal Ganglia sequence model. (Top) One example instance
+         of the model run on the reference backend; the similarity between
+         the current representation in working memory and the six possible
+         actions is shown (note that in the full benchmark, ten items are
+         used). The model quickly progresses from one action to the next,
+         cycling back at the end of the six items. The point at which the
+         model switches from selecting one action to another action
+         (the transition times) are indicated with dashed grey lines.
+         (Bottom) The aggregated accuracy results for each backend on the
+         basal ganglia sequence model. The observed metric is the mean
+         time to transition from one action to the next. The model is run
+         for four second, allowing for approximately 90 transitions, depending
+         on the transition time. The box shows the median and
+         inter-quartile range, while the whiskers extend to 1.5 times the
+         inter-quartile range; outliers are not shown.}
+\end{figure}
+
+\begin{figure}[!ht]
+\begin{center}
+  \includegraphics[width=85mm]{fig5}
+\end{center}
+\textbf{\refstepcounter{figure}\label{fig:05} Figure \arabic{figure}.}
+       {Build time for each model on each backend. Each bar represents
+         the mean build time across 150 instances of each model;
+         error bars are 95\% confidence intervals.}
+\end{figure}
+
+\begin{figure}[!ht]
+\begin{center}
+  \includegraphics[width=85mm]{fig6}
+\end{center}
+\textbf{\refstepcounter{figure}\label{fig:06} Figure \arabic{figure}.}
+       {Run time for each model on each backend. Each bar represents
+         the mean run time across 150 instances of each model;
+         error bars are 95\% confidence intervals.
+         Run time is measured relative to real time;
+         e.g., a value of two indicates that the model ran twice as slow
+         as real time.}
+\end{figure}
+
 \end{document}
-
-%% \begin{table}[!t]
-%% \textbf{\refstepcounter{table}\label{Tab:01} Table \arabic{table}.}{
-%%   Maximum size of the Manuscript }
-
-%% \processtable{ }
-%% {\begin{tabular}{lllll}\toprule
-%%  & Abstract max. legth (incl. spaces) & Figures or tables & Manuscript max. length & Final PDF length\\\midrule
-%%  Clinical Case Study & & & &\\
-%%  Clinical Trial & & & &\\
-%%  Hypothesis and Theory & & & &\\
-%%  Methods & 2000 characters  & 15 & 12000 words & 12 pages\\
-%%  Original Research & & & &\\
-%%  Review & & & &\\
-%%  Technology Report & & & &\\
-%%  Focused Review & 2000 characters & 5 & 5000 words & 5 pages\\
-%%  CPC &  1250 characters& 6 & 2500 words & 4 pages\\
-%%  Perspective & 1250 characters & 2 & 3000 words & 3 pages\\
-%%  Mini Review & & & &\\
-%%  Classification & 1250 characters & 10 & 2000 words & 12 pages\\
-%%  Editorial & none & none & 1000 words & 1 page \\
-%%  Book review & & & &\\
-%%  Frontiers Commentary & none & 1 & 1000 words & 1 page\\
-%%  General Commentary & & & &\\
-%%  Field Grand Challenge & & & &\\
-%%  Opinion & none & 1 & 2000 words & 2 pages\\
-%%  Specialty Grand Challenge& & & &\\\botrule
-%% \end{tabular}}{}
-%% \end{table}
-
-%% \begin{figure}[h!]
-%% \begin{center}
-%% \includegraphics[width=10cm]{logo1}
-%% \end{center}
-%% \textbf{\refstepcounter{figure}\label{fig:01} Figure \arabic{figure}.}
-%%        { Enter the caption for your figure here.  Repeat as necessary
-%%          for each of your figures }
-%% \end{figure}

### 2015-06-28 paper/supplementary.tex
First draft of paper done!
Needs work though.

--- 2015-04-15 paper/paper.tex
@@
-\documentclass{frontiersSCNS}
+%%% You will need to have the following packages installed: datetime, fmtcount, etoolbox, fcprefix, which are normally inlcuded in WinEdt. %%%
+\documentclass{frontiers_suppmat} % for all articles
 
-\usepackage{url,lineno}
-\linenumbers
+\usepackage{url}
 
+\graphicspath{{../figures/}}
+
+\def\articleType{Supplementary Material}
 \def\keyFont{\fontsize{8}{11}\helveticabold }
@@
 
-\title[Benchmarking neuromorphic systems with Nengo]{Benchmarking neuromorphic systems with Nengo}
+\title[Supplementary Material]{{\helveticaitalic{Supplementary Material}}:\\ \helvetica{ Benchmarking neuromorphic systems with Nengo}}
 \author[\firstAuthorLast ]{\Authors}
@@
 
-\begin{abstract}
+\section{Supplementary Tables and Figures}
 
-  Abstract
-
-  \tiny
-  % 5--8 keywords
-  \keyFont{ \section{Keywords:}  }
-\end{abstract}
-
-\section{Introduction}
-
-Benchmarking is a notoriously difficult task...
-
-Nengo is a rigorously tested software package
-for building and simulating
-large-scale neural models
-that can perform cognitively relevant tasks.
-It provides a high-level API (frontend)
-that can express large-scale models concisely
-and in a platform-independent manner.
-Several Nengo-compatible simulators (backends)
-have been developed that can
-run Nengo models on diverse platforms,
-including neuromorphic hardware.
-Nengo's separation between frontend and backend
-and rigorous test suite
-provide standardized comparisons
-between different neuromorphic implementations
-that are geared toward (???) functional performance,
-rather than artificial metrics
-that may or may not contribute to functional performance.
-
-Other software that do similar things:
-many neural simulators exist, and have tests,
-but don't have the high-level API
-that Nengo has.
-On the other hand, some simulators
-have high-level APIs
-(Topographica?) but a) aren't functional
-and b) can't use diverse backends.
-
-??? In the subsequent sections,
-we detail the architecture of Nengo's
-frontend and backend,
-and describe what each backend
-is required to implement.
-We explain Nengo's testing framework,
-including descriptions of the testing fixtures
-used to collect and visualize benchmarks.
-We then list the metrics that will be collected,
-and the backends on which we will collect metrics.
-Finally, we will show and discuss
-the results of collecting those metrics
-for each backend.
-
-\section{Background}
-
-There are two key features of Nengo 2.0
-that enable rapid benchmarking of neuromorphic systems.
-The first is a decoupling of model creation and simulation,
-resulting in a platform independent frontend interface
-to any backend that implements a certain set of requirements.
-The second is a ``fuzzy'' test suite ensuring that
-Nengo can be used to create models that solve cognitive tasks.
-This test suite makes ample use of test fixtures
-to enable data collection while testing on arbitrary backends.
-
-\subsection{Nengo architecture}
-
-Nengo has a strict separation between
-the frontend and backend.
-The frontend exposes a modelling interface
-that uses Python and NumPy \cite{???}
-to define models concisely.
-Backends are responsible for transforming
-those frontend objects into code that
-can be run on the target platform.
-While each backend must be exposed
-through Python, this requirement
-does not significantly limit
-flexibility in the backend.
-A backend can be implemented in C and exposed
-through Python bindings,
-or can be run as a separate process
-managed by the Python backend,
-with data transmitted to Python through sockets
-or other inter-process communication protocols.
-
-\subsubsection{Frontend interface}
-
-Go over the nengo objects
-
-Unlike other programming models,
-it's not like... for sure.
-Go over symbolic dists.
-
-Some things are suggestions.
-Go over backend hints.
-
-\subsubsection{Backend requirements}
-
-Go over the Simulator object, and required methods.
-
-Go over (briefly) translation of frontend to backend.
-Needed: some kind of neuron model; takes current,
-produces output (rates, spikes, whatever).
-Needed: Ops (look at all ops)
-
-\subsection{Fuzzy testing}
-
-As of version 2.0.1, Nengo's test suite contains 618 tests.
-Some test are unit tests though; how many?
-In all, ??? can be considered ``functional'' tests,
-as they construct a model,
-build a simulator object (see previous sec???)
-and test that the output of that model
-matches the desired output,
-to a certain tolerance.
-
-Unlike traditional software testing,
-there can be significant variability
-in many aspects of a Nengo model.
-Many model parameters, for example,
-can be randomly generated;
-other aspects of a model,
-such as injected noise,
-are necessarily random.
-Noise is a fundamental property
-of neuromorphic systems.
-The accuracy of any large-scale model
-is dependent on many factors,
-including the number of neurons used
-to implement a particular task.
-For this reason,
-functional tests can only
-ensure that the backend implements
-the system described by the frontend
-well enough.
-Each test must determine what
-``well enough'' means for that particular network.
-While this introduces some subjectivity
-to these benchmarks,
-it is nearly impossible to create
-completely objective benchmarks.
-??? more or remove last bit
-
-Nengo's test suite employs the \texttt{pytest}
-testing framework \cite{???}.
-??? introduce test fixtures
-
-\subsubsection{Test fixtures}
-
-\paragraph{\texttt{rng} \& \texttt{seed}} to manage random factors
-
-\paragraph{\texttt{Simulator}} to switch backend
-
-\paragraph{\texttt{nl}} to switch neuron type
-
-\paragraph{\texttt{plt}} to save plots
-
-\paragraph{\texttt{analytics}} to save data
-
-\paragraph{\texttt{logger}} to save text
-
-\section{Methods}
-
-\subsection{Metrics collected}
-
-\subsubsection{Compliance}
-
-\subsubsection{Accuracy}
-
-\subsubsection{Speed}
-
-\subsection{Backends tested}
-
-\paragraph{Reference}
-
-\paragraph{Simplified reference}
-
-\paragraph{OpenCL}
-
-\paragraph{SpiNNaker hardware}
-
-\paragraph{Neurogrid simulation}
-
-\section{Results}
-
-\section{Discussion}
-
-\subsection{Data Sharing}
-
-%% Frontiers supports the policy of data sharing, and authors are advised
-%% to make freely available any materials and information described in
-%% their article, and any data relevant to the article (while not
-%% compromising confidentiality in the context of human-subject research)
-%% that may be reasonably requested by others for the purpose of academic
-%% and non-commercial research. In regards to deposition of data and data
-%% sharing through databases, Frontiers urges authors to comply with the
-%% current best practices within their discipline.
-
-\section*{Disclosure/Conflict-of-Interest Statement}
-
-%Frontiers follows the recommendations by the International Committee
-%of Medical Journal Editors
-%(http://www.icmje.org/ethical_4conflicts.html) which require that all
-%financial, commercial or other relationships that might be perceived
-%by the academic community as representing a potential conflict of
-%interest must be disclosed. If no such relationship exists, authors
-%will be asked to declare that the research was conducted in the
-%absence of any commercial or financial relationships that could be
-%construed as a potential conflict of interest. When disclosing the
-%potential conflict of interest, the authors need to address the
-%following points: • Did you or your institution at any time receive
-%payment or services from a third party for any aspect of the
-%submitted work?  • Please declare financial relationships with
-%entities that could be perceived to influence, or that give the
-%appearance of potentially influencing, what you wrote in the
-%submitted work.  • Please declare patents and copyrights, whether
-%pending, issued, licensed and/or receiving royalties relevant to the
-%work.  • Please state other relationships or activities that readers
-%could perceive to have influenced, or that give the appearance of
-%potentially influencing, what you wrote in the submitted work.
-
-%% The authors declare that the research was conducted in the absence of
-%% any commercial or financial relationships that could be construed as a
-%% potential conflict of interest.
-
-\section*{Author Contributions}
-
-%When determining authorship the following criteria should be observed:
-%• Substantial contributions to the conception or design of the work; or the acquisition, analysis, or interpretation of data for the work; AND
-%• Drafting the work or revising it critically for important intellectual content; AND
-%• Final approval of the version to be published ; AND
-%• Agreement to be accountable for all aspects of the work in ensuring that questions related to the accuracy or integrity of any part of the work are appropriately investigated and resolved.
-%Contributors who meet fewer than all 4 of the above criteria for authorship should not be listed as authors, but they should be acknowledged. (http://www.icmje.org/roles_a.html)
-
-%% The statement about the authors and contributors can be up to several
-%% sentences long, describing the tasks of individual authors referred to
-%% by their initials and should be included at the end of the manuscript
-%% before the References section.
-
-\section*{Acknowledgments}
-%% Acknowledgments
-
-\paragraph{Funding\textcolon} %% Funding
-
-\section*{Supplemental Data}
-%% Supplementary Material should be uploaded separately on submission, if
-%% there are Supplementary Figures, please include the caption in the
-%% same file as the figure. LaTeX Supplementary Material templates can be
-%% found in the Frontiers LaTeX folder
-
-\bibliographystyle{frontiersinSCNS}
-\bibliography{paper}
-
-\section*{Figures}
+\begin{figure}[!ht]
+\begin{center}
+  \includegraphics[width=85mm]{fig7}
+\end{center}
+\textbf{\refstepcounter{figure}\label{fig:01} Supplementary Figure \arabic{figure}.}
+       {Run time for each model with probes removed on each backend.
+         Each bar represents the mean run time across 100 instances
+         of each model;
+         error bars are 95\% confidence intervals.
+         Run time is measured relative to real time;
+         e.g., a value of two indicates that the model ran twice as slow
+         as real time.}
+\end{figure}
 
 \end{document}
-
-%% \begin{table}[!t]
-%% \textbf{\refstepcounter{table}\label{Tab:01} Table \arabic{table}.}{
-%%   Maximum size of the Manuscript }
-
-%% \processtable{ }
-%% {\begin{tabular}{lllll}\toprule
-%%  & Abstract max. legth (incl. spaces) & Figures or tables & Manuscript max. length & Final PDF length\\\midrule
-%%  Clinical Case Study & & & &\\
-%%  Clinical Trial & & & &\\
-%%  Hypothesis and Theory & & & &\\
-%%  Methods & 2000 characters  & 15 & 12000 words & 12 pages\\
-%%  Original Research & & & &\\
-%%  Review & & & &\\
-%%  Technology Report & & & &\\
-%%  Focused Review & 2000 characters & 5 & 5000 words & 5 pages\\
-%%  CPC &  1250 characters& 6 & 2500 words & 4 pages\\
-%%  Perspective & 1250 characters & 2 & 3000 words & 3 pages\\
-%%  Mini Review & & & &\\
-%%  Classification & 1250 characters & 10 & 2000 words & 12 pages\\
-%%  Editorial & none & none & 1000 words & 1 page \\
-%%  Book review & & & &\\
-%%  Frontiers Commentary & none & 1 & 1000 words & 1 page\\
-%%  General Commentary & & & &\\
-%%  Field Grand Challenge & & & &\\
-%%  Opinion & none & 1 & 2000 words & 2 pages\\
-%%  Specialty Grand Challenge& & & &\\\botrule
-%% \end{tabular}}{}
-%% \end{table}
-
-%% \begin{figure}[h!]
-%% \begin{center}
-%% \includegraphics[width=10cm]{logo1}
-%% \end{center}
-%% \textbf{\refstepcounter{figure}\label{fig:01} Figure \arabic{figure}.}
-%%        { Enter the caption for your figure here.  Repeat as necessary
-%%          for each of your figures }
-%% \end{figure}

### 2015-06-28 fnme/benchmarks.py

@@ -6,11 +6,13 @@ nengo_brainstorms backend, adapted to be run using Nengo test suite.
 Contributors:
   - Terry Stewart (CNRG lab)
   - Trevor Bekolay (CNRG lab)
+  - Jan Gosmann (CNRG lab)
   - Sam Fok (Brains in Silicon, Stanford University)
   - Alexander Neckar (Brains in Silicon, Stanford University)
   - John Aguayo (Brains in Silicon, Stanford University)
 """
 import numpy as np
+import seaborn as sns
 
 import nengo
 import nengo.spa as spa
@@ -22,8 +24,10 @@ try:
 except ImportError:
     pass
 
+from .plots import setup, prettify, onecolumn, twocolumn
 from .utils import HilbertCurve
 
+colors = sns.color_palette()
 
 # --- 1. Communication channel chain
 def test_cchannelchain(Simulator, plt, rng, seed, outfile, probes):
@@ -53,21 +57,21 @@ def test_cchannelchain(Simulator, plt, rng, seed, outfile, probes):
     sim.run(0.5)
 
     if probes:
-        plt.subplot(2, 1, 1)
-        plt.plot(sim.trange(), sim.data[p_input], c='k', lw=2)
-        for p_output in p_outputs:
-            plt.plot(sim.trange(), sim.data[p_output])
+        setup(figsize=(onecolumn * 2, 4.0))
+        for i, p_output in enumerate(p_outputs):
+            plt.plot(sim.trange(), sim.data[p_output],
+                     c=colors[i % len(colors)])
+        plt.plot(sim.trange(), sim.data[p_input], c='k', lw=1)
+        plt.yticks((-0.6, 0, 0.6))
+        plt.xticks((0, 0.05, 0.1))
         plt.ylabel('Decoded output')
-        plt.xticks(())
-
-        plt.subplot(2, 1, 2)
-        for p_output in p_outputs:
-            plt.plot(sim.trange(), np.sum(np.abs(
-                sim.data[p_output] - sim.data[p_input]), axis=1))
-        plt.ylabel("Error")
         plt.xlabel('Time (s)')
+        plt.saveas = 'results-1.svg'
 
         with open(outfile, 'a') as outf:
+            outf.write('"n_neurons": %d,\n' % sum(
+                e.n_neurons for e in model.all_ensembles))
+            outf.write('"simtime": 0.5,\n')
             outf.write('"rmse": %f,\n' % (
[…]

### 2015-06-28 fnme/plots.py

@@ -1,25 +1,77 @@
 import json
 import os
+import subprocess
 from collections import OrderedDict
 from glob import glob
 
-import numpy as np
 import matplotlib.pyplot as plt
 import pandas as pd
 import seaborn as sns
+import svgutils.transform as sg
+from scipy import stats
 
 root = os.path.dirname(__file__)
 plots_dir = os.path.realpath(os.path.join(root, os.pardir, 'plots'))
 results_dir = os.path.realpath(os.path.join(root, os.pardir, 'results'))
 noprobes_dir = os.path.join(results_dir, 'noprobes')
 results_dir = os.path.join(results_dir, 'probes')
+fig_dir = os.path.realpath(os.path.join(root, os.pardir, 'figures'))
+# Change if not on Mac OS X
+inkscape = os.path.expanduser("~/Applications/Inkscape.app/Contents"
+                              "/Resources/bin/inkscape")
+
+onecolumn = 3.34646  # inches
+twocolumn = 7.08661  # inches
 
 
-def setup():
+class RectElement(sg.FigureElement):
+    def __init__(self, x, y):
+        s = 18
+        rect = sg.etree.Element(sg.SVG+"rect",
+                                {"x": str(x), "y": str(y - s),
+                                 "width": str(s), "height": str(s),
+                                 "style": "fill:white;"})
+        sg.FigureElement.__init__(self, rect)
+
+
+def el(char, path, x, y, scale=1, offset=(10, 30)):
+    toret = []
+    if char is not None:
+        toret.append(RectElement(x + offset[0], y + offset[1]))
+        toret.append(sg.TextElement(x + offset[0],
+                                    y + offset[1],
+                                    char,
+                                    size=24,
+                                    weight='bold',
+                                    font='Arial'))
+    if path.endswith(".svg"):
+        svg = sg.fromfile(path)
+        svg = svg.getroot()
+        svg.moveto(str(x), str(y), scale)
+        return [svg] + toret
+
+
+def svgfig(w, h):
+    w = str(w)
+    h = str(h)
+    return sg.SVGFigure(w, h)
+
+
+def savefig(fig, out):
+    svg_path = os.path.join(fig_dir, '%s.svg' % out)
+    pdf_path = os.path.join(fig_dir, '%s.pdf' % out)
[…]

### 2015-06-28 make.py

@@ -25,8 +25,12 @@ def task_reset():
 
 def task_paper():
     d = os.path.join(root, 'paper')
-    return {'actions': [CmdAction('rubber --pdf paper.tex', cwd=d)],
-            'targets': [os.path.join(d, 'paper.pdf')]}
+    yield {'name': 'main',
+           'actions': [CmdAction('rubber --pdf paper.tex', cwd=d)],
+           'targets': [os.path.join(d, 'paper.pdf')]}
+    yield {'name': 'supplementary',
+           'actions': [CmdAction('rubber --pdf supplementary.tex', cwd=d)],
+           'targets': [os.path.join(d, 'supplementary.pdf')]}
 
 
 def task_compliance():
@@ -68,14 +72,23 @@ def task_benchmarks():
 
 
 def task_plots():
-    yield {'name': 'compliance',
-           'actions': [(fnme.plots.compliance,)]}
     yield {'name': 'accuracy',
            'actions': [(fnme.plots.accuracy,)]}
     yield {'name': 'speed',
            'actions': [(fnme.plots.speed, (True,))]}
     yield {'name': 'speed-np',
            'actions': [(fnme.plots.speed, (False,))]}
+
+
+def task_combine():
+    yield {'name': 'fig1',
+           'actions': [(fnme.plots.fig1,)]}
+    yield {'name': 'fig2',
+           'actions': [(fnme.plots.fig2,)]}
+    yield {'name': 'fig3',
+           'actions': [(fnme.plots.fig3,)]}
+    yield {'name': 'fig4',
+           'actions': [(fnme.plots.fig4,)]}
 
 
 if __name__ == '__main__':

### 2015-06-30 paper/paper.tex
Incorporate feedback from Chris

@@
 including neuromorphic hardware.
-Nengo's separation between frontend and backend
-and rigorous test suite
+Nengo's separation between frontend and backend,
+as well as its rigorous test suite,
 provide standardized comparisons
 between different neuromorphic implementations
-that are geared toward (???) functional performance,
-rather than artificial metrics
-that may or may not contribute to functional performance.
+with respect to functional performance.
 
@@
 build large-scale functional models,
-and contains tests of functional performance;
+and hence its codebase contains
+tests of functional performance;
 it is therefore not intentionally
@@
 the ability to collect benchmarks
-is provided essentially for free.
+is automatically provided to any Nengo backend.
 Finally, since the test suite exists
@@
 
-Other software that do similar things:
+???expand Other software that do similar things:
 many neural simulators exist, and have tests,
@@
 frontend and backend,
-and describe what each backend
+and describe what any backend
 is required to implement.
@@
 used to collect and visualize benchmarks.
-We then list the metrics that will be collected,
-and the backends on which we will collect metrics.
-Finally, we will show and discuss
+We then list the metrics that are collected
+in this paper,
+and the backends on which we collect metrics.
+Finally, we show and discuss
 the results of collecting those metrics
 for each backend.
+
+??? Name backends and give brief intro to them
+in intro. Can then refer to them in other sections.
 
@@
 that validate and store symbolic information
-about the neural model that will be simulated.
-A lot of reasoning can be done at this symbolic level,
-which takes significant burdens off of each backend.
+about the neural model to be simulated.
 
@@
 or as a function of time.
+The \textit{Node} allows the model to
+interact with arbitrary code,
+which can simulate an environment,
+connect the model to a sensor or actuator,
+and so on.
 
@@
 The two objects being connected are the only mandatory parameters;
-the synapse model filtering the connection
-and a function applied to the vector
-communicated across the connection
-can optionally be specified.
+the synapse model filtering the connection,
+a function applied to the vector
+communicated across the connection,
+and one or more learning rules
+can optionally be specified,
+along with several other optional parameters.
 
@@
 can optionally be specified.
+The \textit{Probe} provides the main mechanism
+for data collection during run time.
 
@@
 an ensemble's maximum firing rate defaults to
-a uniform distribution between 200 and 400 Hz,
+a uniform distribution,
 but this could be set to a Gaussian distribution
@@
 contained in the provided network.
-When parts of the model must be
-randomly sampled, the random factors
-should be identical when a network
 In the reference backend,
@@
 and so on.
+When parts of the model are randomly sampled,
+the random factors should become deterministic
+when a network's seed is set.
 
@@
 
-As of version 2.0.1, Nengo's test suite contains 618 tests.
-Some test are unit tests though; how many?
-In all, ??? can be considered ``functional'' tests,
-as they construct a model,
-build a simulator object (see previous sec???),
-run that object,
-and test that the output of that model
+As of version 2.0.1, Nengo's full test suite contains 618 tests.
+Many tests are unit tests
+that ensure the frontend API operates as we expect.
+212 tests construct a simulator instance,
+run the simulator, and test the output of that model
 (as exposed through \texttt{trange}
 and \texttt{data})
-matches the desired output,
-to a certain tolerance.
+and therefore can be considered ``functional'' tests.
+For the remainder of this paper,
+we will focus only on these 212 functional tests.
 
@@
 to these benchmarks,
-it is nearly impossible to create
-completely objective benchmarks.
-??? more or remove last bit
+we believe this is an acceptable consequence
+of the breadth of their application.
 
@@
 See Figure~\ref{???} for a
-concrete example of this.
+concrete example of using the
+\texttt{analytics\_data} fixture.
 
@@
 accuracy and speed are only collected
-for tests that define an an accuracy metric
+for tests that define an accuracy metric
 (i.e., those that use the \texttt{analytics} fixture).
-In this study, we focus on four such tests,
-which we claim are all necessary components
-of large-scale cognitive brain models,
-though they are by no means a sufficient set
-for all complex cognitive behaviors.
+In this study, we focus on four such tests
+that address central functioning aspects
+of a wide variety of large-scale briain models
+(see \cite{NEF or SPA book or both?}).
 
@@
 in the activity of spiking neurons.
+
+??? include code for this example, as an appendix?
 
@@
 
-\paragraph{4. Neurogrid software (\texttt{nengo\_brainstorm}).}
-The Neurogrid backend is a software implementation
-of a potential neuromorphic chip being developed
-by Boahen et al. \cite{???}.
-It does not aim for speed;
+\paragraph{4. Brainstorm software (\texttt{nengo\_brainstorm}).}
+The Brainstorm backend is a software implementation
+of a new neuromorphic chip
+based partly on Neurogrid \cite{???}
+currently in development
+by the Brain in Silicon lab
+at Stanford University.
+The software backend does not aim for speed;
 instead, it attempts to emulate the hardware
@@
 developed by Furber et al. \cite{???}.
-In contrast to the Neurogrid backend,
+In contrast to the Brainstorm backend,
 this backend targets physical neuromorphic hardware,
@@
 of being simple but not necessarily feature-rich.
-The Neurogrid backend is the least compliant,
+The Brainstorm backend is the least compliant,
 but it is still an early experimental test bed;
 this is not necessarily indicative of the
-final Neurogrid hardware backend being
+final Brainstorm hardware backend being
 less compliant than other backends.
@@
 The reference and OpenCL backends perform well here,
-as do the distilled and Neurogrid backends.
+as do the distilled and Brainstorm backends.
 The SpiNNaker backend performs well in most cases,
@@
 (e.g., the chained communication channel model).
-The distilled and Neurogrid backends---which
+The distilled and Brainstorm backends---which
 have a very similar build process---become
@@
 though it builds the largest model faster than
-the distilled and Neurogrid backends.
+the distilled and Brainstorm backends.
 
@@
 the basal ganglia sequence.
-In this model, the distilled and Neurogrid backends
+In this model, the distilled and Brainstorm backends
 performed very poorly
@@
 Above and beyond the benchmarking results,
-however, we assert that the primary contribution
+however, we believe that the primary contribution
 of this study is to provide evidence that Nengo
@@
 While this is similar to the goal
-of similar projects, such a PyNN \cite{???},
+of other projects, such a PyNN \cite{???},
 Nengo is unique in focusing on large-scale simulations,
@@
 to make functionally interesting large-scale models.
-These models are typically build and tested
+These models are typically built and tested
 in the reference backend,
@@
  OpenCL (\texttt{nengo\_ocl}) & 187 & 88.2\% \\
- Neurogrid (\texttt{nengo\_brainstorm}) & 107 & 50.4\% \\\botrule
+ Brainstorm (\texttt{nengo\_brainstorm}) & 107 & 50.4\% \\\botrule
 \end{tabular}}{}
 \end{table}
+
+% ??? figure out these colors!
+
+% ??? Add A B C etc labels to figures
 
@@
          time to transition from one action to the next. The model is run
-         for four second, allowing for approximately 90 transitions, depending
+         for four seconds, allowing for approximately 90 transitions, depending
          on the transition time. The box shows the median and

### 2015-06-30 paper/paper.tex
Incorporate feedback from Andrew

@@
 \paragraph{5. SpiNNaker hardware (\texttt{nengo\_spinnaker}).}
-The SpiNNaker backend targets
-the eponymous neuromorphic hardware
-developed by Furber et al. \cite{???}.
+The SpiNNaker backend \cite{Mundy et al., 2015 in press}
+targets the eponymous neuromorphic hardware
+developed by Furber et al. \cite{10.1109/JPROC.2014.2304638}.
 In contrast to the Brainstorm backend,
@@
 is to run in real-time even if it is possible to run faster.
-(??? Andrew is this true?)
+(??? confirmed: always runs at real time)
 The most important result is for the largest model,
@@
 
+??? For SpiNNaker, place and route is most costly part of
+preparing a sim, not necessarily interfacing with hardware
+
+??? Add something about overhead; calling ``run'' still
+results in writing data to the board. Actual simulation
+occurs in real-time for SpiNNaker; can safely interact
+with robotics, neuromorphic hardware, etc
+
 Despite the fast run times for
@@
 of the slowdown.
+
 Similarly, we should investigate
@@
 (e.g., in the basal ganglia sequence model).
+??? Product difference might be due to different saturation
+properties in SpiNNaker ???
 
@@
 \end{table}
+
+% ??? Make color palette grey-scale friendly
 
@@
 \end{figure}
+
+% ??? Remove left plot
+
+% ??? Make middle a stem plot
 

### 2015-06-30 paper/paper.tex
Incorporate feedback from Terry

@@
 Nengo's separation between frontend and backend,
-as well as its rigorous test suite,
+as well as its extensive test suite,
 provide standardized comparisons
@@
 The frontend exposes a modelling interface
-that uses Python and NumPy \cite{???}
-to define models concisely.
+that uses Python to define models concisely.
 Backends are responsible for transforming
@@
 about the neural model to be simulated.
+All neural models defined with Nengo
+are built with these five building blocks,
+including Spaun, a model that performs
+eight cognitive tasks with 2.5 million neurons
+that use visual input to produce motor output
+\cite{spaun}.
+A backend only needs to be aware of these
+five objects to run Nengo models,
+and therefore run the benchmarks discussed in this paper.
 
 The primary abstraction in Nengo is the \textit{Ensemble},
-which is a group of neurons (or neuron-like functions)
-that collectively represent a time-varying vector of numbers.
+which is a group of neurons.
+The activity of these neurons
+forms a distributed representation of a numerical vector;
+for example, a group of 100 neurons might represent
+a three-dimensional vector,
+and as that vector changes,
+the pattern of neural activity
+will change accordingly.
 Two parameters are mandatory: the number of neurons,
@@
 
-The \textit{Node} plays a similar role of representing
-time-varying vectors of numbers,
-but does so directly, without simulating a group of neurons.
-As such, the only mandatory parameter
-is what vector should be represented;
-this can be specified as a constant vector,
-or as a function of time.
-The \textit{Node} allows the model to
-interact with arbitrary code,
-which can simulate an environment,
-connect the model to a sensor or actuator,
-and so on.
+The \textit{Node} provides a structure for all
+non-neural aspects of a model.
+\textit{Nodes} can provide input to a system,
+collect output values,
+interface with physical sensors and motors,
+or provide any other computation needed in a mode.
+In the case of the benchmarks presented in this paper,
+\textit{Nodes} are used to provide input signals
+to \textit{Ensembles}.
 
@@
 make up the public interface
-that Nengo tests expect from backends;
-it is an example
-of the adapter pattern \cite{???}. % Maybe lose?
+that Nengo tests expect from backends.
 While the existence of the methods
@@
 While this introduces some subjectivity
-to these benchmarks,
+to testing,
 we believe this is an acceptable consequence
 of the breadth of their application.
+When adapting these functional tests for benchmarking,
+we record the actual accuracy rather than
+ensuring that it is within some tolerances.
 
@@
 (see \cite{NEF or SPA book or both?}).
+??? Each test has several parameters
+that can be varied
+in order to benchmark extreme cases
+(e.g., representing many dimensions
+with few neurons).
+We test each model with parameters
+typically used in large-scale models,
+but make these parameterized models
+available at \url{???github url}
+for those who want to explore extreme cases.
 
@@
 
+??? Also include appendix with version numbers used?
+
 \paragraph{2. Two-dimensional product.}
@@
 in large-scale models;
-it is the primary operation used to
-bind semantic pointers, for example
-\cite{???}.
+it is the primary operation needed to support
+symbol-like processing using neuron-like elements,
+for example \cite{spaun or SPA book}.
 
@@
 \paragraph{4. Basal Ganglia sequence.}
-In this model, comprised of 4900 LIF neurons,
-a basal ganglia is created (as described in \cite{???})
-that runs through a fixed sequence of actions.
-Stewart et al. \cite{???} have showed that
-these simple action sequences should
-switch at a rate of ???.
-This model tests that each backend can
-build this basal ganglia model,
-which is commonly used for action selection,
-and that actions can be selected at the
-hypothesized rate.
+In this model, brain structures
+known collectively as the basal ganglia
+are contructed from 4900 LIF neurons,
+organized such that they iterate
+through a repeating set of actions.
+This model has been used to investigate
+action selection and learning \cite{stewart, bekolay}
+and the switching time between actions
+has been closely mapped to human decision making
+\cite{stewart 2010}.
+This benchmark tests the ability
+to construct this model,
+and evaluates the time needed
+to transition between actions.
 
@@
 Therefore, the distilled backend is easier to read
-and suitable for learning about Nengo
-or as a starting point for new backends.
+and suitable for learning about Nengo,
+but is expected to be slower in terms of run time.
 

### 2015-07-01 paper/paper.tex
Full edit by Trevor
Filled in most sections now (except stuff at the end).
Ready to rerun benchmarks and regenerate plots.

@@
 \linenumbers
+\usepackage{inconsolata}
+\usepackage{listings}
+\lstset{language=Python}
+\lstset{basicstyle=\ttfamily,breaklines=true}
 
@@
 
-  Abstract
+  Nengo is a software package for designing and simulating
+  large-scale neural models.
+  Nengo is architected such that the same Nengo model
+  can be simulated on any of several
+  Nengo backends with few to no modifications.
+  Backends translate a model to specific platforms,
+  which include GPUs and neuromorphic hardware.
+  Nengo also contains a large test suite
+  that can be run with any backend
+  and focuses primarily on functional performance.
+  We propose that Nengo's large test suite
+  can be used to benchmark neuromorphic hardware's
+  functional performance and speed simulating
+  in an efficient, unbiased, and future-proof manner.
+  We implement four benchmark models and show that
+  Nengo can collect several benchmark metrics
+  that identify situations in which
+  some backends perform differently
+  or significantly faster than others.
 
@@
   % 5--8 keywords
-  \keyFont{ \section{Keywords:}  }
+  \keyFont{ \section{Keywords:} Nengo, benchmarking, neuromorphic hardware }
 \end{abstract}
@@
 
-???expand Other software that do similar things:
-many neural simulators exist, and have tests,
-but don't have the high-level API
-that Nengo has.
-On the other hand, some simulators
-have high-level APIs
-(Topographica?) but a) aren't functional
-and b) can't use diverse backends.
-
-??? In the subsequent sections,
+Several Nengo backends exist or are in active development.
+In this paper, we will run benchmarks
+on five backends.
+The reference, distilled, and Brainstorm backends
+run on general purpose computers,
+and focus on aspects other than speed.
+The OpenCL backend aims to be a fast backend
+that still works on general purpose computers,
+but can also take advantage of
+graphical processing units (GPUs).
+The SpiNNaker backend uses
+SpiNNaker neuromorphic hardware to
+simulate models in real time
+for natural interaction with
+physical sensors and actuators.
+
+In the subsequent sections,
 we detail the architecture of Nengo's
@@
 is required to implement.
-We explain Nengo's testing framework,
-including descriptions of the testing fixtures
+We describe Nengo's testing framework,
+including explanations of the testing fixtures
 used to collect and visualize benchmarks.
-We then list the metrics that are collected
-in this paper,
-and the backends on which we collect metrics.
+We then list the metrics
+that are collected in this paper,
+and give further details on the backends benchmarked.
 Finally, we show and discuss
@@
 
-??? Name backends and give brief intro to them
-in intro. Can then refer to them in other sections.
-
 \section{Background}
 
-There are two key features of Nengo 2.0
+There are two key features of Nengo
+(starting from version 2.0)
 that enable rapid benchmarking of neuromorphic systems.
@@
 Nengo can be used to create models that solve cognitive tasks.
-This test suite makes ample use of test fixtures
+The test suite makes ample use of test fixtures
 to enable data collection while testing on arbitrary backends.
@@
 Nengo has a strict separation between
-the frontend and backend.
+frontend and backend.
 The frontend exposes a modelling interface
@@
 that use visual input to produce motor output
-\cite{spaun}.
+\cite{eliasmith2012}.
 A backend only needs to be aware of these
@@
 
-The \textit{Probe} denotes that a particular
+The \textit{Probe} provides the main mechanism
+for data collection during run time
+by denoting that a particular
 quantity in the simulation should be recorded
@@
 can optionally be specified.
-The \textit{Probe} provides the main mechanism
-for data collection during run time.
 
@@
 for the four other objects.
-This results in much shorter and less error-prone
+This results in shorter and less error-prone
 model creation scripts.
@@
 express a functional network
-with ??? neurons and ??? connections
-(representing ??? connection weights)
-in ??? lines of code can be seen
-in Figure~\ref{???}.
+with 500 neurons and 6 connections
+(representing 50,000 connection weights
+and 100 direct current injection sites)
+in under 20 lines of code
+can be seen in Appendix~\ref{App:01}.
 
 \subsubsection{Backend requirements}
+\label{Sec:Backend}
 
@@
 that Nengo tests expect from backends.
-While the existence of the methods
+While the existence of these methods
 and attribute are necessary
 for every Nengo model,
-they are not sufficient;
 backends are not required
@@
 Backends are responsible for informing
-the user when model cannot be implemented
+the user when a model cannot be implemented
 on that backend.
-The compliance metric (see section ???)
-explicitly tracks the details of what
+The compliance metric (see Section~\ref{Sec:Metrics})
+explicitly tracks what
 types of models can be implemented
@@
 The details of how each backend
-implements high-level frontend model
+implements high-level frontend models
 are out of the scope of this paper.
@@
 Many tests are unit tests
-that ensure the frontend API operates as we expect.
+that ensure the frontend API operates as expected.
 212 tests construct a simulator instance,
@@
 Nengo's test suite employs the \texttt{pytest}
-testing framework \cite{???}.
+testing framework \footnote{Available at \url{http://pytest.org/}.}.
 \texttt{pytest} enables
@@
 and run for any test that might use it.
-The example script in Figure~\ref{???}
+The example script in Appendix~\ref{App:01}
 demonstrates how these fixtures
@@
 allows for tests to be run with multiple backends.
-As detailed in section ???,
+As detailed in Section~\ref{Sec:Backend},
 each backend must expose a simulator class
@@
 in this paper are generated.
-The \texttt{plt} fixture exposes the Matplotlib \cite{???}
+The \texttt{plt} fixture exposes the Matplotlib \cite{hunter2007}
 \texttt{pyplot} interface to a test function.
-These functions can then analyze and plot
+Test functions can then analyze and plot
 the data generated in a simulation
@@
 with the \texttt{analytics} fixture.
-See Figure~\ref{???} for a
+See Appendix~\ref{App:01} for a
 concrete example of using the
@@
 \subsection{Metrics collected}
+\label{Sec:Metrics}
 
@@
 for this reason, a backend that has relatively
-low compliance can still be very useful
+low compliance can still be useful
 in many situations.
@@
 
+It should be noted that
+during a \texttt{run} call,
+each backend incurs some overhead
+to manage the simulation in addition
+to actually moving the simulation forward.
+The amount of overhead depends
+on the backend; those on specific hardware platforms
+(like the SpiNNaker and OpenCL backends)
+are likely to incur more overhead
+than those on general purpose platforms.
+However, we include the overhead in
+our speed benchmarking because
+it is not possible to distinguish
+overhead from actual run time
+in a backend-agnostic way.
+
 \subsection{Test models}
@@
 of a wide variety of large-scale briain models
-(see \cite{NEF or SPA book or both?}).
-??? Each test has several parameters
+(see \cite{eliasmith2003a,eliasmith2013}).
+
+Each test has several parameters
 that can be varied
 in order to benchmark extreme cases
-(e.g., representing many dimensions
-with few neurons).
+(see Appendix~\ref{App:01} for examples).
 We test each model with parameters
@@
 but make these parameterized models
-available at \url{???github url}
+available at \url{https://github.com/tbekolay/fnme2015}
 for those who want to explore extreme cases.
@@
 
-??? include code for this example, as an appendix?
-
-??? Also include appendix with version numbers used?
-
 \paragraph{2. Two-dimensional product.}
@@
 we use a space-filling curve
-(the Hilbert curve \cite{???})
+(the Hilbert curve \cite{hilbert1891})
 as the input signal to ensure that
@@
 symbol-like processing using neuron-like elements,
-for example \cite{spaun or SPA book}.
+for example \cite{eliasmith2013}.
 
@@
 This model has been used to investigate
-action selection and learning \cite{stewart, bekolay}
+action selection and learning \cite{stewart2012a}
 and the switching time between actions
 has been closely mapped to human decision making
-\cite{stewart 2010}.
+\cite{stewart2010}.
 This benchmark tests the ability
@@
 on any general purpose computer
-by using NumPy \cite{???}
+by using NumPy \cite{vanderwalt2011}
 for fast vectorized computations.
@@
 The OpenCL backend uses the Open Computing Language
-(OpenCL; \cite{???})
+(OpenCL; \cite{stone2010})
 to run Nengo models on many different computing devices,
@@
 of a new neuromorphic chip
-based partly on Neurogrid \cite{???}
+based partly on Neurogrid \cite{benjamin2014}
 currently in development
 by the Brain in Silicon lab
-at Stanford University.
+at Stanford University\footnote{
+  Some details available at \url{http://brainstorm.stanford.edu/projects/}.}.
 The software backend does not aim for speed;
@@
 \paragraph{5. SpiNNaker hardware (\texttt{nengo\_spinnaker}).}
-The SpiNNaker backend \cite{Mundy et al., 2015 in press}
+The SpiNNaker backend \cite{mundyinpress}
 targets the eponymous neuromorphic hardware
-developed by Furber et al. \cite{10.1109/JPROC.2014.2304638}.
+developed by \citeauthor{furber2014}.
 In contrast to the Brainstorm backend,
@@
 
-\subsection{Hardware used for running benchmarks}
-
-??? ask Xuan
-
-SpiNN-5 board
+\subsection{Benchmarking environment}
+
+All benchmarks were run on a server
+running Debian unstable.
+The server was configured with
+two Intel Xeon E5-2650 CPUs
+clocked at 2.00GHz,
+four Nvidia Tesla C2075 GPUs,
+and 64 GB of RAM.
+A single 48-chip SpiNN-5 board
+was connected through
+a 1 GB ethernet port on
+the Supermicro X9DRG-QF motherboard.
+
+The versions of software
+used for benchmarking can be found in
+Supplementary Table~1.
 
@@
 perform well, the SpiNNaker backend
-performs significantly worse than the
+performs statistically worse than the
 other four backends.
@@
 as do the distilled and Brainstorm backends.
-The SpiNNaker backend performs well in most cases,
-but some instances of the model
-are significantly less accurate
-than the majority of instances.
+??? revisit with new results
+%% The SpiNNaker backend performs well in most cases,
+%% but some instances of the model
+%% are signifless accurate
+%% than the majority of instances.
 
@@
 around 43 milliseconds, which matches
-the results from Stewart et al. 2010 \cite{???}
+the results from \citeauthor{stewart2010}
 for simple actions.
@@
 time reported for complex actions.
+??? Run again with passthrough nodes removed
+and make figure
 
@@
 The SpiNNaker backend incurs an unavoidable cost
-in setting up the hardware,
+in setting up the hardware
+(determining the placement of computational resources,
+and generating routes to connect resouces),
 though it builds the largest model faster than
@@
 SpiNNaker, on the other hand, is slower than other backends
-for these models, but only because its goal
+for these models, because its goal
 is to run in real-time even if it is possible to run faster.
-(??? confirmed: always runs at real time)
 The most important result is for the largest model,
@@
 on this moderately-sized model.
-
-??? For SpiNNaker, place and route is most costly part of
-preparing a sim, not necessarily interfacing with hardware
-
-??? Add something about overhead; calling ``run'' still
-results in writing data to the board. Actual simulation
-occurs in real-time for SpiNNaker; can safely interact
-with robotics, neuromorphic hardware, etc
-
-Despite the fast run times for
-the OpenCL and SpiNNaker backends,
-we also investigated the possibility
-that probes were slowing these backend down,
-since probes require moving data from
-their native platform (GPU or SpiNNaker board)
-to the CPU. However, we found that
+Since the SpiNNaker board always runs at real-time,
+this means that around one-third of the time taken
+for the \texttt{run} call is overhead.
+
+Other backends also incur overhead,
+especially when data is recorded
+through probes.
+We investigated the possibility
+that the overhead involved in probes
+dominated the actual run time for some backends.
+However, we found that
 removing probes from these models
-made almost no impact on their run time
-(see Figure~\ref{Fig:07}).
+made very little impact on
+the total time taken in a \texttt{run} call
+(see Supplementary Figure~1).
 
@@
 of the slowdown.
-
 Similarly, we should investigate
 the model instances in which the SpiNNaker backend
-is less accurate (e.g., in the controlled oscillator model)
-or different from other backends
-(e.g., in the basal ganglia sequence model).
-??? Product difference might be due to different saturation
-properties in SpiNNaker ???
+differs from other backends
+in the product model.
 
@@
 While this is similar to the goal
-of other projects, such a PyNN \cite{???},
-Nengo is unique in focusing on large-scale simulations,
+of other projects, most notably PyNN \cite{davison2008},
+Nengo is unique in focusing on
+large-scale functional simulations,
 rather than attempting to support
 detailed single-neuron models
-(though this capability is still possible in Nengo;
-see \cite{???}).
+(though this capability is still possible in Nengo).
+Topographica \cite{bednar2009} plays a similar role,
+in that it can interact with multiple neural simulators
+with a high-level API, but its API focuses specifically
+on models of topographic maps
+and other sensory pathways,
+rather than focusing on function and dynamics.
 
@@
 
-???concluding remarks
+In summary, we have implemented
+four benchmark models using the same
+testing framework used for Nengo's test suite,
+and gathered benchmark results
+for five backends,
+including an OpenCL backend that targets GPUs
+and a backend that targets
+SpiNNaker neuromorphic hardware.
+All five backends were able to implement
+the models accurately,
+with the OpenCL and SpiNNaker backends
+simulating the largest model much faster
+than the reference backend.
+We believe that the these benchmarks
+can be easily expanded upon
+to develop a suite of benchmarks
+that can be run by any neuromorphic hardware
+or neural simulator
+with an associated Nengo backend.
+Running these benchmarks in a common environment
+and cleanly visualizing the results
+could catalyze the development of
+neural systems that implement
+large-scale functional models
+efficiently and accurately.
 
@@
 
+\clearpage
+\appendix
+
+\section{Chained communication channel model}
+\label{App:01}
+
+\begin{lstlisting}
+import numpy as np
+import nengo
+from nengo.utils.numpy import rmse
+
+def test_cchannelchain(Simulator, analytics, plt, rng, seed):
+    # Parameters that can be varied to investigate extreme cases
+    dims = 2
+    layers = 5
+    n_neurons = 100
+    synapse = nengo.Lowpass(0.01)
+
+    with nengo.Network(seed=seed) as model:
+        hypersphere = nengo.dists.UniformHypersphere()
+        value = hypersphere.sample(dims, 1, rng=rng).ravel()
+        stim = nengo.Node(value)
+
+        ens = [nengo.Ensemble(n_neurons, dimensions=dims)
+               for _ in range(layers)]
+
+        nengo.Connection(stim, ens[0])
+        for i in range(layers - 1):
+            nengo.Connection(ens[i], ens[i+1], synapse=synapse)
+
+        p_input = nengo.Probe(stim)
+        p_outputs = [nengo.Probe(ens[i], synapse=synapse)
+                     for i in range(layers)]
+
+    sim = Simulator(model)
+    sim.run(0.5)
+
+    for p_output in p_outputs:
+        plt.plot(sim.trange(), sim.data[p_output])
+    plt.plot(sim.trange(), sim.data[p_input], color='k', linewidth=1)
+    plt.ylabel('Decoded output')
+    plt.xlabel('Time (s)')
+
+    last = p_outputs[-1]
+    decoding_rmse = rmse(value, sim.data[last][sim.trange() > 0.4]
+    analytics.add_data('rmse', decoding_rmse)
+
+def test_compare_cchannelchain(analytics_data, plt):
+    rmses = [d['rmse'] for d in analytics_data]
+    plt.bar(np.arange(len(rmses)), rmses, align='center')
+    plt.ylabel("RMSE")
+\end{lstlisting}
+
 \end{document}

### 2015-07-01 paper/supplementary.tex
Full edit by Trevor
Filled in most sections now (except stuff at the end).
Ready to rerun benchmarks and regenerate plots.

@@
 
+\begin{table}[!ht]
+\textbf{\refstepcounter{table}\label{Tab:01} Supplementary Table \arabic{table}.}{
+  Software versions used for benchmarking.
+  The PyPI name is the unique identifier used for installing the Python package
+  through the Python Package Index (PyPI). Packages can be found by
+  visiting \url{https://pypi.python.org/pypi/<PyPI name>}.}
+
+\processtable{ }
+{\begin{tabular}{lcc}\toprule
+ Package & PyPI name & Version number\\\midrule
+ Nengo & \texttt{nengo} & Development version, commit \texttt{7d2d24145} \\
+ Distilled backend & \texttt{nengo\_distilled} & 0.1.0 \\
+ OpenCL backend & \texttt{nengo\_ocl} & 0.1.0 \\
+ Brainstorm backend & Not available on PyPI & Development version, commit \texttt{ac3cfa708} \\
+ SpiNNaker backend & \texttt{nengo\_spinnaker} & 0.2.3 \\
+ NumPy & \texttt{numpy} & 1.8.1 \\\botrule
+\end{tabular}}{}
+\end{table}
+
 \begin{figure}[!ht]

### 2015-07-08 fnme/benchmarks.py
Better benchmarking and plots
Incorporated all the feedback on the plots and the benchmarking.
Should be ready for round 2 (which should be the final round)
of benchmarks!

Highlights:
- Use 'cubehelix' colors instead of Seaborn defaults. Reasoning:
  luminance changes so these should print out such that you can
  differentiate them, and they should still be colorblind friendly.
- `outfile` now gives a file pointer, instead of a path, so that
  we can make it a tempfile when not profiling speed
- Now possible to not profile speed (used in the `plots` task
  to run the benchmarks for plots rath

@@ -24,10 +24,11 @@ try:
 except ImportError:
     pass
 
-from .plots import setup, prettify, onecolumn, twocolumn
+from .plots import setup, onecolumn
 from .utils import HilbertCurve
 
-colors = sns.color_palette()
+colors = sns.color_palette("cubehelix", n_colors=6)
+
 
 # --- 1. Communication channel chain
 def test_cchannelchain(Simulator, plt, rng, seed, outfile, probes):
@@ -57,23 +58,29 @@ def test_cchannelchain(Simulator, plt, rng, seed, outfile, probes):
     sim.run(0.5)
 
     if probes:
-        setup(figsize=(onecolumn * 2, 4.0))
-        for i, p_output in enumerate(p_outputs):
-            plt.plot(sim.trange(), sim.data[p_output],
-                     c=colors[i % len(colors)])
-        plt.plot(sim.trange(), sim.data[p_input], c='k', lw=1)
-        plt.yticks((-0.6, 0, 0.6))
-        plt.xticks((0, 0.05, 0.1))
-        plt.ylabel('Decoded output')
-        plt.xlabel('Time (s)')
-        plt.saveas = 'results-1.svg'
+        if type(plt).__name__ != 'Mock':
+            setup(figsize=(onecolumn * 2, 4.0))
+            colors = sns.cubehelix_palette(5)
+            lines = []
+            for i, p_output in enumerate(p_outputs):
+                l = plt.plot(sim.trange(), sim.data[p_output],
+                             c=colors[i % len(colors)])
+                lines.append(l[0])
+            plt.legend(lines, ["Ensemble %d" % i for i in range(1, 6)], loc='best')
+            plt.plot(sim.trange(), sim.data[p_input], c='k', lw=1)
+            plt.xlim(right=0.12)
+            plt.yticks((-0.5, 0, 0.5))
+            plt.xticks((0, 0.05, 0.1))
+            plt.ylabel('Decoded output')
+            plt.xlabel('Time (s)')
+            sns.despine()
+            plt.saveas = 'results-1.svg'
 
-        with open(outfile, 'a') as outf:
-            outf.write('"n_neurons": %d,\n' % sum(
-                e.n_neurons for e in model.all_ensembles))
-            outf.write('"simtime": 0.5,\n')
-            outf.write('"rmse": %f,\n' % (
-                rmse(sim.data[p_outputs[-1]][sim.trange() > 0.4], value)))
+        outfile.write('"n_neurons": %d,\n' % sum(
[…]

### 2015-07-08 fnme/conftest.py

@@ -1,6 +1,7 @@
 """py.test stuff that runs the benchmarks."""
 
 import importlib
+import tempfile
 
 import pytest
 
@@ -55,6 +56,7 @@ def add_speed_profiling(Simulator):
 _Simulator = None
 outdir = None
 _probes = True
+_profile = True
 
 
 def pytest_configure(config):
@@ -62,7 +64,11 @@ def pytest_configure(config):
     if not config.getoption('simulator'):
         raise ValueError("Please provide a simulator to benchmark.")
     _Simulator = load_class(config.getoption('simulator')[0])
-    add_speed_profiling(_Simulator)
+
+    global profile
+    profile = config.getoption('noprofile')
+    if profile:
+        add_speed_profiling(_Simulator)
 
     if config.getoption('seed'):
         # Change up the seed to get new networks
@@ -96,18 +102,22 @@ def load_class(fully_qualified_name):
 def outfile(request, seed):
     path = os.path.join(outdir, "%s-%s.txt" % (
         request.function.__name__, nengo.tests.conftest.test_seed))
-    with open(path, 'w') as outf:
+    if profile:
+        outf = open(path, 'w')
         outf.write('{\n')
-    return path
+    else:
+        outf = tempfile.TemporaryFile()
+    return outf
 
 
 @pytest.fixture
 def Simulator(request, outfile):
     def save_profiling():
-        with open(outfile, 'a') as outf:
-            outf.write('"buildtime": %f,\n' % _Simulator.build_time)
-            outf.write('"runtime": %f\n}\n' % _Simulator.run_time)
+        outfile.write('"buildtime": %f,\n' % _Simulator.build_time)
+        outfile.write('"runtime": %f\n}\n' % _Simulator.run_time)
         del _Simulator.build_time
         del _Simulator.run_time
-    request.addfinalizer(save_profiling)
+    request.addfinalizer(outfile.close)
+    if profile:
+        request.addfinalizer(save_profiling)
     return _Simulator

### 2015-07-08 fnme/options.py

@@ -1,5 +1,6 @@
 from nengo.tests.options import pytest_addoption as _nengooptions
 
+
 def pytest_addoption(parser):
     # Make simulator passable
     parser.addoption('--simulator', nargs=1, type=str, default=None,
@@ -8,5 +9,7 @@ def pytest_addoption(parser):
                      help='Specify the global test seed.')
     parser.addoption('--noprobes', action='store_false', default=True,
                      help='Disable probing.')
+    parser.addoption('--noprofile', action='store_false', default=True,
+                     help='Disable speed profiling.')
 
     _nengooptions(parser)

### 2015-07-08 fnme/plots.py

@@ -8,7 +8,7 @@ import matplotlib.pyplot as plt
 import pandas as pd
 import seaborn as sns
 import svgutils.transform as sg
-from scipy import stats
+from mpl_toolkits.axes_grid1.inset_locator import mark_inset, zoomed_inset_axes
 
 root = os.path.dirname(__file__)
 plots_dir = os.path.realpath(os.path.join(root, os.pardir, 'plots'))
@@ -34,7 +34,7 @@ class RectElement(sg.FigureElement):
         sg.FigureElement.__init__(self, rect)
 
 
-def el(char, path, x, y, scale=1, offset=(10, 30)):
+def el(char, path, x, y, scale=1, offset=(4, 24)):
     toret = []
     if char is not None:
         toret.append(RectElement(x + offset[0], y + offset[1]))
@@ -44,11 +44,12 @@ def el(char, path, x, y, scale=1, offset=(10, 30)):
                                     size=24,
                                     weight='bold',
                                     font='Arial'))
-    if path.endswith(".svg"):
+    if path is not None and path.endswith(".svg"):
         svg = sg.fromfile(path)
         svg = svg.getroot()
         svg.moveto(str(x), str(y), scale)
-        return [svg] + toret
+        toret = [svg] + toret
+    return toret
 
 
 def svgfig(w, h):
@@ -59,32 +60,36 @@ def svgfig(w, h):
 
 def savefig(fig, out):
     svg_path = os.path.join(fig_dir, '%s.svg' % out)
-    pdf_path = os.path.join(fig_dir, '%s.pdf' % out)
-    # eps_path = os.path.join(fig_dir, '%s.eps' % out)
     fig.save(svg_path)
+    svg2other(out)
+
+
+def svg2other(out):
+    svg_path = os.path.join(fig_dir, '%s.svg' % out)
+    pdf_path = os.path.join(fig_dir, '%s.pdf' % out)
+    eps_path = os.path.join(fig_dir, '%s.eps' % out)
     subprocess.call([inkscape, '--export-pdf=%s' % pdf_path, svg_path])
-    # subprocess.call([inkscape, '--export-text-to-path',
-    #                  '--export-eps=%s' % eps_path, svg_path])
+    subprocess.call([inkscape, '--export-text-to-path',
+                     '--export-eps=%s' % eps_path, svg_path])
 
 
-def setup(figsize=None):
+def setup(figsize=None, palette_args=None):
[…]

### 2015-07-08 make.py

@@ -72,6 +72,11 @@ def task_benchmarks():
 
 
 def task_plots():
+    yield {'name': 'models',
+           'actions': [CmdAction(
+               'py.test -p fnme.options --simulator nengo.Simulator '
+               '--seed 5 --plot plots --noprofile -- fnme/benchmarks.py',
+               cwd=root)]}
     yield {'name': 'accuracy',
            'actions': [(fnme.plots.accuracy,)]}
     yield {'name': 'speed',

### 2015-07-08 paper/paper.tex
Add paragraph on small / short models
In response to Andrew's comment.

@@
 however, which operated at around 1.5 times real-time
-on this moderately-sized model.
+on this moderately-sized model. (??? revisit with new results)
 Since the SpiNNaker board always runs at real-time,
@@
 The most important finding from these benchmarks
-is that specialized hardware (including GPUs)
-can result in significantly faster run times
-for certain models,
+is that significant speedups can be gained by
+running models on specialized hardware and GPUs,
 with little to no cost in accuracy.
@@
 Similarly, we should investigate
-the model instances in which the SpiNNaker backend
-differs from other backends
-in the product model.
+the product model instances
+in which the SpiNNaker backend
+differs from other backends.
+
+It should be noted that although there are clear
+relative speed differences between backends,
+these models are very small---each would only
+be a small component of a larger model.
+Spaun, for example, includes multiple copies
+or larger versions of all four of the models
+benchmarked here.
+Additionally, we run them
+for very small amounts of time---the longest
+simulation runs for 10 simulated seconds.
+Real models run for longer amounts of time
+to gather data comparable to those gathered
+in neuroscientific experiments.
+However, we expect that the results
+would be similar, though exaggerated,
+in larger models run for longer amount of time.
+The distilled and brainstorms backends would
+perform slowly, the OpenCL backend should
+run faster than the reference backend,
+and SpiNNaker will continue to run at real-time.
 
@@
 \end{table}
-
-% ??? Make color palette grey-scale friendly
-
-% ??? figure out these colors!
-
-% ??? Add A B C etc labels to figures
 

### 2015-07-09 fnme/benchmarks.py
Different method for removing passthrough nodes
I think these are essentially equivalent, but just in case...

@@ -15,6 +15,7 @@ import numpy as np
 import seaborn as sns
 
 import nengo
+import nengo.utils.builder
 import nengo.spa as spa
 from nengo.utils.numpy import rmse
 from nengo.utils.functions import piecewise
@@ -66,7 +67,8 @@ def test_cchannelchain(Simulator, plt, rng, seed, outfile, probes):
                 l = plt.plot(sim.trange(), sim.data[p_output],
                              c=colors[i % len(colors)])
                 lines.append(l[0])
-            plt.legend(lines, ["Ensemble %d" % i for i in range(1, 6)], loc='best')
+            plt.legend(lines, ["Ensemble %d" % i for i in range(1, 6)],
+                       loc='best')
             plt.plot(sim.trange(), sim.data[p_input], c='k', lw=1)
             plt.xlim(right=0.12)
             plt.yticks((-0.5, 0, 0.5))
@@ -261,6 +263,47 @@ def test_controlledoscillator(Simulator, plt, rng, seed, outfile, probes):
 # The value for the benchmark is a measure of the time taken to go from one
 # item in the sequence to the next.  We compute both a mean and a standard
 # deviation for this timing measure.
+def remove_passthrough_nodes(network):
+    m = nengo.Network()
+
+    conns = list(network.all_connections)
+    inputs, outputs = nengo.utils.builder.find_all_io(conns)
+
+    keep_nodes = []
+    for probe in network.all_probes:
+        if isinstance(probe.target, nengo.Node):
+            if probe.target.output is None:
+                keep_nodes.append(probe.target)
+
+    with m:
+        for ens in network.all_ensembles:
+            m.add(ens)
+        for node in network.all_nodes:
+            if node.output is None and node not in keep_nodes:
+                conns_in = inputs[node]
+                conns_out = outputs[node]
+                for c in conns_in:
+                    conns.remove(c)
+                    outputs[c.pre_obj].remove(c)
+                for c in conns_out:
+                    conns.remove(c)
+                    inputs[c.post_obj].remove(c)
+
+                for c_in in conns_in:
+                    for c_out in conns_out:
+                        c = nengo.utils.builder._create_replacement_connection(
+                            c_in, c_out)
+                        if c is not None:
+                            conns.append(c)
+                            outputs[c.pre_obj].append(c)
+                            inputs[c.post_obj].append(c)
[…]

### 2015-07-28 paper/paper.tex
Final edits; finished second draft

@@
 that use visual input to produce motor output
-\cite{eliasmith2012}.
+\citep{eliasmith2012}.
 A backend only needs to be aware of these
@@
 in this paper are generated.
-The \texttt{plt} fixture exposes the Matplotlib \cite{hunter2007}
+The \texttt{plt} fixture exposes the Matplotlib \citep{hunter2007}
 \texttt{pyplot} interface to a test function.
@@
 of a wide variety of large-scale briain models
-(see \cite{eliasmith2003a,eliasmith2013}).
+(see \citealp{eliasmith2003a,eliasmith2013}).
 
@@
 we use a space-filling curve
-(the Hilbert curve \cite{hilbert1891})
+(the Hilbert curve; \citealp{hilbert1891})
 as the input signal to ensure that
@@
 symbol-like processing using neuron-like elements,
-for example \cite{eliasmith2013}.
+for example \citep{eliasmith2013}.
 
@@
 This model has been used to investigate
-action selection and learning \cite{stewart2012a}
+action selection and learning \citep{stewart2012a}
 and the switching time between actions
 has been closely mapped to human decision making
-\cite{stewart2010}.
+\citep{stewart2010}.
 This benchmark tests the ability
@@
 
+We also test an alternate version
+of the basal ganglia sequence model
+in which some ``passthrough'' nodes
+are pruned from the model.
+Passthrough nodes are nodes
+that collect signals from several sources,
+and pass them to other objects unchanged.
+They act as hubs
+that group together related signals
+to reduce the number of connections
+that must be made to
+a group of related objects.
+Since they do no processing,
+they can be difficult to deal with
+for backends that are designed to
+simulate neurons quickly.
+The basal ganglia makes liberal use
+of passthrough nodes,
+so we also test a version of the model
+with most passthrough nodes removed.
+
 \subsection{Backends tested}
@@
 on any general purpose computer
-by using NumPy \cite{vanderwalt2011}
+by using NumPy \citep{vanderwalt2011}
 for fast vectorized computations.
@@
 The OpenCL backend uses the Open Computing Language
-(OpenCL; \cite{stone2010})
+(OpenCL; \citealp{stone2010})
 to run Nengo models on many different computing devices,
@@
 of a new neuromorphic chip
-based partly on Neurogrid \cite{benjamin2014}
+based partly on Neurogrid \citep{benjamin2014}
 currently in development
@@
 \paragraph{5. SpiNNaker hardware (\texttt{nengo\_spinnaker}).}
-The SpiNNaker backend \cite{mundyinpress}
+The SpiNNaker backend \citep{mundyinpress}
 targets the eponymous neuromorphic hardware
-developed by \citeauthor{furber2014}.
+developed by \citet{furber2014}.
 In contrast to the Brainstorm backend,
@@
 perform well, the SpiNNaker backend
-performs statistically worse than the
-other four backends.
+performs worse than the other four backends.
 Its performance, however, is still well within
@@
 as do the distilled and Brainstorm backends.
-??? revisit with new results
-%% The SpiNNaker backend performs well in most cases,
-%% but some instances of the model
-%% are signifless accurate
-%% than the majority of instances.
+The median accuracy of the SpiNNaker is
+the same as the distilled and Brainstorm backends,
+but there are a high proportion of model instances
+with less accuracy than the median,
+as compared to other backends.
 
@@
 for the basal ganglia sequence model.
-Again, all of the backends perform similarly,
+For the version of model with passthrough nodes,
+all of the backends perform similarly,
 except for the SpiNNaker backend.
@@
 around 43 milliseconds, which matches
-the results from \citeauthor{stewart2010}
+the results from \citet{stewart2010}
 for simple actions.
-The SpiNNaker backend has a transition time
-around 55 milliseconds, which is slower
+The SpiNNaker backend has a median transition time
+around 51 milliseconds, which is slower
 than the time reported by Stewart et al.
 for simple actions, but faster than the
-time reported for complex actions.
-??? Run again with passthrough nodes removed
-and make figure
+time reported for complex actions;
+its interquartile range
+is also significantly larger
+than that of other backends.
+However, its performance for
+the version of the model
+with far fewer passthrough nodes
+is a closer match to the other backends.
+Its median transition time
+is around 47 milliseconds,
+and its interquartile range
+is indistinguishable from the other backends.
 
@@
 (determining the placement of computational resources,
-and generating routes to connect resouces),
+and generating routes to connect resources),
 though it builds the largest model faster than
@@
 The reference backend also did not perform well,
-operating at nearly eight times slower than real-time.
+operating at nearly six times slower than real-time.
 The OpenCL backend performed well, operating at around
-four times slower than real-time.
+three times slower than real-time.
 The best performance was seen by the SpiNNaker backend,
-however, which operated at around 1.5 times real-time
-on this moderately-sized model. (??? revisit with new results)
+however, which operated at around 1.2 times real-time
+(including overhead) on this moderately-sized model.
 Since the SpiNNaker board always runs at real-time,
-this means that around one-third of the time taken
+this means that around one-sixth of the time taken
 for the \texttt{run} call is overhead.
@@
 However, we expect that the results
-would be similar, though exaggerated,
+would be similar
 in larger models run for longer amount of time.
-The distilled and brainstorms backends would
+The distilled and brainstorms backends should
 perform slowly, the OpenCL backend should
@@
 While this is similar to the goal
-of other projects, most notably PyNN \cite{davison2008},
+of other projects, most notably PyNN \citep{davison2008},
 Nengo is unique in focusing on
@@
 (though this capability is still possible in Nengo).
-Topographica \cite{bednar2009} plays a similar role,
+Topographica \citep{bednar2009} plays a similar role,
 in that it can interact with multiple neural simulators
@@
 
-???put results.zip on figshare
-
-???link to Github
+All of the software packages discussed in this paper
+are available online,
+except for the Brainstorm backend,
+which has not yet been publicly released
+(see Supplementary Table~1).
+All of the benchmarks presented here,
+as well as the scripts used to generate
+the presented figures,
+are available at
+\url{https://github.com/ctn-archive/bekolay-fnme2015}.
+The results of running the benchmarks
+are not included in the repository;
+however, they can be downloaded separately at
+\url{}
+to replicate the figures in this paper.
 
@@
 
-???probably something about ABR here?
+The authors of this paper
+are three of the seven co-founders
+of Applied Brain Research (ABR),
+who are the sole copyright holders
+of Nengo and the distilled backend.
+While ABR reserves the right
+to commercialize Nengo,
+it is freely available
+for all non-commercial purposes.
+As of the writing of this paper,
+ABR has not sold any licenses to Nengo,
+but has used it
+for other revenue-generating projects.
 
@@
 
-???todo
+TB adapted the models for benchmarking,
+ran the benchmarks,
+wrote the text of the paper,
+and prepared all of the figures.
+TCS wrote initial versions of the benchmark models
+and edited text.
+CE oversaw all research activities,
+and edited text.
 
@@
 
-???todo
-(Andrew Mundy for SpiNNaker help, feedback on first draft,
-Xuan for GPU server, Eric for help in getting OCL benchmarks running,
-James for implementing most of OCL, Jan for product benchmark)
-
-\paragraph{Funding\textcolon} %% Funding
+We thank Andrew Mundy for his help
+running the SpiNNaker backend
+and providing feedback on drafts of this paper.
+We thank Jan Gosmann for the initial version
+of the product benchmark models,
+and for conceptualization and implementation
+of the \texttt{analytics} and \texttt{analytics\_data}
+fixtures.
+We thank Xuan Choo for administering
+the server on which the benchmarks were run,
+Eric Hunsberger for help in running
+the benchmarks on the OpenCL backend,
+and James Bergstra for
+implementing most of the OpenCL backend.
+
+\paragraph{Funding\textcolon}
+NSERC Discovery,
+NSERC Graduate Fellowships,
+ONR (N000141310419)
+and AFOSR (FA8655-13-1-3084). ??? Chris, can you confirm?
 
@@
  Reference (\texttt{nengo}) & 212 & 100\% \\
+ OpenCL (\texttt{nengo\_ocl}) & 187 & 88.2\% \\
  Distilled (\texttt{nengo\_distilled}) & 129 & 60.8\% \\
- OpenCL (\texttt{nengo\_ocl}) & 187 & 88.2\% \\
  Brainstorm (\texttt{nengo\_brainstorm}) & 107 & 50.4\% \\\botrule
@@
 \textbf{\refstepcounter{figure}\label{fig:01} Figure \arabic{figure}.}
-       {Chained communication channel model. (Top) One example instance
+       {Chained communication channel model. (A) One example instance
          of the model run on the reference backend; the decoded output
@@
          12 milliseconds of the simulation are shown.
-         Each ensemble reaches approximately the correct value of
-         $[-0.6, 0.6]$ (indicated with the solid black line)
+         Each ensemble reaches approximately the correct value
+         (indicated with the solid black line)
          but with slight delays depending on their position in the chain.
-         (Bottom) The aggregated accuracy results for each backend on the
+         (B) The aggregated accuracy results for each backend on the
          chained communication channel model. The observed metric is the root
@@
 \textbf{\refstepcounter{figure}\label{fig:02} Figure \arabic{figure}.}
-       {Two-dimensional product model. (Top) One example instance of the model
+       {Two-dimensional product model. (A) One example instance of the model
          run on the reference backend; the decoded input represented
@@
          in the range $[-1, 1]$.
-         (Middle) The decoded product represented by an ensemble downstream
+         (B) The decoded product represented by an ensemble downstream
          of the ensemble representing the input. It closely matches the
          correct product (indicated with the solid black line).
-         (Bottom) The aggregated accuracy results for each backend on the
+         (C) The aggregated accuracy results for each backend on the
          two-dimensional product model. The measured metric is the root
@@
 
-% ??? Remove left plot
-
-% ??? Make middle a stem plot
-
 \begin{figure}[!ht]
 \begin{center}
-  \includegraphics[width=180mm]{fig3}
+  \includegraphics[width=85mm]{fig3}
 \end{center}
 \textbf{\refstepcounter{figure}\label{fig:03} Figure \arabic{figure}.}
-       {Controlled two-dimensional oscillator model. (Left) One example
-         instance of the model run on the reference backend; the decoded
-         value represented by one of the two dimensions in the oscillatory
-         ensemble is shown. The control signal dictating the frequency of
-         oscillation changes every two seconds; in this plot each two second
-         period is overlaid. Each signal oscillates at approximately the
-         correct frequency (see middle for legend).
-         (Middle) The power spectrum of each two second period.
+       {Controlled two-dimensional oscillator model. (A) One example
+         instance of the model run on the reference backend;
+         the power spectrum is shown for each two second period,
+         colored to indicate the target frequency given by the control signal.
          High power is seen only at the frequency we attempt to induce,
          for each of the five test frequencies.
-         (Right) The aggregated accuracy results for each backend on the
+         (B) The aggregated accuracy results for each backend on the
          two-dimensional product model. The measured metric is the similarity
@@
 \textbf{\refstepcounter{figure}\label{fig:04} Figure \arabic{figure}.}
-       {Basal Ganglia sequence model. (Top) One example instance
+       {Basal Ganglia sequence model. (A) One example instance
          of the model run on the reference backend; the similarity between
@@
          (the transition times) are indicated with dashed grey lines.
-         (Bottom) The aggregated accuracy results for each backend on the
-         basal ganglia sequence model. The observed metric is the mean
+         (B) The aggregated accuracy results for each backend on the
+         basal ganglia sequence model, with all passthrough nodes included.
+         The observed metric is the mean
          time to transition from one action to the next. The model is run
@@
          inter-quartile range, while the whiskers extend to 1.5 times the
-         inter-quartile range; outliers are not shown.}
+         inter-quartile range; outliers are not shown.
+         (C) The aggregated accuracy results for each backend on the
+         basal ganglia sequence model, with most passthrough nodes pruned.
+         Lines has the same meaning as in B.}
 \end{figure}
@@
        {Build time for each model on each backend. Each bar represents
-         the mean build time across 150 instances of each model;
-         error bars are 95\% confidence intervals.}
+         the mean build time across 50 instances of each model;
+         error bars are bootstrapped 95\% confidence intervals.}
 \end{figure}
@@
 \textbf{\refstepcounter{figure}\label{fig:06} Figure \arabic{figure}.}
-       {Run time for each model on each backend. Each bar represents
-         the mean run time across 150 instances of each model;
-         error bars are 95\% confidence intervals.
-         Run time is measured relative to real time;
-         e.g., a value of two indicates that the model ran twice as slow
-         as real time.}
+       {Run speed for each model on each backend. Each bar represents
+         the mean run speed across 50 instances of each model;
+         error bars are bootstrapped 95\% confidence intervals.
+         Run speed is measured as the simulation time plus overhead,
+         relative to real time; e.g., a value of two indicates that
+         the calling \texttt{run} for a number of seconds takes
+         the model two times that number of real seconds to complete the
+         \texttt{run} call.}
+
 \end{figure}

### 2015-07-28 fnme/plots.py

@@ -146,74 +146,74 @@ def accuracy():
 
     plot_summary("sequence", "timing_mean", figsize=(onecolumn * 2, 3.0))
     plt.ylabel("Mean transition time (s)")
+    plt.ylim(0.04, 0.06)
     save("accuracy-4")
 
     plot_summary("sequence_pruned", "timing_mean", figsize=(onecolumn * 2, 3.0))
     plt.ylabel("Mean transition time (s)")
+    plt.ylim(0.04, 0.06)
     save("accuracy-4-pruned")
 
 
 def speed(probes=True):
+    def get_all_data(key, d_args, scale_to_realtime=False):
+        t1 = get_data("cchannelchain", key, **d_args)
+        t1['Model'] = "Chained channels"
+        t2 = get_data("product", key, **d_args)
+        t2['Model'] = "Product"
+        t3 = get_data("controlledoscillator", key, **d_args)
+        t3['Model'] = "Oscillator"
+        t4 = get_data("sequence", key, **d_args)
+        t4['Model'] = "BG sequence"
+        t5 = get_data("sequence_pruned", key, **d_args)
+        t5['Model'] = "BG sequence *"
+        if scale_to_realtime:
+            t1[key] /= 0.5
+            t2[key] /= 5.5
+            t3[key] /= 10.0
+            t4[key] /= 4.0
+            t5[key] /= 4.0
+        return pd.concat((t1, t2, t3, t4, t5))
+
+    model_order = ["Chained channels",
+                   "Product",
+                   "Oscillator",
+                   "BG sequence",
+                   "BG sequence *"]
+
     # Only get build speed for probed data
     if probes:
-        d_args = {'separate_cols': False, 'probes': probes}
-        t1 = get_data("cchannelchain", "buildtime", **d_args)
-        t1['Model'] = "Chained channels"
-        t2 = get_data("product", "buildtime", **d_args)
-        t2['Model'] = "Product"
-        t3 = get_data("controlledoscillator", "buildtime", **d_args)
-        t3['Model'] = "Oscillator"
-        t4 = get_data("sequence", "buildtime", **d_args)
-        t4['Model'] = "BG sequence"
-        build = pd.concat((t1, t2, t3, t4))
+        build = get_all_data("buildtime",
+                             {'separate_cols': False, 'probes': probes})
 
         setup(figsize=(onecolumn * 2, 3.0))
         ax = plt.subplot(1, 1, 1)
[…]

### 2015-07-28 make.py

@@ -25,12 +25,19 @@ def task_reset():
 
 def task_paper():
     d = os.path.join(root, 'paper')
-    yield {'name': 'main',
-           'actions': [CmdAction('rubber --pdf paper.tex', cwd=d)],
-           'targets': [os.path.join(d, 'paper.pdf')]}
-    yield {'name': 'supplementary',
-           'actions': [CmdAction('rubber --pdf supplementary.tex', cwd=d)],
-           'targets': [os.path.join(d, 'supplementary.pdf')]}
+
+    def forsurecompile(fname, bibtex=True):
+        pdf = CmdAction('pdflatex %s.tex' % fname, cwd=d)
+        bib = CmdAction('bibtex %s' % fname, cwd=d)
+        pdf_file = os.path.join(d, '%s.pdf' % fname)
+        tex_file = os.path.join(d, '%s.tex' % fname)
+        bib_file = os.path.join(d, '%s.bib' % fname)
+        return {'name': fname,
+                'file_dep': [tex_file, bib_file] if bibtex else [tex_file],
+                'actions': [pdf, bib, pdf, pdf] if bibtex else [pdf, pdf],
+                'targets': [pdf_file]}
+    yield forsurecompile('paper')
+    yield forsurecompile('supplementary', bibtex=False)
 
 
 def task_compliance():
@@ -71,7 +78,7 @@ def task_benchmarks():
                         'help': 'Additional flags to pass onto py.test'}]}
 
 
-def task_plots():
+def task_figures():
     yield {'name': 'models',
            'actions': [CmdAction(
                'py.test -p fnme.options --simulator nengo.Simulator '
@@ -83,17 +90,11 @@ def task_plots():
            'actions': [(fnme.plots.speed, (True,))]}
     yield {'name': 'speed-np',
            'actions': [(fnme.plots.speed, (False,))]}
-
-
-def task_combine():
-    yield {'name': 'fig1',
-           'actions': [(fnme.plots.fig1,)]}
-    yield {'name': 'fig2',
-           'actions': [(fnme.plots.fig2,)]}
-    yield {'name': 'fig3',
-           'actions': [(fnme.plots.fig3,)]}
-    yield {'name': 'fig4',
-           'actions': [(fnme.plots.fig4,)]}
+    yield {'name': 'combine',
+           'actions': [(fnme.plots.fig1,),
+                       (fnme.plots.fig2,),
+                       (fnme.plots.fig3,),
+                       (fnme.plots.fig4,)]}
 
 
 if __name__ == '__main__':

### 2015-07-28 paper/paper.tex
Incorporate feedback from Chris, part 2

@@
 \usepackage{inconsolata}
-\usepackage{listings}
-\lstset{language=Python}
-\lstset{basicstyle=\ttfamily,breaklines=true}
 
@@
   can be used to benchmark neuromorphic hardware's
-  functional performance and speed simulating
+  functional performance and simulation speed
   in an efficient, unbiased, and future-proof manner.
@@
   Nengo can collect several benchmark metrics
+  across five different backends
   that identify situations in which
-  some backends perform differently
-  or significantly faster than others.
+  some backends perform
+  with different accuracy and speed.
 
@@
 The activity of these neurons
-forms a distributed representation of a numerical vector;
+is generally taken to be
+a distributed representation
+of a numerical state vector;
 for example, a group of 100 neurons might represent
@@
 in under 20 lines of code
-can be seen in Appendix~\ref{App:01}.
+can be seen in Supplementary Figure~2.
+
+It is important to note that,
+although the Nengo frontend
+is designed to make functional networks
+with compact code,
+any spiking neural network topology
+can be implemented in Nengo.
+While we will only show examples
+of functional connection between ensembles,
+it is also possible
+to make direct neuron-to-neuron connections;
+functional and direct connections
+can coexist in the same network,
+as is commonly done in situations
+requiring direct inhibitory currents.
 
@@
 we believe this is an acceptable consequence
-of the breadth of their application.
+of being able to test across multiple backends.
 When adapting these functional tests for benchmarking,
@@
 Nengo's test suite employs the \texttt{pytest}
-testing framework \footnote{Available at \url{http://pytest.org/}.}.
+testing framework.\footnote{Available at \url{http://pytest.org/}.}
 \texttt{pytest} enables
@@
 and run for any test that might use it.
-The example script in Appendix~\ref{App:01}
-demonstrates how these fixtures
-look in test scripts.
+A demonstration of how these fixtures
+are used in test scripts
+can be seen in an example script,
+included as Supplementary Figure~2.
 
@@
 that can be varied
-in order to benchmark extreme cases
+in order to benchmark a wide variety of cases
 (see Appendix~\ref{App:01} for examples).
@@
 but make these parameterized models
-available at \url{https://github.com/tbekolay/fnme2015}
-for those who want to explore extreme cases.
+available at \url{https://github.com/ctn-archive/bekolay-fnme2015}
+for those who want to explore additional cases.
 
@@
 All benchmarks were run on a server
-running Debian unstable.
+running Debian sid.
 The server was configured with
@@
 a 1 GB ethernet port on
-the Supermicro X9DRG-QF motherboard.
+the Supermicro X9DRG-QF motherboard
+for the SpiNNaker benchmarks.
 
@@
 implement this model accurately,
-despite five sources of potential noise.
+despite five layers of processing that include noise.
 
@@
 and other sensory pathways,
-rather than focusing on function and dynamics.
+rather than focusing on
+a wider variety of functions
+and dynamics more generally.
 
 While we cannot claim that Nengo
-solves all of complications that arise
+solves all of the complications that arise
 in benchmarking,
@@
 are three of the seven co-founders
-of Applied Brain Research (ABR),
-who are the sole copyright holders
+of Applied Brain Research (ABR, Inc.),
+which is the sole copyright holder
 of Nengo and the distilled backend.
@@
 implementing most of the OpenCL backend.
+We thank the Brainstorm group
+at Stanford University for making
+their experimental hardware emulation backend
+available to us.
 
 \paragraph{Funding\textcolon}
-NSERC Discovery,
 NSERC Graduate Fellowships,
+NSERC Discovery (grant 261453),
 ONR (N000141310419)
-and AFOSR (FA8655-13-1-3084). ??? Chris, can you confirm?
+AFOSR (FA8655-13-1-3084),
+Canada Research Chairs,
+and Canadian Foundation for Innovation
+Ontario Innovation Trust.
 
@@
          basal ganglia sequence model, with most passthrough nodes pruned.
-         Lines has the same meaning as in B.}
+         Lines have the same meaning as in B.}
 \end{figure}
@@
          the mean build time across 50 instances of each model;
-         error bars are bootstrapped 95\% confidence intervals.}
+         error bars are bootstrapped 95\% confidence intervals.
+         BG Sequence * refers to the basal ganglia sequence model
+         in which passthrough nodes have been removed.}
 \end{figure}
@@
          the model two times that number of real seconds to complete the
-         \texttt{run} call.}
+         \texttt{run} call.
+         BG Sequence * refers to the basal ganglia sequence model
+         in which passthrough nodes have been removed.}
 
@@
 
-\clearpage
-\appendix
-
-\section{Chained communication channel model}
-\label{App:01}
-
-\begin{lstlisting}
-import numpy as np
-import nengo
-from nengo.utils.numpy import rmse
-
-def test_cchannelchain(Simulator, analytics, plt, rng, seed):
-    # Parameters that can be varied to investigate extreme cases
-    dims = 2
-    layers = 5
-    n_neurons = 100
-    synapse = nengo.Lowpass(0.01)
-
-    with nengo.Network(seed=seed) as model:
-        hypersphere = nengo.dists.UniformHypersphere()
-        value = hypersphere.sample(dims, 1, rng=rng).ravel()
-        stim = nengo.Node(value)
-
-        ens = [nengo.Ensemble(n_neurons, dimensions=dims)
-               for _ in range(layers)]
-
-        nengo.Connection(stim, ens[0])
-        for i in range(layers - 1):
-            nengo.Connection(ens[i], ens[i+1], synapse=synapse)
-
-        p_input = nengo.Probe(stim)
-        p_outputs = [nengo.Probe(ens[i], synapse=synapse)
-                     for i in range(layers)]
-
-    sim = Simulator(model)
-    sim.run(0.5)
-
-    for p_output in p_outputs:
-        plt.plot(sim.trange(), sim.data[p_output])
-    plt.plot(sim.trange(), sim.data[p_input], color='k', linewidth=1)
-    plt.ylabel('Decoded output')
-    plt.xlabel('Time (s)')
-
-    last = p_outputs[-1]
-    decoding_rmse = rmse(value, sim.data[last][sim.trange() > 0.4]
-    analytics.add_data('rmse', decoding_rmse)
-
-def test_compare_cchannelchain(analytics_data, plt):
-    rmses = [d['rmse'] for d in analytics_data]
-    plt.bar(np.arange(len(rmses)), rmses, align='center')
-    plt.ylabel("RMSE")
-\end{lstlisting}
-
 \end{document}

### 2015-07-28 paper/supplementary.tex
Incorporate feedback from Chris, part 2

--- 2015-06-28 paper/supplementary.tex
@@
-%%% You will need to have the following packages installed: datetime, fmtcount, etoolbox, fcprefix, which are normally inlcuded in WinEdt. %%%
 \documentclass{frontiers_suppmat} % for all articles
@@
 \usepackage{url}
+\usepackage{inconsolata}
+\usepackage{listings}
+\lstset{language=Python}
+\lstset{basicstyle=\ttfamily,breaklines=true}
 
@@
 \def\corrEmail{tbekolay@uwaterloo.ca}
-
-% \color{FrontiersColor} Is the color used in the Journal name, in the title, and the names of the sections.
 
@@
 
+\begin{table}[!ht]
+\textbf{\refstepcounter{table}\label{Tab:01} Supplementary Table \arabic{table}.}{
+  Software versions used for benchmarking.
+  The PyPI name is the unique identifier used for installing the Python package
+  through the Python Package Index (PyPI). Packages can be found by
+  visiting \url{https://pypi.python.org/pypi/<PyPI name>}.}
+
+\processtable{ }
+{\begin{tabular}{lcc}\toprule
+ Package & PyPI name & Version number\\\midrule
+ Nengo & \texttt{nengo} & Development version, commit \texttt{7d2d24145} \\
+ Distilled backend & \texttt{nengo\_distilled} & 0.1.0 \\
+ OpenCL backend & \texttt{nengo\_ocl} & 0.1.0 \\
+ Brainstorm backend & Not available on PyPI & Development version, commit \texttt{ac3cfa708} \\
+ SpiNNaker backend & \texttt{nengo\_spinnaker} & 0.2.4 \\
+ NumPy & \texttt{numpy} & 1.8.1 \\\botrule
+\end{tabular}}{}
+\end{table}
+
 \begin{figure}[!ht]
 \begin{center}
-  \includegraphics[width=85mm]{fig7}
+  \includegraphics[width=180mm]{fig7}
 \end{center}
@@
          e.g., a value of two indicates that the model ran twice as slow
-         as real time.}
+         as real time.
+         BG Sequence * refers to the basal ganglia sequence model
+         in which passthrough nodes have been removed.}
+\end{figure}
+
+\begin{figure}[!ht]
+\begin{lstlisting}
+import numpy as np
+import nengo
+from nengo.utils.numpy import rmse
+
+def test_cchannelchain(Simulator, analytics, plt, rng, seed):
+    # Parameters that can be varied to investigate extreme cases
+    dims = 2
+    layers = 5
+    n_neurons = 100
+    synapse = nengo.Lowpass(0.01)
+
+    with nengo.Network(seed=seed) as model:
+        hypersphere = nengo.dists.UniformHypersphere()
+        value = hypersphere.sample(dims, 1, rng=rng).ravel()
+        stim = nengo.Node(value)
+
+        ens = [nengo.Ensemble(n_neurons, dimensions=dims)
+               for _ in range(layers)]
+
+        nengo.Connection(stim, ens[0])
+        for i in range(layers - 1):
+            nengo.Connection(ens[i], ens[i+1], synapse=synapse)
+
+        p_input = nengo.Probe(stim)
+        p_outputs = [nengo.Probe(ens[i], synapse=synapse)
+                     for i in range(layers)]
+
+    sim = Simulator(model)
+    sim.run(0.5)
+
+    for p_output in p_outputs:
+        plt.plot(sim.trange(), sim.data[p_output])
+    plt.plot(sim.trange(), sim.data[p_input], color='k', linewidth=1)
+    plt.ylabel('Decoded output')
+    plt.xlabel('Time (s)')
+
+    last = p_outputs[-1]
+    decoding_rmse = rmse(value, sim.data[last][sim.trange() > 0.4]
+    analytics.add_data('rmse', decoding_rmse)
+
+def test_compare_cchannelchain(analytics_data, plt):
+    rmses = [d['rmse'] for d in analytics_data]
+    plt.bar(np.arange(len(rmses)), rmses, align='center')
+    plt.ylabel("RMSE")
+\end{lstlisting}
+\textbf{\refstepcounter{figure}\label{fig:02} Supplementary Figure \arabic{figure}.}
+       {Python code for implementing the chained communication channel model.}
 \end{figure}

### 2015-07-28 make.py

@@ -27,7 +27,8 @@ def task_paper():
     d = os.path.join(root, 'paper')
 
     def forsurecompile(fname, bibtex=True):
-        pdf = CmdAction('pdflatex %s.tex' % fname, cwd=d)
+        pdf = CmdAction('pdflatex -interaction=nonstopmode %s.tex' % fname,
+                        cwd=d)
         bib = CmdAction('bibtex %s' % fname, cwd=d)
         pdf_file = os.path.join(d, '%s.pdf' % fname)
         tex_file = os.path.join(d, '%s.tex' % fname)

### 2015-07-28 paper/paper.tex
Add comment about speed and passthrough nodes

@@
 
+Interestingly, while removing passthrough nodes
+results in significantly slower run times
+for the reference backend,
+it speeds up the OpenCL and SpiNNaker backends slightly.
+This result indicates that passthrough nodes
+add to the overhead incurred by
+SpiNNaker and OpenCL.
 Other backends also incur overhead,
@@
 that the overhead involved in probes
-dominated the actual run time for some backends.
+dominated the run time for some backends.
 However, we found that

### 2015-07-29 paper/paper.tex
Full edit for readability, etc

@@
   We implement four benchmark models and show that
-  Nengo can collect several benchmark metrics
+  Nengo can collect metrics
   across five different backends
   that identify situations in which
-  some backends perform
-  with different accuracy and speed.
+  some backends perform more
+  accurately or quickly.
 
@@
 Even once that effort is undertaken,
-benchmarks often are run a few times
+benchmarks are often run a few times
 and then forgotten,
@@
 build large-scale functional models,
-and hence its codebase contains
+and for this reason its codebase contains
 tests of functional performance;
@@
 to ensure that Nengo continues to function
-correctly, and is run frequently using
+correctly, and is run whenever Nengo is changed using
 continuous integration systems,
@@
 The OpenCL backend aims to be a fast backend
-that still works on general purpose computers,
-but can also take advantage of
+that still works on general purpose computers
+and can take advantage of
 graphical processing units (GPUs).
@@
 We describe Nengo's testing framework,
-including explanations of the testing fixtures
+including explanations of the test fixtures
 used to collect and visualize benchmarks.
@@
 There are two key features of Nengo
-(starting from version 2.0)
+(from version 2.0 onward)
 that enable rapid benchmarking of neuromorphic systems.
@@
 to any backend that implements a certain set of requirements.
-The second is a ``fuzzy'' test suite ensuring that
+The second is a ``fuzzy'' test suite that ensures
 Nengo can be used to create models that solve cognitive tasks.
@@
 for example, a group of 100 neurons might represent
-a three-dimensional vector,
-and as that vector changes,
+an agent's location in three-dimensional space,
+and as the agent moves,
 the pattern of neural activity
@@
 collect output values,
-interface with physical sensors and motors,
-or provide any other computation needed in a mode.
+interface with physical sensors and actuators,
+or provide any other computation needed in a model.
 In the case of the benchmarks presented in this paper,
@@
 (e.g., \textit{Ensembles} or \textit{Nodes}) together.
-The two objects being connected are the only mandatory parameters;
-the synapse model filtering the connection,
+The two objects being connected are the only mandatory parameters.
+The synapse model filtering the connection,
 a function applied to the vector
@@
 at a particular rate.
-The object to be probed must be specified;
-the attribute of that object,
+The object to be probed must be specified.
+The attribute of that object,
 a sampling rate, and a synapse model for filtering
@@
 An important distinction between typical
-parameters and those specified in Nengo
-is that many are stochastic,
-and not necessarily guaranteed
+parameters in a neural simulation
+and those specified in Nengo
+is that Nengo parameters can be stochastic,
+and are not guaranteed
 to be supported by every backend.
@@
 for example,
-are most often specified as probability distributions;
+are often specified as probability distributions;
 an ensemble's maximum firing rate defaults to
@@
 express a functional network
-with 500 neurons and 6 connections
-(representing 50,000 connection weights
-and 100 direct current injection sites)
-in under 20 lines of code
+with 500~neurons and 6~connections
+(representing 50,000~connection weights
+and 100~direct current injection sites)
+in under 20~lines of code
 can be seen in Supplementary Figure~2.
@@
 although the Nengo frontend
-is designed to make functional networks
-with compact code,
-any spiking neural network topology
-can be implemented in Nengo.
+is designed to make large-scale networks
+in relatively few lines of code,
+it does not impose any constraints
+that would preclude
+the creation
+of detailed small-scale networks.
 While we will only show examples
@@
 requiring direct inhibitory currents.
+With both types of connections,
+it is possible to create
+any network topology in Nengo.
 
@@
 ensembles, nodes, connections, and probes,
-and construct the underlying objects necessary
+and construct the backend-specific objects necessary
 to implement the model specified by that network.
@@
 and cannot change;
-other backends may have variable-length timesteps,
-or may not explicitly track timesteps.
+other backends may have variable-length timesteps.
 
@@
 to the times at which data was probed.
-In the reference backend, this will be
+In the reference backend, \texttt{trange} always returns
 a straightforward sequence of increasing
 multiples of \texttt{dt};
-other backends may simulate at variable rates.
-
-Finally, the simulator object exposed by each backend
+other backends may simulate at variable rates,
+though the sequence of times must increase monotonically.
+
+Finally, the simulator object implemented by each backend
 must have an attribute called \texttt{data},
@@
 The details of how each backend
-implements high-level frontend models
+implements the high-level frontend objects
 are out of the scope of this paper.
@@
 to implement a particular task.
-For this reason,
+For these reasons,
 functional tests can only
@@
 are used in test scripts
-can be seen in an example script,
-included as Supplementary Figure~2.
+can be seen in Supplementary Figure~2.
 
@@
 Nengo's test suite defines several test fixtures
-to enable fuzzy testing
+to support fuzzy testing
 that collects and visualizes performance metrics
@@
 \paragraph{\texttt{Simulator}}
-allows for tests to be run with multiple backends.
+allows tests to be run with multiple backends.
 As detailed in Section~\ref{Sec:Backend},
@@
 that can inspected manually.
-For large amounts of data that
-requires more analysis,
-\texttt{analytics} fixture exposes an interface
+For large amounts of data
+requiring more analysis,
+the \texttt{analytics} fixture exposes an interface
 to save arbitrary data (in the form of NumPy arrays)
@@
 enables comparative testing between
-two runs of the same test.
-The two runs might represent two versions
+two or more runs of the same test.
+The runs might represent multiple versions
 of the same backend---one before a
-speedup and one after---or two
+speedup and one after---or multiple
 entirely different backends.
@@
 with the \texttt{analytics} fixture.
-See Appendix~\ref{App:01} for a
+See Supplementary Figure~12Appendix~\ref{App:01} for a
 concrete example of using the
@@
 The amount of overhead depends
-on the backend; those on specific hardware platforms
+on the backend; backends making use
+of hardware other than the CPU
 (like the SpiNNaker and OpenCL backends)
 are likely to incur more overhead
-than those on general purpose platforms.
+than those using the same CPU core
+as the Nengo frontend.
 However, we include the overhead in
@@
 in order to benchmark a wide variety of cases
-(see Appendix~\ref{App:01} for examples).
+(see Supplementary Figure~2 for an example).
 We test each model with parameters
@@
 available at \url{https://github.com/ctn-archive/bekolay-fnme2015}
-for those who want to explore additional cases.
+for those who wish to explore additional cases.
 
@@
 five ensembles,
-comprised of 500 leaky integrate-and-fire (LIF) neurons total,
+comprised of 100 leaky integrate-and-fire (LIF) neurons each
+(500 total),
 are connected in series,
@@
 This model tests how
-robust each backend is to noise introduced
+robust each backend is to the noise introduced
 by representing a vector space
@@
 to cause oscillation at
-2Hz, 1Hz, 0Hz, -1Hz, and -2Hz.
+2~Hz, 1~Hz, 0~Hz, -1~Hz, and -2~Hz.
 In total, the model is comprised of 600 LIF neurons.
@@
 
-\paragraph{4. Basal Ganglia sequence.}
+\paragraph{4. Basal ganglia sequence.}
 In this model, brain structures
@@
 they can be difficult to deal with
-for backends that are designed to
+in backends that are designed to
 simulate neurons quickly.
@@
 for fast vectorized computations.
-It is included with the \texttt{nengo} frontend
+It is included with the Nengo frontend
 as \texttt{nengo.Simulator}.
-When appropriate, other backends will be benchmarked
-relative to the reference backend,
-which has the most features but does not target
+The reference backend offers
+the most features, but does not target
 specialized hardware.
@@
 currently in development
-by the Brain in Silicon lab
-at Stanford University\footnote{
-  Some details available at \url{http://brainstorm.stanford.edu/projects/}.}.
+by the Brains in Silicon lab
+at Stanford University.\footnote{
+  Some details available at \url{http://brainstorm.stanford.edu/projects/}.}
 The software backend does not aim for speed;
-instead, it attempts to emulate the hardware
+instead, it attempts to emulate the proposed hardware
 in order to test its applicability
-to large-scale neural models.
+for large-scale neural models.
 If the emulated hardware can perform well,
@@
 \paragraph{5. SpiNNaker hardware (\texttt{nengo\_spinnaker}).}
-The SpiNNaker backend \citep{mundyinpress}
+The SpiNNaker backend \citep{mundy2015}
 targets the eponymous neuromorphic hardware
@@
 
-All benchmarks were run on a server
-running Debian sid.
+All benchmarks were run 50 times
+on a server running Debian sid.
 The server was configured with
 two Intel Xeon E5-2650 CPUs
-clocked at 2.00GHz,
+clocked at 2.00~GHz,
 four Nvidia Tesla C2075 GPUs,
@@
 implement this model accurately,
-despite five layers of processing that include noise.
+despite five layers of processing
+that each introduce noise.
 
@@
 perform well, the SpiNNaker backend
-performs worse than the other four backends.
+is less accurate than the other four backends.
 Its performance, however, is still well within
@@
 for the basal ganglia sequence model.
-For the version of model with passthrough nodes,
+For the version of the model with passthrough nodes,
 all of the backends perform similarly,
@@
 the version of the model
-with far fewer passthrough nodes
+with passthrough nodes removed
 is a closer match to the other backends.
@@
 SpiNNaker, on the other hand, is slower than other backends
-for these models, because its goal
+for these models because its goal
 is to run in real-time even if it is possible to run faster.
+
 The most important result is for the largest model,
@@
 In this model, the distilled and Brainstorm backends
-performed very poorly
-(though neither has speed as a primary goal).
+performed poorly,
+though neither has speed as a primary goal.
 The reference backend also did not perform well,
 operating at nearly six times slower than real-time.
-The OpenCL backend performed well, operating at around
+The OpenCL backend performed better, operating at around
 three times slower than real-time.
@@
 (e.g., the product and controlled oscillator models)
-bear closer inspection to determine the source
+warrant closer inspection to determine the source
 of the slowdown.
@@
 these models are very small---each would only
-be a small component of a larger model.
+be a small component of a real large-scale model.
 Spaun, for example, includes multiple copies
@@
 benchmarked here.
-Additionally, we run them
+Additionally, in this study, we run these models
 for very small amounts of time---the longest
@@
 Real models run for longer amounts of time
-to gather data comparable to those gathered
+to gather data comparable to data gathered
 in neuroscientific experiments.
@@
 would be similar
-in larger models run for longer amount of time.
-The distilled and brainstorms backends should
+in larger models run for longer amounts of time.
+The distilled and Brainstorm backends should
 perform slowly, the OpenCL backend should
@@
 that can target multiple backends,
-and therefore provides a platform
+and therefore provides an attractive platform
 for benchmarking neuromorphic backends,
@@
 a piece of neuromorphic hardware
-gives access to all of the models
-already developed for it,
+gives access to all Nengo models,
 which is reason enough to develop a backend.
@@
 however, they can be downloaded separately at
-\url{}
+\url{http://dx.doi.org/10.6084/m9.figshare.1496569}
 to replicate the figures in this paper.
@@
          but with slight delays depending on their position in the chain.
-         (B) The aggregated accuracy results for each backend on the
+         (B) The aggregated accuracy results for
+         50 trials of each backend on the
          chained communication channel model. The observed metric is the root
@@
          correct product (indicated with the solid black line).
-         (C) The aggregated accuracy results for each backend on the
+         (C) The aggregated accuracy results for 50 trials of
+         each backend on the
          two-dimensional product model. The measured metric is the root
@@
          for each of the five test frequencies.
-         (B) The aggregated accuracy results for each backend on the
+         (B) The aggregated accuracy results for 50 trials of
+         each backend on the
          two-dimensional product model. The measured metric is the similarity
@@
 \textbf{\refstepcounter{figure}\label{fig:04} Figure \arabic{figure}.}
-       {Basal Ganglia sequence model. (A) One example instance
+       {Basal ganglia sequence model. (A) One example instance
          of the model run on the reference backend; the similarity between
@@
          (the transition times) are indicated with dashed grey lines.
-         (B) The aggregated accuracy results for each backend on the
+         (B) The aggregated accuracy results for 50 trials of
+         each backend on the
          basal ganglia sequence model, with all passthrough nodes included.
@@
          inter-quartile range; outliers are not shown.
-         (C) The aggregated accuracy results for each backend on the
+         (C) The aggregated accuracy results for 50 trials of
+         each backend on the
          basal ganglia sequence model, with most passthrough nodes pruned.

### 2015-07-29 paper/paper.tex
Move supplementary material to main paper
There's plenty of room for it, so why not!

@@
 \usepackage{inconsolata}
+\usepackage{listings}
+\lstset{language=Python}
+\lstset{basicstyle=\ttfamily,breaklines=true}
 
@@
 in under 20~lines of code
-can be seen in Supplementary Figure~2.
+can be seen in Appendix~A.
 
@@
 are used in test scripts
-can be seen in Supplementary Figure~2.
+can be seen in Appendix~A.
 
@@
 with the \texttt{analytics} fixture.
-See Supplementary Figure~12Appendix~\ref{App:01} for a
+See Appendix~A for a
 concrete example of using the
@@
 in order to benchmark a wide variety of cases
-(see Supplementary Figure~2 for an example).
+(see Appendix~A for an example).
 We test each model with parameters
@@
 used for benchmarking can be found in
-Supplementary Table~1.
+Table~\ref{Tab:02}.
 
@@
 the total time taken in a \texttt{run} call
-(see Supplementary Figure~1).
+(see Figure~\ref{fig:07}).
 
@@
 which has not yet been publicly released
-(see Supplementary Table~1).
+(see Table~\ref{tab:02}).
 All of the benchmarks presented here,
@@
 
+\clearpage
+
+\section*{Appendix A: Chained Communication Channel model}
+
+\begin{lstlisting}
+import numpy as np
+import nengo
+from nengo.utils.numpy import rmse
+
+def test_cchannelchain(Simulator, analytics, plt, rng, seed):
+    # Parameters that can be varied to investigate extreme cases
+    dims = 2
+    layers = 5
+    n_neurons = 100
+    synapse = nengo.Lowpass(0.01)
+
+    with nengo.Network(seed=seed) as model:
+        hypersphere = nengo.dists.UniformHypersphere()
+        value = hypersphere.sample(dims, 1, rng=rng).ravel()
+        stim = nengo.Node(value)
+
+        ens = [nengo.Ensemble(n_neurons, dimensions=dims)
+               for _ in range(layers)]
+
+        nengo.Connection(stim, ens[0])
+        for i in range(layers - 1):
+            nengo.Connection(ens[i], ens[i+1], synapse=synapse)
+
+        p_input = nengo.Probe(stim)
+        p_outputs = [nengo.Probe(ens[i], synapse=synapse)
+                     for i in range(layers)]
+
+    sim = Simulator(model)
+    sim.run(0.5)
+
+    for p_output in p_outputs:
+        plt.plot(sim.trange(), sim.data[p_output])
+    plt.plot(sim.trange(), sim.data[p_input], color='k', linewidth=1)
+    plt.ylabel('Decoded output')
+    plt.xlabel('Time (s)')
+
+    last = p_outputs[-1]
+    decoding_rmse = rmse(value, sim.data[last][sim.trange() > 0.4]
+    analytics.add_data('rmse', decoding_rmse)
+
+def test_compare_cchannelchain(analytics_data, plt):
+    rmses = [d['rmse'] for d in analytics_data]
+    plt.bar(np.arange(len(rmses)), rmses, align='center')
+    plt.ylabel("RMSE")
+\end{lstlisting}
+
 \section*{Figures}
@@
  Brainstorm (\texttt{nengo\_brainstorm}) & 107 & 50.4\% \\\botrule
+\end{tabular}}{}
+\end{table}
+
+\begin{table}[!ht]
+\textbf{\refstepcounter{table}\label{Tab:02} Table \arabic{table}.}{
+  Software versions used for benchmarking.
+  The PyPI name is the unique identifier used for installing the Python package
+  through the Python Package Index (PyPI). Packages can be found by
+  visiting \url{https://pypi.python.org/pypi/<PyPI name>}.}
+
+\processtable{ }
+{\begin{tabular}{lcc}\toprule
+ Package & PyPI name & Version number\\\midrule
+ Nengo & \texttt{nengo} & Development version, commit \texttt{7d2d24145} \\
+ Distilled backend & \texttt{nengo\_distilled} & 0.1.0 \\
+ OpenCL backend & \texttt{nengo\_ocl} & 0.1.0 \\
+ Brainstorm backend & Not available on PyPI & Development version, commit \texttt{ac3cfa708} \\
+ SpiNNaker backend & \texttt{nengo\_spinnaker} & 0.2.4 \\
+ NumPy & \texttt{numpy} & 1.8.1 \\\botrule
 \end{tabular}}{}
@@
 
+\begin{figure}[!ht]
+\begin{center}
+  \includegraphics[width=85mm]{fig7}
+\end{center}
+\textbf{\refstepcounter{figure}\label{fig:07} Figure \arabic{figure}.}
+       {Run time for each model with probes removed on each backend.
+         Each bar represents the mean run time across 100 instances
+         of each model;
+         error bars are 95\% confidence intervals.
+         Run time is measured relative to real time;
+         e.g., a value of two indicates that the model ran twice as slow
+         as real time.
+         BG Sequence * refers to the basal ganglia sequence model
+         in which passthrough nodes have been removed.}
+\end{figure}
+
 \end{document}

### 2015-07-29 make.py

@@ -38,7 +38,6 @@ def task_paper():
                 'actions': [pdf, bib, pdf, pdf] if bibtex else [pdf, pdf],
                 'targets': [pdf_file]}
     yield forsurecompile('paper')
-    yield forsurecompile('supplementary', bibtex=False)
 
 
 def task_compliance():

### 2015-07-30 paper/paper.tex
Incorporate feedback from Terry and Andrew
Ready to submit!

@@
 Several Nengo backends exist or are in active development.
-In this paper, we will run benchmarks
+In this paper, we run benchmarks
 on five backends.
@@
 and one or more learning rules
-can optionally be specified,
-along with several other optional parameters.
+can optionally be specified.
 
@@
 that address central functioning aspects
-of a wide variety of large-scale briain models
+of a wide variety of large-scale brain models
 (see \citealp{eliasmith2003a,eliasmith2013}).
@@
 known collectively as the basal ganglia
-are contructed from 4900 LIF neurons,
-organized such that they iterate
+are constructed from 4900 LIF neurons,
+and are organized such that they iterate
 through a repeating set of actions.
@@
 A single 48-chip SpiNN-5 board
-was connected through
-a 1 GB ethernet port on
+was connected directly to
+a 1 Gb/s Ethernet port on
 the Supermicro X9DRG-QF motherboard
@@
 All other backends have a transition time
-around 43 milliseconds, which matches
-the results from \citet{stewart2010}
-for simple actions.
-The SpiNNaker backend has a median transition time
-around 51 milliseconds, which is slower
-than the time reported by Stewart et al.
-for simple actions, but faster than the
-time reported for complex actions;
+around 43 milliseconds,
+but the SpiNNaker backend has a median transition time
+around 51 milliseconds;
 its interquartile range
@@
 this means that around one-sixth of the time taken
-for the \texttt{run} call is overhead.
+for the \texttt{run} call is overhead
+when running this model for 10 seconds.
 
@@
 of the slowdown.
-Similarly, we should investigate
-the product model instances
+
+Differences in accuracy benchmarks
+are also important for individual backends.
+The improved accuracy
+for the SpiNNaker backend
+when passthrough nodes are removed
+from the basal ganglia model
+has resulted in ongoing work to
+automatically remove passthrough nodes
+in the build phase of the SpiNNaker backend.
+Similarly, we will investigate
+instances of the product model
 in which the SpiNNaker backend
-differs from other backends.
+is less accurate than other backends,
+though we suspect that its
+lack of floating point hardware
+may be responsible.
 
@@
          500 millisecond simulation. The box shows the median and
-         inter-quartile range, while the whiskers extend to 1.5 times the
-         inter-quartile range; outliers are not shown.}
+         interquartile range, while the whiskers extend to 1.5 times the
+         interquartile range; outliers are not shown.}
 \end{figure}
@@
          correct initial state). The box shows the median and
-         inter-quartile range, while the whiskers extend to 1.5 times the
-         inter-quartile range; outliers are not shown.}
+         interquartile range, while the whiskers extend to 1.5 times the
+         interquartile range; outliers are not shown.}
 \end{figure}
@@
          all frequencies. The box shows the median and
-         inter-quartile range, while the whiskers extend to 1.5 times the
-         inter-quartile range; outliers are not shown.}
+         interquartile range, while the whiskers extend to 1.5 times the
+         interquartile range; outliers are not shown.}
 \end{figure}
@@
          on the transition time. The box shows the median and
-         inter-quartile range, while the whiskers extend to 1.5 times the
-         inter-quartile range; outliers are not shown.
+         interquartile range, while the whiskers extend to 1.5 times the
+         interquartile range; outliers are not shown.
          (C) The aggregated accuracy results for 50 trials of

### 2015-07-30 paper/paper.tex
Add cover letter
And a few other changes from the submission process.

@@
   % 5--8 keywords
-  \keyFont{ \section{Keywords:} Nengo, benchmarking, neuromorphic hardware }
+  \keyFont{ \section{Keywords:} Nengo, benchmarking, neuromorphic hardware,
+    large-scale neural networks, spiking neural networks}
 \end{abstract}
@@
 which has not yet been publicly released
-(see Table~\ref{tab:02}).
+(see Table~\ref{Tab:02}).
 All of the benchmarks presented here,

### 2015-08-29 paper/rebuttals.txt
Add reviews and rebuttal todo list

Todo list
=========

Work

- [ ] 1-4: Try to get unit tests running SpiNNaker
- [ ] 1-4: Why does removing probes slow down reference?
- [ ] 1-4: Ensure confidence intervals are real things
- [ ] 2-2: Find some citations of previous neuromorphic / simulator benchmarking
- [ ] 2-4: Collect information about current inputs?
- [ ] 2-5: Use different boxplot whisker type?

Writing

- [ ] 1-4: Rewrite lines 320-325
- [ ] 1-4: Write something about negative frequencies
- [ ] 1-4: Look up CPG frequencies or something
- [ ] 1-4: Explain compliance more (Table 1 especially)
- [ ] 1-5: Add discussion paragraph on efficiency
- [ ] 2-3: Add text on limitations to introduction / discussion
- [ ] 2-4: Add discussion on current input vs spike input?
- [ ] 2-4: Discuss why you'd want to set seeds
- [ ] 2-4: Comment on larger networks
- [ ] 2-4: Define fuzzy testing
- [ ] 2-4: Change table 1, 2 order
- [ ] 2-5: Better accuracy figure descriptions
- [ ] 2-5: Fig 7: Why are some slower with no probes
- [ ] 2-6: Fix typo
- [ ] 2-7: Fix citation for Stewart 2010

Reviewer 1
==========

1. What are the main findings reported in this manuscript?
----------------------------------------------------------

The main contribution of this work is a benchmarking suite designed to
test neuron simulators in a relevant and objective way. This is
performed by analyzing three fundamental metrics - compliance,
accuracy, and speed - under different network test
conditions. Compliance metrics determine feature coverage for a neural
simulator, while the accuracy and speed metrics are tested under four
neurally-relevant operations: representation with robustness to noise,
nonlinear computation, stability with recurrent dynamics, and
large-scale interaction of multiple recurrent populations, all
implemented with neurons. Finally, five neural simulators with
different algorithmic and hardware optimizations are tested on these
benchmarks.

2. Other comments on the introduction.
--------------------------------------

The introduction is well-written and motivates the study; the
background provides sufficient detail to understand the architecture
of this solution.

3. Other comments on the materials and methods.
-----------------------------------------------

The materials and methods describes well the metrics and models used
to evaluate the backends.

4. Other comments on the results.
---------------------------------

1. Further clarification should be given as to why the SpiNNaker
backend was not tested for compliance, as lines 276-77 are not
sufficient. The reason is not clear as build and run time for the
examined models in Figures 5-7 do not seem prohibitive to running 212
tests; additionally, SpiNNaker supports a wide variety of neuron
models and parameters, so it appears adequate to support the necessary
descriptions required by Nengo. Please clarify.

2. Lines 320-325 are not clear.

a) While Figure 6 does show an increase for the Nengo reference
backend run times by removing passthrough nodes, the run time appears
to be a 15% increase (~7x vs ~6x slower than real-time, Figure 6
green, BG Sequence to BG Sequence *), which is approximately the same
relative speedup as that offered by removing probes for the SpiNNaker
backend (~1.5x to ~1.2x, Figures 6 and 7, BG sequence, blue). So,
"significant" is a strong claim and should be clarified.

b) Additionally, Figure 7 seems to indicate that removing probes
actually makes the network slower for the reference backend for BG
sequence * (~8x vs ~6.8x, Figures 6 and 7, light blue, BG Sequence
*). Either outliers / standard deviations are stronger than they
appear from the plot, or the reason for the network slowing down with
probes removed should be explained.

c) Finally, the speedup by removing passthrough nodes for the OpenCL
backend (Figure 6, green, BG sequence to BG sequence*) disappears once
probes are removed (Figure 7, green, BG sequence to BG sequence*).

Essentially, please verify that the error bars on the plots are
representative of the true confidence intervals. If they are correct,
there seem to be some anomalies in the data (removing reporting output
slows down the reference backend for BG*, speedups in OpenCL become
slowdowns once reporting output is removed). If this all has to do
with build time / overhead / short runtimes / network latency, then
that should be mentioned in the text.

3. In Figure 3, the meaning of negative frequencies (-1 Hz, -2 Hz)
should be at least briefly mentioned. Presumably, since this is a
circular oscillator, it is being run in reverse. However, it's not
clear to me why negative frequencies should be at all different than
positive frequencies, and how the range -2 Hz to 2 Hz was chosen. A
citation that references this range in biology for CPGs, for example,
would bolster this choice.

4. Table 1, the compliance of the four backends, should be explained
more fully in the caption. The levels of coverage are surprisingly low
given that all backends are able to perform the main cognitive-level
tasks; common failure cases (e.g., missing neuron models) should be
mentioned to show why these are not necessary.

5. Other comments on the discussion or the conclusions.
-------------------------------------------------------

The initially stated conclusion that significant speedups can be
obtained with specialized hardware without sacrificing accuracy is
good, although perhaps not very surprising. However, the greater
challenge of creating a list of cognitively-relevant tasks and an
infrastructure for objective testing is significant. Moreover, the
improved accuracy of SpiNNaker with passthrough nodes removed,
discovered by these tests, is an encouraging sign that the
optimization loop of hardware and implementation through this test
framework can yield real improvements.

The biggest omission from this discussion and the manuscript is any
mention of efficiency. Neuromorphic systems have long held that their
primary advantage is significant efficiency, and the lack of ability
of the benchmarking to capture that is unfortunate. This could perhaps
be implemented as an optional query on the backend; the power
consumption of most CPUs and GPUs can be publicly referenced and
approximated, or the implementation could provide its own statistics
for specialized hardware. Perhaps the Brainstorm backend’s main
advantage is in power efficiency, and there should be resulting
statistics that can show that. Regardless of implementation, the
authors should at least mention that efficiency could be evaluated in
future work.

6. Please add here any further comments on this manuscript.
--------------------------------------------------------

This work addresses a very challenging topic - that is, how to
objectively compare systems designed for different objectives in a
high-dimensional benchmarking space. The approach of choosing
cognitive tasks and measuring the ability of neuromorphic systems to
perform them is insightful and relevant.

It does, however, represent only an initial step towards obtaining the
necessary concrete metrics to measure neuromorphic systems. Many
quantities remain untested in this framework; researchers who build
neuromorphic systems designed for neural simulation, the target
audience of this manuscript, focus on optimizing many of the following
quantities: simulation speed, simulation accuracy, energy per synaptic
event, accurate timing, number of neurons represented, number of
connections represented, repertoire of neural models, online learning,
and likely others. Of these, the test framework objectively compares
only along the first two, though the compliance tests likely would
stress some of the others. I hope to see future work along these lines
to expand the reach of these tests.

Nonetheless, this work provides a substantive proposal to begin
evaluating neuromorphic neural simulators.

Reviewer 2
==========

1. What are the main findings reported in this manuscript?
----------------------------------------------------------

This paper describes how the Nengo test suite can be used for
benchmarking neuromorphic systems and compare them to neural
simulators on general-purpose computers. It introduces the Nengo test
suite, describes three benchmark metrics (compliance, accuracy, speed)
and shows benchmark results for four tests on five different
backends. Of these backends, only one is actually running on
neuromorphic hardware, one is a simulator of a neuromorphic system,
and three are software simulators (with one employing GPUs). Benchmark
results are shortly discussed.

2. Does the introduction present the study in an appropriate context?
---------------------------------------------------------------------

No

The introduction gives a clear motivation for the work in the article,
but it does not state which works have been done previously on that
topic. For example, there are several articles investigating accuracy
in neuromorphic hardware for specific benchmark problems. As three of
the backends are software-based, it would also be appropriate here to
cite prior work on accuracy/speed in neural software simulators.

3. Other comments on the introduction.
--------------------------------------

As the Nengo test suite was not designed for benchmarking, it would be
helpful to have some indications on the limitations of the method (its
potential is described already pretty clear) - this could be done in
the Discussion section as well.

4. Other comments on the materials and methods.
-----------------------------------------------

I found the separation in Background and Methods helpful for
understanding, even if it does not follow the standard article
structure. Some points should be clarified:

- The benchmarks make use of current input to neurons. However, quite
  a lot of neuromorphic systems do only offer spike input, or current
  inputs are not so flexible to program. Of course, current input can
  be emulated by spike input, but that may add some additional
  noise/inaccuracy. This should be dicsussed in the Background/Methods
  sections; also, an indication on how the currents look like in the
  benchmark models would be helpful, so that designers of neuromorphic
  systems get an idea of what would be required.

- At several points, the authors mention that seeds can be set
  explicitely for deterministic experiment runs. Is there a reason for
  this? For benchmarking, setting a fixed seed is misleading in my
  opinion, as it suggests that all backends run exactly the same
  experiment. However, as the order in which the single parts of a
  network are generated is not the same, this is not the case in
  general. Furthermore, neuromorphic hardware systems may use built-in
  noise sources (i.e. true random numbers). All that requires a
  statistical comparison of results over several experiment
  repetitions, as the authors do in their benchmarks.

- The authors state that Nengo is well-suited for generating large
  networks. However, the tests they present are only limited in
  size. A comment on larger benchmark models in the test suite and/or
  the possibility to scale up the present benchmarks would be
  desirable.

Minor:

- I found the heading of section 2.2 ("Fuzzy testing") puzzling - is
  this a fixed term I am missing? In any case, it would be helpful to
  explain the term.

- Table 2 is referenced before Table 1 in the text - their order
  should be changed

5. Other comments on the results.
---------------------------------

I found the description of the Figures on accuracy too short. Even if
the accuracy results themselves are not the main focus of the article,
some more explanations for the results should be given. In particular,
in Figs. 1 and 2, why does the Nengo reference backend show a
significantly higher variability than the Brainstorm and distilled
backends? In Figs. 3 and 4, where do the deviations in the SpiNNaker
backend come from (my first guess would be the employed 1ms time step,
which is larger than the 0.1ms typically used in software simulators)?

Also, the whiskers in Figs. 1-4 seem to be only multiples of the box
sizes, so plotting them does not add any information - it may be even
misleading when not carefully reading the caption.

Some of the results in Fig. 7 are puzzling: For BG sequence*, the run
time for nengo and nengo_ocl is even higher without probes (compared
to Fig. 6), being well outside the 95% confidence intervals. This
should be explained.

6. Other comments on the discussion or the conclusions.
-------------------------------------------------------

As already mentioned for the Introduction, it would make the
Discussion section much more balanced if the limitations of the
approach would be discussed as well, together with some outlook to
potential improvements or complementary approaches.

Minor:

- typo in line 373: "We believe that THE these benchmarks..."

7. Please add here any further comments on this manuscript.
-----------------------------------------------------------

Overall, the article presents an attractive idea for benchmarking
neuromorphic systems. In my opinion its main weakness is the lack of
embedding in the current literature. Apart from that, it is a nice
contribution to the field, and the open source code is a good
opportunity for other neuromorphic system operators for benchmarking
their systems.

Minor:

- missing citation details for Stewart et al. 2010

### 2015-09-13 paper/paper.tex
Update requirements, including Nengo

@@
 
-As of version 2.0.1, Nengo's full test suite contains 618 tests.
+As of September 2015, Nengo's full test suite contains 643 tests.
 Many tests are unit tests
 that ensure the frontend API operates as expected.
-212 tests construct a simulator instance,
+289 tests construct a simulator instance,
 run the simulator, and test the output of that model
@@
 For the remainder of this paper,
-we will focus only on these 212 functional tests.
+we will focus only on these 289 functional tests.
 

### 2015-09-13 fnme/benchmarks.py

@@ -110,8 +110,7 @@ def test_product(Simulator, plt, seed, outfile, probes):
         ens_direct = nengo.Node(output=lambda t, x: x[0] * x[1], size_in=2)
         nengo.Connection(stimulus, ens_direct)
         if probes:
-            probe_inp = nengo.Probe(
-                product_net.product.ensembles[0], synapse=0.005)
+            probe_inp = nengo.Probe(stimulus, synapse=0.005)
             probe_direct = nengo.Probe(ens_direct)
             probe_test = nengo.Probe(product_net.output, synapse=0.005)
 

### 2015-09-13 fnme/plots.py

@@ -99,7 +99,7 @@ def get_data(task, key, separate_cols=True, probes=True):
         data = OrderedDict()
     else:
         data = []
-    dirs = [d for d in os.listdir(data_dir)
+    dirs = [d for d in sorted(os.listdir(data_dir))
             if '.sim' in d]
     sims = [os.path.basename(d).split('.')[0] for d in dirs]
 
@@ -211,6 +211,11 @@ def speed(probes=True):
     inset = zoomed_inset_axes(plt.gca(), 0.38,
                               bbox_to_anchor=(0.6, 0.98),
                               bbox_transform=plt.gcf().transFigure)
+
+    # Have to remove non-BG models before plotting inset
+    run = run[run['Model'] != "Chained channels"]
+    run = run[run['Model'] != "Product"]
+    run = run[run['Model'] != "Oscillator"]
     sns.barplot(x='Model', y='runtime', hue='Backend',
                 data=run, ax=inset, order=model_order)
     plt.axhline(1.0, lw=1, c='k', ls=':')

### 2015-09-13 make.py

@@ -41,21 +41,21 @@ def task_paper():
 
 
 def task_compliance():
-    def run_tests(backend, pytest_args='', cwd='.'):
+    def run_tests(backend, pytest_args, cwd):
         result = '{}/results/{}.txt'.format(root, backend)
-        pytest = ('py.test --benchmarks --optional'
-                  ' {} > {}'.format(pytest_args, result))
+        pytest = ('py.test --neurons nengo.Direct,nengo.LIF --slow --plots '
+                  '--analytics -- {} > {}'.format(pytest_args, result))
         action = CmdAction(pytest, cwd=cwd)
         return {'name': backend,
                 'actions': ['rm -f {}'.format(result), action],
                 'targets': [result],
                 'uptodate': [check_timestamp_unchanged(cwd)]}
     yield run_tests('nengo_ocl', 'nengo_ocl/tests/test_sim_ocl.py',
-                    cwd=os.path.join(os.pardir, 'nengo_ocl'))
+                    os.path.join(os.pardir, 'nengo_ocl'))
     yield run_tests('nengo_distilled', 'nengo_distilled/tests/test_nengo.py',
-                    cwd=os.path.join(os.pardir, 'nengo_distilled'))
+                    os.path.join(os.pardir, 'nengo_distilled'))
     yield run_tests('nengo_brainstorm', 'nengo_brainstorm/tests/test_nengo.py',
-                    cwd=os.path.join(os.pardir, 'nef-chip-hardware'))
+                    os.path.join(os.pardir, 'nef-chip-hardware'))
 
 
 def task_benchmarks():

### 2015-09-13 fnme/benchmarks.py
Add seed to BG sequence model
Whoops!

@@ -311,7 +311,7 @@ def _test_sequence(Simulator, plt, seed, outfile, probes, prune_passthrough):
     T = 4.0
     seq_length = 6
 
-    with spa.SPA() as model:
+    with spa.SPA(seed=seed) as model:
         model.state = spa.Memory(dimensions=dimensions,
                                  subdimensions=subdimensions)
 

### 2015-09-13 fnme/plots.py
Not on Mac OS X anymore

@@ -16,9 +16,10 @@ results_dir = os.path.realpath(os.path.join(root, os.pardir, 'results'))
 noprobes_dir = os.path.join(results_dir, 'noprobes')
 results_dir = os.path.join(results_dir, 'probes')
 fig_dir = os.path.realpath(os.path.join(root, os.pardir, 'figures'))
-# Change if not on Mac OS X
-inkscape = os.path.expanduser("~/Applications/Inkscape.app/Contents"
-                              "/Resources/bin/inkscape")
+inkscape = "inkscape"
+# Uncomment if on Mac OS X
+# inkscape = os.path.expanduser("~/Applications/Inkscape.app/Contents"
+#                               "/Resources/bin/inkscape")
 
 onecolumn = 3.34646  # inches
 twocolumn = 7.08661  # inches

### 2015-09-13 make.py
Add task to download data from figshare

@@ -23,6 +23,28 @@ def task_reset():
                         'rm -rf ./results/noprobes']}
 
 
+def task_download_data():
+    """Downloads analyzed data from Figshare."""
+    def download_data(article_id):
+        import json
+        import requests
+        r = requests.get("http://api.figshare.com/v1/articles/" + article_id)
+        detail = json.loads(r.content)
+        for file_info in detail['items'][0]['files']:
+            outpath = os.path.join(root, file_info['name'])
+            if os.path.exists(outpath):
+                print("%s exists. Skipping." % outpath)
+                continue
+            with open(outpath, 'wb') as outf:
+                print("Downloading %s..." % outpath)
+                dl = requests.get(file_info['download_url'])
+                outf.write(dl.content)
+    return {'actions': [(download_data, ['1496569']),
+                        "unzip results.zip",
+                        "rm -f results.zip",
+                        "rm -rf __MACOSX"]}
+
+
 def task_paper():
     d = os.path.join(root, 'paper')
 

### 2015-09-13 make.py
Better figure generation
With the file_dep and targets, it will now skip plots that have
been generated recently.

@@ -101,22 +101,44 @@ def task_benchmarks():
 
 
 def task_figures():
+    figdir = os.path.join(root, 'figures')
+    plotdir = os.path.join(root, 'plots')
+    plotfile = os.path.join(root, 'fnme', 'plots.py')
+    benchfile = os.path.join(root, 'fnme', 'benchmarks.py')
+    figexts = ('pdf', 'svg', 'eps')
+    acc_plots = [os.path.join(plotdir, 'accuracy-%d.svg' % (i+1))
+                 for i in range(4)] + [os.path.join(
+                     plotdir, 'accuracy-4-pruned.svg')]
+    res_plots = [os.path.join(plotdir, 'results-%d.svg' % (i+1))
+                 for i in range(5)]
+
     yield {'name': 'models',
            'actions': [CmdAction(
                'py.test -p fnme.options --simulator nengo.Simulator '
                '--seed 5 --plot plots --noprofile -- fnme/benchmarks.py',
-               cwd=root)]}
+               cwd=root)],
+           'file_dep': [plotfile, benchfile],
+           'targets': res_plots}
     yield {'name': 'accuracy',
-           'actions': [(fnme.plots.accuracy,)]}
+           'actions': [(fnme.plots.accuracy,)],
+           'file_dep': [plotfile],
+           'targets': acc_plots}
     yield {'name': 'speed',
-           'actions': [(fnme.plots.speed, (True,))]}
+           'actions': [(fnme.plots.speed, (True,))],
+           'targets': [os.path.join(figdir, 'fig%d.%s' % (i, ext))
+                       for ext in figexts for i in range(5, 7)]}
     yield {'name': 'speed-np',
-           'actions': [(fnme.plots.speed, (False,))]}
+           'actions': [(fnme.plots.speed, (False,))],
+           'targets': [os.path.join(figdir, 'fig7.%s' % ext)
+                       for ext in figexts]}
     yield {'name': 'combine',
            'actions': [(fnme.plots.fig1,),
                        (fnme.plots.fig2,),
                        (fnme.plots.fig3,),
-                       (fnme.plots.fig4,)]}
+                       (fnme.plots.fig4,)],
+            'file_dep': acc_plots + res_plots,
+            'targets': [os.path.join(figdir, 'fig%d.%s' % (i, ext))
+                        for ext in figexts for i in range(1, 5)]}
 
 
 if __name__ == '__main__':

### 2015-09-13 paper/rebuttals.txt
Edits in response to reviewer feedback

@@
-Todo list
-=========
-
-Work
-
-- [ ] 1-4: Try to get unit tests running SpiNNaker
-- [ ] 1-4: Why does removing probes slow down reference?
-- [ ] 1-4: Ensure confidence intervals are real things
-- [ ] 2-2: Find some citations of previous neuromorphic / simulator benchmarking
-- [ ] 2-4: Collect information about current inputs?
-- [ ] 2-5: Use different boxplot whisker type?
-
-Writing
-
-- [ ] 1-4: Rewrite lines 320-325
-- [ ] 1-4: Write something about negative frequencies
-- [ ] 1-4: Look up CPG frequencies or something
-- [ ] 1-4: Explain compliance more (Table 1 especially)
-- [ ] 1-5: Add discussion paragraph on efficiency
-- [ ] 2-3: Add text on limitations to introduction / discussion
-- [ ] 2-4: Add discussion on current input vs spike input?
-- [ ] 2-4: Discuss why you'd want to set seeds
-- [ ] 2-4: Comment on larger networks
-- [ ] 2-4: Define fuzzy testing
-- [ ] 2-4: Change table 1, 2 order
-- [ ] 2-5: Better accuracy figure descriptions
-- [ ] 2-5: Fig 7: Why are some slower with no probes
-- [ ] 2-6: Fix typo
-- [ ] 2-7: Fix citation for Stewart 2010
-
 Reviewer 1
@@
 
-The main contribution of this work is a benchmarking suite designed to
-test neuron simulators in a relevant and objective way. This is
-performed by analyzing three fundamental metrics - compliance,
-accuracy, and speed - under different network test
-conditions. Compliance metrics determine feature coverage for a neural
-simulator, while the accuracy and speed metrics are tested under four
-neurally-relevant operations: representation with robustness to noise,
-nonlinear computation, stability with recurrent dynamics, and
-large-scale interaction of multiple recurrent populations, all
-implemented with neurons. Finally, five neural simulators with
-different algorithmic and hardware optimizations are tested on these
-benchmarks.
+> The main contribution of this work is a benchmarking suite designed
+> to test neuron simulators in a relevant and objective way. This is
+> performed by analyzing three fundamental metrics - compliance,
+> accuracy, and speed - under different network test
+> conditions. Compliance metrics determine feature coverage for a
+> neural simulator, while the accuracy and speed metrics are tested
+> under four neurally-relevant operations: representation with
+> robustness to noise, nonlinear computation, stability with recurrent
+> dynamics, and large-scale interaction of multiple recurrent
+> populations, all implemented with neurons. Finally, five neural
+> simulators with different algorithmic and hardware optimizations are
+> tested on these benchmarks.
 
@@
 
-The introduction is well-written and motivates the study; the
-background provides sufficient detail to understand the architecture
-of this solution.
+> The introduction is well-written and motivates the study; the
+> background provides sufficient detail to understand the architecture
+> of this solution.
 
@@
 
-The materials and methods describes well the metrics and models used
-to evaluate the backends.
+> The materials and methods describes well the metrics and models used
+> to evaluate the backends.
 
@@
 
-1. Further clarification should be given as to why the SpiNNaker
-backend was not tested for compliance, as lines 276-77 are not
-sufficient. The reason is not clear as build and run time for the
-examined models in Figures 5-7 do not seem prohibitive to running 212
-tests; additionally, SpiNNaker supports a wide variety of neuron
-models and parameters, so it appears adequate to support the necessary
-descriptions required by Nengo. Please clarify.
+> 1. Further clarification should be given as to why the SpiNNaker
+> backend was not tested for compliance, as lines 276-77 are not
+> sufficient. The reason is not clear as build and run time for the
+> examined models in Figures 5-7 do not seem prohibitive to running
+> 212 tests; additionally, SpiNNaker supports a wide variety of neuron
+> models and parameters, so it appears adequate to support the
+> necessary descriptions required by Nengo. Please clarify.
 
-2. Lines 320-325 are not clear.
+You are completely correct that this comment is not sufficient.
+A technical answer would be that SpiNNaker has a lot of
+set up and tear down code, which makes running the test suite
+slow and error-prone. The tests creates a large number of
+small models and runs them for small amounts of time;
+this results in the SpiNNaker boards' memory filling up with
+improperly freed resources. So, the real answer is more a
+time management one; we decided that getting the unit tests
+running would take too much time for this paper.
+However, this answer is not very satisfying, so we have
+put in the time to run the test suite with the SpiNNaker
+backend. Table 1 (now Table 2) now also gives results
+for the SpiNNaker backend, and the text has been updated
+accordingly.
 
-a) While Figure 6 does show an increase for the Nengo reference
-backend run times by removing passthrough nodes, the run time appears
-to be a 15% increase (~7x vs ~6x slower than real-time, Figure 6
-green, BG Sequence to BG Sequence *), which is approximately the same
-relative speedup as that offered by removing probes for the SpiNNaker
-backend (~1.5x to ~1.2x, Figures 6 and 7, BG sequence, blue). So,
-"significant" is a strong claim and should be clarified.
+> 2. Lines 320-325 are not clear.
 
-b) Additionally, Figure 7 seems to indicate that removing probes
-actually makes the network slower for the reference backend for BG
-sequence * (~8x vs ~6.8x, Figures 6 and 7, light blue, BG Sequence
-*). Either outliers / standard deviations are stronger than they
-appear from the plot, or the reason for the network slowing down with
-probes removed should be explained.
+> a) While Figure 6 does show an increase for the Nengo reference
+> backend run times by removing passthrough nodes, the run time appears
+> to be a 15% increase (~7x vs ~6x slower than real-time, Figure 6
+> green, BG Sequence to BG Sequence *), which is approximately the same
+> relative speedup as that offered by removing probes for the SpiNNaker
+> backend (~1.5x to ~1.2x, Figures 6 and 7, BG sequence, blue). So,
+> "significant" is a strong claim and should be clarified.
 
-c) Finally, the speedup by removing passthrough nodes for the OpenCL
-backend (Figure 6, green, BG sequence to BG sequence*) disappears once
-probes are removed (Figure 7, green, BG sequence to BG sequence*).
+Good point. We used 'significant' colloquially here and
+have reworded this paragraph; it now reads:
 
-Essentially, please verify that the error bars on the plots are
-representative of the true confidence intervals. If they are correct,
-there seem to be some anomalies in the data (removing reporting output
-slows down the reference backend for BG*, speedups in OpenCL become
-slowdowns once reporting output is removed). If this all has to do
-with build time / overhead / short runtimes / network latency, then
-that should be mentioned in the text.
+  While passthrough nodes were removed in the basal ganglia sequence
+  model for improved accuracy, it is interesting to note that speed is
+  also impacted in this version of the model.  While the distilled and
+  Brainstorm backends are unaffected, both the SpiNNaker and OpenCL
+  backends run faster when passthrough nodes are removed.  This result
+  indicates that passthrough nodes contribute to SpiNNaker's overhead.
+  The reference backend, on the other hand, runs slower, indicating
+  that the computational costs of the additional connections
+  introduced when removing passthrough nodes are greater than the
+  costs of the passthrough nodes.
 
-3. In Figure 3, the meaning of negative frequencies (-1 Hz, -2 Hz)
-should be at least briefly mentioned. Presumably, since this is a
-circular oscillator, it is being run in reverse. However, it's not
-clear to me why negative frequencies should be at all different than
-positive frequencies, and how the range -2 Hz to 2 Hz was chosen. A
-citation that references this range in biology for CPGs, for example,
-would bolster this choice.
+> b) Additionally, Figure 7 seems to indicate that removing probes
+> actually makes the network slower for the reference backend for BG
+> sequence * (~8x vs ~6.8x, Figures 6 and 7, light blue, BG Sequence
+> *). Either outliers / standard deviations are stronger than they
+> appear from the plot, or the reason for the network slowing down with
+> probes removed should be explained.
 
-4. Table 1, the compliance of the four backends, should be explained
-more fully in the caption. The levels of coverage are surprisingly low
-given that all backends are able to perform the main cognitive-level
-tasks; common failure cases (e.g., missing neuron models) should be
-mentioned to show why these are not necessary.
+We did not notice the slowdown upon initial submission,
+so seeing this was puzzling to us as well.
+To investigate whether this effect was real,
+we first replicated it on two additional machines;
+the version without probes was significantly slower
+than the version with probes on all machines,
+as measured by non-overlapping
+bootstrapped 95% confidence intervals.
+Then, we investigated the internal structures of the two
+versions of networks, in terms of the step functions
+produced by them.
+The version with probes had 600 step functions;
+595 of these implemented the same equations
+as the networks without probes, while the
+remaining five functions implemented the probing.
+The simulator loop also indicated that
+the version without probes should have executed
+strictly fewer operations than the version with probes.
+We conclude that the reason for the speedup
+must have been somehow related to
+a lower level of abstraction than we investigated
+(e.g., the data was better organized in RAM
+in the version with probes).
+
+Very few networks in Nengo have zero probes,
+so there were some obvious opportunities to optimize
+the reference backend for the special case
+in which no probes exist. After implementing
+two such optimizations, we were able to consistently
+achieve identical performance with probes and without.
+However, it was not our intention to perform
+a detailed comparison of the affect of probes
+on runtimes, and we feel that including Figure 7
+(which only had a few sentences of text associated with it)
+was more distracting than illuminating.
+For these reasons, we have removed Figure 7 in this revision.
+
+> c) Finally, the speedup by removing passthrough nodes for the OpenCL
+> backend (Figure 6, green, BG sequence to BG sequence*) disappears once
+> probes are removed (Figure 7, green, BG sequence to BG sequence*).
+
+As discussed above, Figure 7 has now been removed.
+We believe that, with more robust benchmarks
+and investigation of the probe system in the OpenCL backend,
+the speedup would still occur,
+but will address this in future work that focuses
+on probing across multiple backends.
+
+> Essentially, please verify that the error bars on the plots are
+> representative of the true confidence intervals. If they are correct,
+> there seem to be some anomalies in the data (removing reporting output
+> slows down the reference backend for BG*, speedups in OpenCL become
+> slowdowns once reporting output is removed). If this all has to do
+> with build time / overhead / short runtimes / network latency, then
+> that should be mentioned in the text.
+
+We have verified that the error bars reported are bootstrapped 95%
+confidence intervals, as claimed in the figure captions of
+Figures 5 and 6. As previously mentioned, we also replicated
+the paradoxical slowdown with probes removed; however,
+with the removal of Figure 7, we believe that additional text attesting
+to the validity of the confidence intervals is not warranted.
+
+> 3. In Figure 3, the meaning of negative frequencies (-1 Hz, -2 Hz)
+> should be at least briefly mentioned. Presumably, since this is a
+> circular oscillator, it is being run in reverse. However, it's not
+> clear to me why negative frequencies should be at all different than
+> positive frequencies, and how the range -2 Hz to 2 Hz was chosen. A
+> citation that references this range in biology for CPGs, for example,
+> would bolster this choice.
+
+The meaning of negative frequencies has been made explicit in text;
+line 239 now notes that "negative frequencies indicate
+oscillations in the reverse direction." In that line, we have
+also added a footnote with a citation to Duysens and Van de Crommert, 1998,
+which provides some evidence that locomotive CPGs may run in reverse
+for backward locomotion.
+
+In terms of why the range -2 to 2 was chosen,
+this was because we have used oscillators of these frequencies
+in previous model. In line 219 we note that
+"We test each model with parameters typically used
+in large-scale models, but make these parameterized models
+available ... for those who wish to explore additional cases."
+The parameter is trivial to change, up to an upper frequency limit
+which depends on the properties of the neurons in use;
+we would be happy to show results for a different set of frequencies
+if that would be preferable.
+
+> 4. Table 1, the compliance of the four backends, should be explained
+> more fully in the caption. The levels of coverage are surprisingly low
+> given that all backends are able to perform the main cognitive-level
+> tasks; common failure cases (e.g., missing neuron models) should be
+> mentioned to show why these are not necessary.
+
+The caption for the compliance table (which now includes all 5 backends)
+has been updated. It now reads:
+
+  Compliance of the five backends. Compliance is the number of
+  functional tests passed by a particular backend. We have divided
+  these tests into tests parameterized by neuron type, and those not
+  parameterized.  Non-parameterized tests are either designed to work
+  with only one neuron type, or use leaky integreate-and-fire (LIF)
+  neurons, which are implemented on all backends. For parameterized
+  tests, we have separated the compliance for those tests using LIF
+  neurons, which all backends implement, and for any additional neuron
+  types implemented. Since there are 31 parameterized tests, the
+  maximum compliance is 31 times the number of neuron types
+  implemented.  The reference backend implements three additional
+  neuron types, while OpenCL, Distilled, and Brainstorm implement one
+  additional neuron type, and SpiNNaker only implements LIF neurons.
+
+Additionally, a paragraph explaining common failure cases
+is included in the main text in lines 311-321. It reads:
+
+  It should be noted that these test suites are being run on the
+  distilled, Brainstorm, and SpiNNaker backends for the first time in
+  this study.  In other words, these results are the first objective
+  interrogation of each backend's feature set.  In many cases, tests
+  failed by backends are tests of features recently added to Nengo,
+  such as stochastic processes for injecting current noise.  As such,
+  we expect compliance on all backends to rise quickly as backend
+  developers implement these new features.  The OpenCL backend has
+  significantly higher compliance in large part because it is
+  developed by the same group that develops the reference backend.
+  However, there are some notable features missing from some backends,
+  such as learning through plasticity rules applied to
+  neuron-to-neuron connections, and implementation differences, such
+  as one timestep delays on connections with no synaptic filter, that
+  may remain even when backends are brought up to date with the
+  reference implementation.  It is likely that tests will be rewritten
+  in the future to allow some implementation differences if they do
+  not affect simulation accuracy.
 
@@
 
-The initially stated conclusion that significant speedups can be
-obtained with specialized hardware without sacrificing accuracy is
-good, although perhaps not very surprising. However, the greater
-challenge of creating a list of cognitively-relevant tasks and an
-infrastructure for objective testing is significant. Moreover, the
-improved accuracy of SpiNNaker with passthrough nodes removed,
-discovered by these tests, is an encouraging sign that the
-optimization loop of hardware and implementation through this test
-framework can yield real improvements.
+> The initially stated conclusion that significant speedups can be
+> obtained with specialized hardware without sacrificing accuracy is
+> good, although perhaps not very surprising. However, the greater
+> challenge of creating a list of cognitively-relevant tasks and an
+> infrastructure for objective testing is significant. Moreover, the
+> improved accuracy of SpiNNaker with passthrough nodes removed,
+> discovered by these tests, is an encouraging sign that the
+> optimization loop of hardware and implementation through this test
+> framework can yield real improvements.
+>
+> The biggest omission from this discussion and the manuscript is any
+> mention of efficiency. Neuromorphic systems have long held that
+> their primary advantage is significant efficiency, and the lack of
+> ability of the benchmarking to capture that is unfortunate. This
+> could perhaps be implemented as an optional query on the backend;
+> the power consumption of most CPUs and GPUs can be publicly
+> referenced and approximated, or the implementation could provide its
+> own statistics for specialized hardware. Perhaps the Brainstorm
+> backend’s main advantage is in power efficiency, and there should be
+> resulting statistics that can show that. Regardless of
+> implementation, the authors should at least mention that efficiency
+> could be evaluated in future work.
 
-The biggest omission from this discussion and the manuscript is any
-mention of efficiency. Neuromorphic systems have long held that their
-primary advantage is significant efficiency, and the lack of ability
-of the benchmarking to capture that is unfortunate. This could perhaps
-be implemented as an optional query on the backend; the power
-consumption of most CPUs and GPUs can be publicly referenced and
-approximated, or the implementation could provide its own statistics
-for specialized hardware. Perhaps the Brainstorm backend’s main
-advantage is in power efficiency, and there should be resulting
-statistics that can show that. Regardless of implementation, the
-authors should at least mention that efficiency could be evaluated in
-future work.
+This is a great point, and indeed points out one of the weaknesses
+of the "standardization" approach that we are espousing with Nengo:
+new metrics may take a long time to be implemented since they
+must be implemented on all backends.
+
+We have a paragraph to the discussion section
+to discuss this issue, and to register our desire to collect
+efficiency information in future work. Lines 417-423 now read:
+
+  One inherent weakness of using Nengo as a standard platform for
+  benchmarking neuromorphic systems is that new benchmarking
+  capabilities may take a long time to be standardized and developed.
+  If one wishes to add a new metric, such as power consumption, we
+  must first come to a consensus on a suitable interface to this
+  information through Nengo.  Once consensus is reached, it must be
+  implemented and tested on all backends before benchmarks can be
+  written using that quantity.  Despite this limitation, we believe
+  that it is possible to use Nengo to collect power consumption
+  information, and plan to implement efficiency comparisons in future
+  work.
 
@@
 
-This work addresses a very challenging topic - that is, how to
-objectively compare systems designed for different objectives in a
-high-dimensional benchmarking space. The approach of choosing
-cognitive tasks and measuring the ability of neuromorphic systems to
-perform them is insightful and relevant.
+> This work addresses a very challenging topic - that is, how to
+> objectively compare systems designed for different objectives in a
+> high-dimensional benchmarking space. The approach of choosing
+> cognitive tasks and measuring the ability of neuromorphic systems to
+> perform them is insightful and relevant.
 
-It does, however, represent only an initial step towards obtaining the
-necessary concrete metrics to measure neuromorphic systems. Many
-quantities remain untested in this framework; researchers who build
-neuromorphic systems designed for neural simulation, the target
-audience of this manuscript, focus on optimizing many of the following
-quantities: simulation speed, simulation accuracy, energy per synaptic
-event, accurate timing, number of neurons represented, number of
-connections represented, repertoire of neural models, online learning,
-and likely others. Of these, the test framework objectively compares
-only along the first two, though the compliance tests likely would
-stress some of the others. I hope to see future work along these lines
-to expand the reach of these tests.
+> It does, however, represent only an initial step towards obtaining
+> the necessary concrete metrics to measure neuromorphic systems. Many
+> quantities remain untested in this framework; researchers who build
+> neuromorphic systems designed for neural simulation, the target
+> audience of this manuscript, focus on optimizing many of the
+> following quantities: simulation speed, simulation accuracy, energy
+> per synaptic event, accurate timing, number of neurons represented,
+> number of connections represented, repertoire of neural models,
+> online learning, and likely others. Of these, the test framework
+> objectively compares only along the first two, though the compliance
+> tests likely would stress some of the others. I hope to see future
+> work along these lines to expand the reach of these tests.
 
-Nonetheless, this work provides a substantive proposal to begin
-evaluating neuromorphic neural simulators.
+> Nonetheless, this work provides a substantive proposal to begin
+> evaluating neuromorphic neural simulators.
 
@@
 
-This paper describes how the Nengo test suite can be used for
-benchmarking neuromorphic systems and compare them to neural
-simulators on general-purpose computers. It introduces the Nengo test
-suite, describes three benchmark metrics (compliance, accuracy, speed)
-and shows benchmark results for four tests on five different
-backends. Of these backends, only one is actually running on
-neuromorphic hardware, one is a simulator of a neuromorphic system,
-and three are software simulators (with one employing GPUs). Benchmark
-results are shortly discussed.
+> This paper describes how the Nengo test suite can be used for
+> benchmarking neuromorphic systems and compare them to neural
+> simulators on general-purpose computers. It introduces the Nengo
+> test suite, describes three benchmark metrics (compliance, accuracy,
+> speed) and shows benchmark results for four tests on five different
+> backends. Of these backends, only one is actually running on
+> neuromorphic hardware, one is a simulator of a neuromorphic system,
+> and three are software simulators (with one employing
+> GPUs). Benchmark results are shortly discussed.
 
@@
 
-No
+> No
 
-The introduction gives a clear motivation for the work in the article,
-but it does not state which works have been done previously on that
-topic. For example, there are several articles investigating accuracy
-in neuromorphic hardware for specific benchmark problems. As three of
-the backends are software-based, it would also be appropriate here to
-cite prior work on accuracy/speed in neural software simulators.
+> The introduction gives a clear motivation for the work in the
+> article, but it does not state which works have been done previously
+> on that topic. For example, there are several articles investigating
+> accuracy in neuromorphic hardware for specific benchmark
+> problems. As three of the backends are software-based, it would also
+> be appropriate here to cite prior work on accuracy/speed in neural
+> software simulators.
+
+We have added two paragraphs to the introduction citing prior work
+benchmarking SpiNNaker, FACETS, and Brian,
+and situating this study in that context in lines 19-35.
+They read:
+
+  Prior work benchmarking neural simulators and neuromorphic hardware
+  has focused on low-level neural performance.  For example,
+  \citet{sharp2013} showed that SpiNNaker can simulate a recurrent
+  network of leaky integrate-and-fire neurons with similar firing rate
+  and inter-spike intervals as the NEST neural simulator, but around
+  six times faster.  \citet{stromatias2013} showed that SpiNNaker's
+  power consumption varies between 15 and 37 Watts (0.5--0.8 Watts per
+  chip) depending on the number of neurons being simulated.
+  \citet{goodman2008brian} showed that Brian simulated a randomly
+  connected network of 4000 leaky integrate-and-fire twice as fast as
+  an equivalent Matlab implementation, but around three times as slow
+  as a C implementation.  In all of these cases, none of the networks
+  elicited activity that could be directly related to experimentally
+  recorded data on a behavioral task.
+
+  In contrast, \citet{ehrlich2010} and \citet{bruderle2011} have
+  presented a set of benchmarks that target the FACETS neuromorphic
+  system through the PyNN Python package.  These benchmarks include an
+  attractor-based memory model, a model of self-sustained AI states,
+  and a Synfire Chain, all of which are directly related to
+  neuroscientific experiments.  We aim to build on this line of
+  research to provide an unbiased, efficient, and future-proof set of
+  benchmarks that focuses on high-level functional performance using
+  Nengo instead of PyNN.  We have previously shown that Nengo is an
+  order of magnitude faster than the simulators that PyNN targets
+  \citep{bekolay2013}, and have recently implemented backends that
+  target neuromorphic hardware.
 
@@
 
-As the Nengo test suite was not designed for benchmarking, it would be
-helpful to have some indications on the limitations of the method (its
-potential is described already pretty clear) - this could be done in
-the Discussion section as well.
+> As the Nengo test suite was not designed for benchmarking, it would
+> be helpful to have some indications on the limitations of the method
+> (its potential is described already pretty clear) - this could be
+> done in the Discussion section as well.
+
+We have added a paragraph to the discussion noting that Nengo's
+standards-based development and frontend-backend separation mean that
+development can be slow (e.g., collecting power consumption
+would mean figuring out a standard for this and then implementing
+it across all backends) in lines 417-423. It reads:
+
+  One inherent weakness of using Nengo as a standard platform for
+  benchmarking neuromorphic systems is that new benchmarking
+  capabilities may take a long time to be standardized and developed.
+  If one wishes to add a new metric, such as power consumption (as was
+  done in \citealp{stromatias2013}), we must first come to a consensus
+  on a suitable interface to this information through Nengo.  Once
+  consensus is reached, it must be implemented and tested on all
+  backends before benchmarks can be written using that quantity.
+  Despite this limitation, we believe that it is possible to use Nengo
+  to collect power consumption information, and plan to implement
+  energy efficiency comparisons in future work.
 
@@
 
-I found the separation in Background and Methods helpful for
-understanding, even if it does not follow the standard article
-structure. Some points should be clarified:
+> I found the separation in Background and Methods helpful for
+> understanding, even if it does not follow the standard article
+> structure. Some points should be clarified:
+>
+> - The benchmarks make use of current input to neurons. However,
+>   quite a lot of neuromorphic systems do only offer spike input, or
+>   current inputs are not so flexible to program. Of course, current
+>   input can be emulated by spike input, but that may add some
+>   additional noise/inaccuracy. This should be dicsussed in the
+>   Background/Methods sections; also, an indication on how the
+>   currents look like in the benchmark models would be helpful, so
+>   that designers of neuromorphic systems get an idea of what would
+>   be required.
 
-- The benchmarks make use of current input to neurons. However, quite
-  a lot of neuromorphic systems do only offer spike input, or current
-  inputs are not so flexible to program. Of course, current input can
-  be emulated by spike input, but that may add some additional
-  noise/inaccuracy. This should be dicsussed in the Background/Methods
-  sections; also, an indication on how the currents look like in the
-  benchmark models would be helpful, so that designers of neuromorphic
-  systems get an idea of what would be required.
+This is an excellent point that we really should have addressed
+in the initial submission. The paper that we cited in the section
+on the SpiNNaker backend (Mundy et al., 2015) gives a detailed
+account of how SpiNNaker uses decoded values to change the
+input currents to individual neurons, and a prior publication
+(Galluppi et al., 2012, which is now cited) describes a process
+to implement Nengo with primarily spike-based communication
+on SpiNNaker. We have added a paragraph to the Methods section
+with brief descriptions of how SpiNNaker handles currents,
+and how other neuromorphic hardware can be made to handle
+currents from Nengo as well in lines 285-297.
+The paragraph reads:
 
-- At several points, the authors mention that seeds can be set
-  explicitely for deterministic experiment runs. Is there a reason for
-  this? For benchmarking, setting a fixed seed is misleading in my
-  opinion, as it suggests that all backends run exactly the same
-  experiment. However, as the order in which the single parts of a
-  network are generated is not the same, this is not the case in
-  general. Furthermore, neuromorphic hardware systems may use built-in
-  noise sources (i.e. true random numbers). All that requires a
-  statistical comparison of results over several experiment
-  repetitions, as the authors do in their benchmarks.
+  Unlike software backends, considerable effort is taken to translate
+  a Nengo model into something that can run on a SpiNNaker board.
+  Fortunately, SpiNNaker can be reprogrammed as it is composed of a
+  large collection of chips, each with 18 ARM processing cores.  In
+  particular, this allows SpiNNaker to take advantage of Nengo's
+  encoding and decoding capabilities, greatly reducing the amount of
+  RAM needed \citep{mundy2015}.  The SpiNNaker backends accomplishes
+  this by using decoded values to determine changes to the input
+  currents to each neuron, rather than using purely spike-based
+  transmission.  However, a previous implementation of a Nengo
+  SpiNNaker backend \citep{galluppi2012} used primarily spike-based
+  communication, only making an explicit signal-to-spike encoding at
+  the beginning of the network and an explicit spike-to-signal
+  decoding at the end of a network.  Neuromorphic hardware that can
+  only communicate through spikes can be made to interact with Nengo
+  through explicit encoding and decoding processes like the one used
+  in \citealp{galluppi2012}, or by using Nengo on the host machine to
+  explicitly generate spike patterns that are communicated to the
+  device.  However, these methods may introduce additional noise in
+  the simulation, resulting in inaccuracies.
 
-- The authors state that Nengo is well-suited for generating large
-  networks. However, the tests they present are only limited in
-  size. A comment on larger benchmark models in the test suite and/or
-  the possibility to scale up the present benchmarks would be
-  desirable.
+> - At several points, the authors mention that seeds can be set
+>   explicitely for deterministic experiment runs. Is there a reason
+>   for this? For benchmarking, setting a fixed seed is misleading in
+>   my opinion, as it suggests that all backends run exactly the same
+>   experiment. However, as the order in which the single parts of a
+>   network are generated is not the same, this is not the case in
+>   general. Furthermore, neuromorphic hardware systems may use
+>   built-in noise sources (i.e. true random numbers). All that
+>   requires a statistical comparison of results over several
+>   experiment repetitions, as the authors do in their benchmarks.
 
-Minor:
+Fair point. For logistical reasons, it is often nice to be able
+to set a seed and track it; for example, in collecting data for
+this paper, each model's results are stored in a file whose name
+includes the seed. This makes it easy to ensure that the same
+model is not run twice, biasing the sample.
+However, in general, it is true that setting seeds is not important
+for benchmarking. For this reason, we have removed the mentions
+of setting seeds, including references to the `rng` and `seed`
+fixtures. We have kept one reference in the Background section discussing
+the frontend interface, but have  reworded that it slightly;
+it now reads:
 
-- I found the heading of section 2.2 ("Fuzzy testing") puzzling - is
-  this a fixed term I am missing? In any case, it would be helpful to
-  explain the term.
+  The only parameter on the network is an optional integer seed;
+  setting this should make all of the random factors in the model
+  deterministic, which is important for testing and debugging models,
+  but is not used for benchmarking.
 
-- Table 2 is referenced before Table 1 in the text - their order
-  should be changed
+> - The authors state that Nengo is well-suited for generating large
+>   networks. However, the tests they present are only limited in
+>   size. A comment on larger benchmark models in the test suite
+>   and/or the possibility to scale up the present benchmarks would be
+>   desirable.
+
+We have added an explicit mention of the size of Spaun on lines 401-402
+(since Spaun is built with Nengo and shows that it is possible
+to generate large networks). We have also added a short paragraph
+to the Test models subsection discussing larger models;
+see lines 255-259 which read:
+
+  We have used relatively small models run for short times in order to
+  run many iterations on all backends.  However, all of these models
+  could be made significantly larger by increasing the number of
+  neurons used (i.e., adjusting the \texttt{n\_neurons} parameter on
+  ensembles), and increasing the dimensionality of the signals
+  represented in the model.  Additionally, existing tests of the
+  semantic pointer architecture within Nengo use significantly more
+  neurons than the models presented here, and could be adapted into
+  benchmarks.
+
+> Minor:
+>
+> - I found the heading of section 2.2 ("Fuzzy testing") puzzling - is
+>   this a fixed term I am missing? In any case, it would be helpful
+>   to explain the term.
+
+The term "Fuzzy testing" borrows from the concept of Fuzzy logic
+from computer science. However, upon searching for other uses
+of the term, we noticed that the term "Fuzz testing" is commonly
+used to refer to automated testing with random data.
+In order to avoid confusion with "Fuzz testing",
+and to avoid inventing new parlance for litte gain,
+we have changed the heading of section 2.2 to "Functional testing",
+and have removed other references to "fuzzy testing".
+
+> - Table 2 is referenced before Table 1 in the text - their order
+>   should be changed
+
+Thank you, this has been corrected.
 
@@
 
-I found the description of the Figures on accuracy too short. Even if
-the accuracy results themselves are not the main focus of the article,
-some more explanations for the results should be given. In particular,
-in Figs. 1 and 2, why does the Nengo reference backend show a
-significantly higher variability than the Brainstorm and distilled
-backends? In Figs. 3 and 4, where do the deviations in the SpiNNaker
-backend come from (my first guess would be the employed 1ms time step,
-which is larger than the 0.1ms typically used in software simulators)?
+> I found the description of the Figures on accuracy too short. Even
+> if the accuracy results themselves are not the main focus of the
+> article, some more explanations for the results should be given. In
+> particular, in Figs. 1 and 2, why does the Nengo reference backend
+> show a significantly higher variability than the Brainstorm and
+> distilled backends? In Figs. 3 and 4, where do the deviations in the
+> SpiNNaker backend come from (my first guess would be the employed
+> 1ms time step, which is larger than the 0.1ms typically used in
+> software simulators)?
 
-Also, the whiskers in Figs. 1-4 seem to be only multiples of the box
-sizes, so plotting them does not add any information - it may be even
-misleading when not carefully reading the caption.
+We have added additional details in the section 4.2 on accuracy.
+These additional details are listed below.
 
-Some of the results in Fig. 7 are puzzling: For BG sequence*, the run
-time for nengo and nengo_ocl is even higher without probes (compared
-to Fig. 6), being well outside the 95% confidence intervals. This
-should be explained.
+We are still in the progress of investigating the deviations
+in the SpiNNaker backend; however, we are collaborating with
+the SpiNNaker group to improve accuracy on these examples.
+The 1ms time step is not the issue here, however,
+as all of the backends tested use a 1ms time step.
+
+Figure 1:
+
+  The Brainstorm and distilled backends have the least variability and
+  the SpiNNaker backend has the most variability, though the median
+  RSME is the same across all backends.  One driver of these
+  differences is in how each backend implement synaptic filtering.
+  The reference and OpenCL backends, for example, implement arbitrary
+  linear time-invariant filters, of which the lowpass filter used in
+  this model is a specific example.  The Brianstorm and distilled
+  backends only support lowpass filters, and therefore implement it
+  more accurately.  Another reason for these differences is in how
+  each backend handles ensembles operating near the edge of their
+  representational range (i.e., the radius of the ensemble).  The
+  outlier with highest RMSE represents a model instance in which the
+  static vector target was at the extreme of the representational
+  range; the SpiNNaker backend's relatively high RMSE on this example
+  indicates that it may not perform as well as other backends in this
+  situation.  However, accuracy could be improved by increasing the
+  representational range, though doing so may necessitate an increase
+  in the number of evaluation points generated when solving for
+  decoding weights.
+
+Figure 2:
+
+  Again, the more generic synaptic filtering model used in the
+  reference and OpenCL backends is the likely cause of increased
+  variability on this model.  It is also likely that performance at
+  the extremes of the representational range is responsible for the
+  SpiNNaker backend's reduced accuracy, though we have not
+  investigated this in detail.
+
+Figure 3:
+
+  In this example, differences in synaptic filtering are more
+  pronounced than in previous examples, as the recurrent connection is
+  responsible for the dynamics of the oscillation.  This result
+  indicates that the synaptic filtering model of SpiNNaker may also
+  warrant closer examination for accuracy.
+
+Figure 4:
+
+  The large difference between the two versions of this model for the
+  SpiNNaker backend indicates that node-to-ensemble and
+  ensemble-to-node connections introduce additional delays that are
+  not present on other backends.  This result is to be expected, as
+  nodes can execute arbitrary code and are therefore difficult to
+  simulate in real time with special purpose hardware.
+
+> Also, the whiskers in Figs. 1-4 seem to be only multiples of the box
+> sizes, so plotting them does not add any information - it may be
+> even misleading when not carefully reading the caption.
+
+Thank you for bringing up this point!
+Our description of the box plot was not quite correct
+in the initial submission. We have rewritten this description
+as follows:
+
+  The box shows the median and interquartile range, while the whiskers
+  extend to the farthest data point within 1.5 times the interquartile
+  range; outliers are shown above and below the whiskers.
+
+As noted in these captions, we have also now included the outliers.
+We were initially concerned that outliers would make the rest of the
+boxplot too small relative to the expanded axes caused by outliers.
+However, we now feel that including all of the data makes these
+boxplots more useful.
+
+> Some of the results in Fig. 7 are puzzling: For BG sequence*, the
+> run time for nengo and nengo_ocl is even higher without probes
+> (compared to Fig. 6), being well outside the 95% confidence
+> intervals. This should be explained.
+
+We did not notice the slowdown upon initial submission,
+so seeing this was puzzling to us as well.
+To investigate whether this effect was real,
+we first replicated it on two additional machines;
+the version without probes was significantly slower
+than the version with probes on all machines,
+as measured by non-overlapping
+bootstrapped 95% confidence intervals.
+Then, we investigated the internal structures of the two
+versions of networks, in terms of the step functions
+produced by them.
+The version with probes had 600 step functions;
+595 of these implemented the same equations
+as the networks without probes, while the
+remaining five functions implemented the probing.
+The simulator loop also indicated that
+the version without probes should have executed
+strictly fewer operations than the version with probes.
+We conclude that the reason for the speedup
+must have been somehow related to
+a lower level of abstraction than we investigated
+(e.g., the data was better organized in RAM
+in the version with probes).
+
+Very few networks in Nengo have zero probes,
+so there were some obvious opportunities to optimize
+the reference backend for the special case
+in which no probes exist. After implementing
+two such optimizations, we were able to consistently
+achieve identical performance with probes and without.
+However, it was not our intention to perform
+a detailed comparison of the affect of probes
+on runtimes, and we feel that including Figure 7
+(which only had a few sentences of text associated with it)
+was more distracting than illuminating.
+For these reasons, we have removed Figure 7 in this revision.
 
@@
 
-As already mentioned for the Introduction, it would make the
-Discussion section much more balanced if the limitations of the
-approach would be discussed as well, together with some outlook to
-potential improvements or complementary approaches.
+> As already mentioned for the Introduction, it would make the
+> Discussion section much more balanced if the limitations of the
+> approach would be discussed as well, together with some outlook to
+> potential improvements or complementary approaches.
 
-Minor:
+As previously mentioned, we added in a paragraph to the discussion
+on the primary weakness of the approach.
+This paragraph also includes a potential improvement:
+collecting power consumption information (lines 417-423).
 
-- typo in line 373: "We believe that THE these benchmarks..."
+> Minor:
+>
+> - typo in line 373: "We believe that THE these benchmarks..."
+
+Corrected, thank you!
 
@@
 
-Overall, the article presents an attractive idea for benchmarking
-neuromorphic systems. In my opinion its main weakness is the lack of
-embedding in the current literature. Apart from that, it is a nice
-contribution to the field, and the open source code is a good
-opportunity for other neuromorphic system operators for benchmarking
-their systems.
+> Overall, the article presents an attractive idea for benchmarking
+> neuromorphic systems. In my opinion its main weakness is the lack of
+> embedding in the current literature. Apart from that, it is a nice
+> contribution to the field, and the open source code is a good
+> opportunity for other neuromorphic system operators for benchmarking
+> their systems.
+>
+> Minor:
+>
+> - missing citation details for Stewart et al. 2010
 
-Minor:
-
-- missing citation details for Stewart et al. 2010
+Corrected, thank you! In correcting this, we noticed that
+Mundy et al., 2015 was also missing details,
+which have been filled in.

### 2015-09-13 paper/paper.tex
Edits in response to reviewer feedback

@@
 quickly becoming obsolete.
-We propose that the Nengo test suite
+However, benchmarks can spur progress
+as tool developers have an objective
+metric to maximize or minimize.
+
+Prior work benchmarking neural simulators
+and neuromorphic hardware has focused
+on low-level neural performance.
+For example, \citet{sharp2013}
+showed that SpiNNaker can simulate
+a recurrent network of leaky integrate-and-fire neurons
+with similar firing rate and inter-spike intervals
+as the NEST neural simulator,
+but around six times faster.
+\citet{stromatias2013} showed that
+SpiNNaker's power consumption varies
+between 15 and 37 Watts
+(0.5--0.8 Watts per chip)
+depending on the number of neurons
+being simulated.
+\citet{goodman2008brian} showed that
+Brian simulated a randomly connected
+network of 4000 leaky integrate-and-fire
+twice as fast as an equivalent Matlab implementation,
+but around three times as slow as
+a C implementation.
+In all of these cases,
+none of the networks
+elicited activity that could be
+directly related to experimentally recorded data
+on a behavioral task.
+
+In contrast,
+\citet{ehrlich2010} and \citet{bruderle2011}
+have presented a set of benchmarks that target
+the FACETS neuromorphic system
+through the PyNN Python package.
+These benchmarks include
+an attractor-based memory model,
+a model of self-sustained AI states,
+and a Synfire Chain,
+all of which are
+directly related to neuroscientific experiments.
+We aim to build on this line of research
+and provide an unbiased,
+efficient, and future-proof set
+of benchmarks that focuses
+on high-level functional performance
+using Nengo instead of PyNN.
+We have previously shown that Nengo
+is an order of magnitude faster than
+the software simulators that PyNN targets
+\citep{bekolay2013},
+and have recently implemented backends
+that target neuromorphic hardware.
+
+In this study,
+we propose that the Nengo test suite
 can serve as an unbiased, efficient, and future-proof
 set of benchmarks for neuromorphic systems.
-
 Nengo is a rigorously tested software package
@@
 to any backend that implements a certain set of requirements.
-The second is a ``fuzzy'' test suite that ensures
+The second is a functional test suite that ensures
 Nengo can be used to create models that solve cognitive tasks.
@@
 all of the random factors
-in the model deterministic.
-Aside from managing the random seed,
-the network is responsible for maintaining
+in the model deterministic,
+which is important for testing
+and debugging models,
+but is not used for benchmarking.
+The network is also responsible for maintaining
 a network-specific set of default parameters
@@
 and so on.
-When parts of the model are randomly sampled,
-the random factors should become deterministic
-when a network's seed is set.
 
@@
 
-\subsection{Fuzzy testing}
+\subsection{Functional testing}
 
@@
 Nengo's test suite defines several test fixtures
-to support fuzzy testing
-that collects and visualizes performance metrics
+to support collecting and visualizing performance metrics
 on multiple backends.
-
-\paragraph{\texttt{rng} \& \texttt{seed}}
-enable deterministic testing despite
-all of the random factors that affect a model.
-Test functions that generate random values
-(as inputs to a model, for example)
-generate those values using \texttt{rng},
-which is a random number generator
-with an interface identical to
-NumPy's random module.
-When a test function creates a network,
-it passes in \texttt{seed} to make
-the random components
-of the frontend-to-backend translation deterministic.
-Importantly, these random components
-are seeded by hashing a string uniquely
-identifying each test function,
-ensuring that tolerances must be set
-wide enough that changing the seed
-should only rarely result in test failures.
-The hash function is also seeded
-with a global integer,
-which is changed periodically to ensure
-that tests have good tolerances.
 
@@
 2~Hz, 1~Hz, 0~Hz, -1~Hz, and -2~Hz.
+Negative frequencies indicate oscillations
+in the reverse direction.\footnote{There is some evidence
+  that neural oscillators such as locomotive central pattern generators
+  accomplish forward and backward locomotion
+  with the same neural mechanism \citep{duysens1998}.
+  While this does not mean that all neural oscillators must
+  be able to operate in the reverse direction,
+  we believe that the capability to traverse
+  the limit cycle forward and backward is advantageous,
+  and in the current design requires no additional neural resources.}
 In total, the model is comprised of 600 LIF neurons.
@@
 
+We have used relatively small
+models run for short times in order
+to run many iterations on all backends.
+However, all of these models
+could be made significantly larger
+by increasing the number of neurons used
+(i.e., adjusting the \texttt{n\_neurons}
+parameter on ensembles),
+and increasing the dimensionality
+of the signals represented in the model.
+Additionally, existing tests
+of the semantic pointer architecture
+within Nengo use significantly more neurons
+than the models presented here,
+and could be adapted into benchmarks.
+
 \subsection{Backends tested}
@@
 
+Unlike software backends,
+considerable effort is taken
+to translate a Nengo model into
+something that can run on a SpiNNaker board.
+Fortunately, SpiNNaker can be reprogrammed
+as it is composed of a large collection
+of chips, each with 18 ARM processing cores.
+In particular, this allows SpiNNaker
+to take advantage of Nengo's
+encoding and decoding capabilities,
+greatly reducing the amount of RAM needed
+\citep{mundy2015}.
+The SpiNNaker backends accomplishes this
+by using decoded values to determine
+changes to the input currents to each neuron,
+rather than using purely
+spike-based transmission.
+However, a previous implementation
+of a Nengo SpiNNaker backend
+\citep{galluppi2012}
+used primarily spike-based communication,
+only making an explicit signal-to-spike
+encoding at the beginning
+of the network and an explicit
+spike-to-signal decoding
+at the end of a network.
+Neuromorphic hardware that
+can only communicate through spikes
+can be made to interact with Nengo
+through explicit encoding and decoding processes
+like the one used in \citealp{galluppi2012},
+or by using Nengo on the host machine
+to explicitly generate spike patterns
+that are communicated to the device.
+However, these methods may introduce
+additional noise in the simulation,
+resulting in inaccuracies.
+
 \subsection{Benchmarking environment}
@@
 used for benchmarking can be found in
-Table~\ref{Tab:02}.
+Table~\ref{Tab:01}.
 
@@
 \subsection{Compliance}
-
-Table~\ref{Tab:01} gives compliance results for
-all backends except the SpiNNaker backend,
-which is not yet set up to run the Nengo test suite.
-Of the four currently running unit tests,
-the OpenCL backend has the highest compliance
-(other than the reference backend).
+Table~\ref{Tab:02} gives compliance results for all backends.
+Compliance has been separated into tests
+that use a backend's default neuron type
+(leaky integrate-and-fire in all of the backends tested),
+and tests that are parameterized by neuron type.
+Of the non-reference backends,
+the OpenCL backend has the highest compliance.
 The distilled backend has lower compliance
@@
 of being simple but not necessarily feature-rich.
-The Brainstorm backend is the least compliant,
-but it is still an early experimental test bed;
-this is not necessarily indicative of the
+The Brainstorm backend fails one more test
+than the distilled background;
+however, it is still an early experimental test bed,
+and is not necessarily indicative of the
 final Brainstorm hardware backend being
 less compliant than other backends.
+Finally, the SpiNNaker backend
+passes the fewest tests.
+
+It should be noted that these test suites
+are being run on the distilled, Brainstorm,
+and SpiNNaker backends for the first time in this study.
+In other words, these results are the first objective
+interrogation of each backend's feature set.
+In many cases, tests failed by backends
+are tests of features recently added
+to Nengo, such as stochastic processes
+for injecting current noise.
+As such, we expect compliance on all backends
+to rise quickly as backend developers
+implement these new features.
+The OpenCL backend has
+significantly higher compliance in large part
+because it is developed by the same
+group that develops the reference backend.
+However, there are some notable features
+missing from some backends,
+such as learning through plasticity rules
+applied to neuron-to-neuron connections,
+and implementation differences,
+such as one timestep delays on connections
+with no synaptic filter,
+that may remain even when backends
+are brought up to date with
+the reference implementation.
+It is likely that tests will be rewritten
+in the future to allow some implementation differences
+if they do not affect simulation accuracy.
 
@@
 that each introduce noise.
+The Brainstorm and distilled backends
+have the least variability
+and the SpiNNaker backend has the most variability,
+though the median RSME is the same across all backends.
+One driver of these differences
+is in how each backend implement synaptic filtering.
+The reference and OpenCL backends,
+for example,
+implement arbitrary linear time-invariant filters,
+of which the lowpass filter used in this model
+is a specific example.
+The Brianstorm and distilled backends
+only support lowpass filters,
+and therefore implement it
+more accurately.
+Another reason for these differences
+is in how each backend handles
+ensembles operating near the edge
+of their representational range
+(i.e., the radius of the ensemble).
+The outlier with highest RMSE represents
+a model instance in which the static vector target
+was at the extreme of the representational range;
+the SpiNNaker backend's relatively high RMSE
+on this example indicates that it
+may not perform as well as other backends
+in this situation.
+However, accuracy could be improved
+by increasing the representational range,
+though doing so may necessitate an increase
+in the number of evaluation points generated
+when solving for decoding weights.
 
@@
 acceptable ranges for the two-dimensional product model.
+Again, the more generic synaptic filtering model
+used in the reference and OpenCL backends
+is the likely cause of increased variability
+on this model.
+It is also likely that performance at the extremes
+of the representational range
+is responsible for the SpiNNaker backend's
+reduced accuracy,
+though we have not investigated this in detail.
 
@@
 as compared to other backends.
+In this example, differences in synaptic filtering
+are more pronounced than in previous examples,
+as the recurrent connection is responsible
+for the dynamics of the oscillation.
+This result indicates that the synaptic filtering model
+of SpiNNaker may also warrant closer examination
+for accuracy.
 
@@
 is indistinguishable from the other backends.
+The large difference between the two versions
+of this model for the SpiNNaker backend
+indicates that node-to-ensemble and
+ensemble-to-node connections
+introduce additional delays that are
+not present on other backends.
+This result is to be expected,
+as nodes can execute arbitrary code
+and are therefore difficult
+to simulate in real time
+with special purpose hardware.
 
@@
 
-Interestingly, while removing passthrough nodes
-results in significantly slower run times
-for the reference backend,
-it speeds up the OpenCL and SpiNNaker backends slightly.
+While passthrough nodes were removed
+in the basal ganglia sequence model
+for improved accuracy,
+it is interesting to note that speed
+is also impacted in this version of the model.
+While the distilled and Brainstorm backends
+are unaffected,
+both the SpiNNaker and OpenCL backends run faster
+when passthrough nodes are removed.
 This result indicates that passthrough nodes
-add to the overhead incurred by
-SpiNNaker and OpenCL.
-Other backends also incur overhead,
-especially when data is recorded
-through probes.
-We investigated the possibility
-that the overhead involved in probes
-dominated the run time for some backends.
-However, we found that
-removing probes from these models
-made very little impact on
-the total time taken in a \texttt{run} call
-(see Figure~\ref{fig:07}).
+contribute to SpiNNaker's overhead.
+The reference backend, on the other hand,
+runs slower,
+indicating that the computational costs
+of the additional connections introduced
+when removing passthrough nodes
+are greater than the costs of
+the passthrough nodes.
 
@@
 or larger versions of all four of the models
-benchmarked here.
+benchmarked here in its 2.5 million neuron network.
 Additionally, in this study, we run these models
@@
 
+One inherent weakness of using Nengo
+as a standard platform for benchmarking
+neuromorphic systems is that new benchmarking
+capabilities may take a long time to
+be standardized and developed.
+If one wishes to add a new metric,
+such as power consumption
+(as was done in \citealp{stromatias2013}),
+we must first come to a consensus
+on a suitable interface to this information
+through Nengo.
+Once consensus is reached,
+it must be implemented and tested
+on all backends before
+benchmarks can be written using
+that quantity.
+Despite this limitation,
+we believe that it is possible to use
+Nengo to collect power consumption information,
+and plan to implement energy efficiency comparisons
+in future work.
+
 While we cannot claim that Nengo
@@
 than the reference backend.
-We believe that the these benchmarks
+We believe that these benchmarks
 can be easily expanded upon
@@
 which has not yet been publicly released
-(see Table~\ref{Tab:02}).
+(see Table~\ref{Tab:01}).
 All of the benchmarks presented here,
@@
 
-def test_cchannelchain(Simulator, analytics, plt, rng, seed):
+def test_cchannelchain(Simulator, analytics, plt):
     # Parameters that can be varied to investigate extreme cases
@@
 
-    with nengo.Network(seed=seed) as model:
+    with nengo.Network() as model:
         hypersphere = nengo.dists.UniformHypersphere()
-        value = hypersphere.sample(dims, 1, rng=rng).ravel()
+        value = hypersphere.sample(dims, 1).ravel()
         stim = nengo.Node(value)
@@
 
+\clearpage
+
 \section*{Figures}
@@
 \textbf{\refstepcounter{table}\label{Tab:01} Table \arabic{table}.}{
-  Compliance of four backends.}
-
-\processtable{ }
-{\begin{tabular}{lcc}\toprule
- Backend & Number of tests passed & Percentage of tests passed\\\midrule
- Reference (\texttt{nengo}) & 212 & 100\% \\
- OpenCL (\texttt{nengo\_ocl}) & 187 & 88.2\% \\
- Distilled (\texttt{nengo\_distilled}) & 129 & 60.8\% \\
- Brainstorm (\texttt{nengo\_brainstorm}) & 107 & 50.4\% \\\botrule
-\end{tabular}}{}
-\end{table}
-
-\begin{table}[!ht]
-\textbf{\refstepcounter{table}\label{Tab:02} Table \arabic{table}.}{
   Software versions used for benchmarking.
@@
  NumPy & \texttt{numpy} & 1.8.1 \\\botrule
+\end{tabular}}{}
+\end{table}
+
+\begin{table}[!ht]
+\textbf{\refstepcounter{table}\label{Tab:02} Table \arabic{table}.}{
+  Compliance of the five backends. Compliance is the number of functional
+  tests passed by a particular backend. We have divided these tests into
+  tests parameterized by neuron type, and those not parameterized.
+  Non-parameterized tests are either designed to work with only
+  one neuron type, or use leaky integrate-and-fire (LIF) neurons,
+  which are implemented on all backends. For parameterized tests,
+  we have separated the compliance for those tests using LIF neurons,
+  which all backends implement, and for any additional neuron types
+  implemented. Since there are 31 parameterized tests, the maximum
+  compliance is 31 times the number of neuron types implemented.
+  The reference backend implements three additional neuron types,
+  while OpenCL, Distilled, and Brainstorm implement one additional neuron type,
+  and SpiNNaker only implements LIF neurons.}
+
+\processtable{ }
+{\begin{tabular}{lccc}\toprule
+ Backend & Non-parameterized tests passed & LIF tests passed & Other tests passed \\ \midrule
+ Reference (\texttt{nengo}) & 165 (100\%) & 31 (100\%) & 93 \\
+ OpenCL (\texttt{nengo\_ocl}) & 147 (89.0\%) & 29 (93.5\%) & 29 \\
+ Distilled (\texttt{nengo\_distilled}) & 95 (57.6\%) & 15 (48.4\%) & 15 \\
+ Brainstorm (\texttt{nengo\_brainstorm}) & 94 (57.0\%) & 15 (48.4\%) & 15 \\
+ SpiNNaker (\texttt{nengo\_spinnaker}) & 88 (53.3\%) & 7 (22.6\%) & 0 \\\botrule
 \end{tabular}}{}
@@
          500 millisecond simulation. The box shows the median and
-         interquartile range, while the whiskers extend to 1.5 times the
-         interquartile range; outliers are not shown.}
+         interquartile range, while the whiskers extend to the farthest
+         data point within 1.5 times the interquartile range;
+         outliers are shown above and below the whiskers.}
 \end{figure}
@@
          correct initial state). The box shows the median and
-         interquartile range, while the whiskers extend to 1.5 times the
-         interquartile range; outliers are not shown.}
+         interquartile range, while the whiskers extend to the farthest
+         data point within 1.5 times the interquartile range;
+         outliers are shown above and below the whiskers.}
 \end{figure}
@@
          all frequencies. The box shows the median and
-         interquartile range, while the whiskers extend to 1.5 times the
-         interquartile range; outliers are not shown.}
+         interquartile range, while the whiskers extend to the farthest
+         data point within 1.5 times the interquartile range;
+         outliers are shown above and below the whiskers.}
 \end{figure}
@@
          on the transition time. The box shows the median and
-         interquartile range, while the whiskers extend to 1.5 times the
-         interquartile range; outliers are not shown.
+         interquartile range, while the whiskers extend to the farthest
+         data point within 1.5 times the interquartile range;
+         outliers are shown above and below the whiskers.
          (C) The aggregated accuracy results for 50 trials of
@@
 
-\begin{figure}[!ht]
-\begin{center}
-  \includegraphics[width=85mm]{fig7}
-\end{center}
-\textbf{\refstepcounter{figure}\label{fig:07} Figure \arabic{figure}.}
-       {Run time for each model with probes removed on each backend.
-         Each bar represents the mean run time across 100 instances
-         of each model;
-         error bars are 95\% confidence intervals.
-         Run time is measured relative to real time;
-         e.g., a value of two indicates that the model ran twice as slow
-         as real time.
-         BG Sequence * refers to the basal ganglia sequence model
-         in which passthrough nodes have been removed.}
-\end{figure}
-
 \end{document}

### 2015-09-13 fnme/plots.py

@@ -128,7 +128,7 @@ def get_data(task, key, separate_cols=True, probes=True):
 def plot_summary(task, key, probes=True, figsize=None, rotation=0):
     setup(figsize=figsize)
     data = get_data(task, key, probes=probes)
-    sns.boxplot(data=data, showfliers=False)
+    sns.boxplot(data=data)
     plt.gca().set_xticklabels(data.columns, rotation=rotation)
 
 

### 2015-09-14 paper/rebuttals.txt
Incorporate feedback from Terry

@@
 this was because we have used oscillators of these frequencies
-in previous model. In line 219 we note that
+in previous models. In line 219 we note that
 "We test each model with parameters typically used
@@
 
+Briefly, we do not have a satisfying explanation
+of why the reference backend shows higher variability than
+the Brainstorm and distilled backends.
+We discuss this briefly in the additional details below
+and have added a sentence to the discussion
+indicating that we will examine this result in the future
+(lines 398-399: "We also plan to investigate
+why the reference and OpenCL backends
+have higher variability than other backends on
+the simple feedforward models.")
+
 We are still in the progress of investigating the deviations
@@
   RSME is the same across all backends.  One driver of these
-  differences is in how each backend implement synaptic filtering.
-  The reference and OpenCL backends, for example, implement arbitrary
-  linear time-invariant filters, of which the lowpass filter used in
-  this model is a specific example.  The Brianstorm and distilled
-  backends only support lowpass filters, and therefore implement it
-  more accurately.  Another reason for these differences is in how
-  each backend handles ensembles operating near the edge of their
-  representational range (i.e., the radius of the ensemble).  The
-  outlier with highest RMSE represents a model instance in which the
-  static vector target was at the extreme of the representational
-  range; the SpiNNaker backend's relatively high RMSE on this example
-  indicates that it may not perform as well as other backends in this
-  situation.  However, accuracy could be improved by increasing the
-  representational range, though doing so may necessitate an increase
-  in the number of evaluation points generated when solving for
-  decoding weights.
+  differences is in how each backend handles ensembles operating near
+  the edge of their representational range (i.e., the radius of the
+  ensemble).  The outlier with highest RMSE represents a model
+  instance in which the static vector target was at the extreme of the
+  representational range; the SpiNNaker backend's relatively high RMSE
+  on this example indicates that it may not perform as well as other
+  backends in this situation.  The SpiNNaker backend uses signed fixed
+  point numbers with 16 digits before the decimal point, and 15 digits
+  after the decimal point; accuracy could be improved by optimizing
+  the backend's internal calculations to use as many digits as
+  possible.  For all backends, accuracy could be improved by
+  increasing the representational range and increasing the number of
+  evaluation points generated when solving for decoding weights.
 
@@
 
-  Again, the more generic synaptic filtering model used in the
-  reference and OpenCL backends is the likely cause of increased
-  variability on this model.  It is also likely that performance at
-  the extremes of the representational range is responsible for the
-  SpiNNaker backend's reduced accuracy, though we have not
-  investigated this in detail.
+  Again, it is likely that performance at the extremes of the
+  representational range is responsible for the SpiNNaker backend's
+  reduced accuracy, though we have not investigated this in detail.
+  This benchmark also suggests that the reference and OpenCL backends
+  have more variability than other backends, particularly the
+  Brainstorm and distilled backends.
 
@@
 
-  In this example, differences in synaptic filtering are more
-  pronounced than in previous examples, as the recurrent connection is
-  responsible for the dynamics of the oscillation.  This result
-  indicates that the synaptic filtering model of SpiNNaker may also
-  warrant closer examination for accuracy.
+  In this example, differences in how each backend implements synaptic
+  filtering are more pronounced than in previous examples, as the
+  recurrent connection is responsible for the dynamics of the
+  oscillation.  Relatively large variability in the reference, OpenCL
+  and SpiNNaker backends suggests that their synaptic filtering
+  implementations should be examined for potential accuracy
+  improvements.
 

### 2015-09-14 paper/paper.tex
Incorporate feedback from Terry

@@
 One driver of these differences
-is in how each backend implement synaptic filtering.
-The reference and OpenCL backends,
-for example,
-implement arbitrary linear time-invariant filters,
-of which the lowpass filter used in this model
-is a specific example.
-The Brianstorm and distilled backends
-only support lowpass filters,
-and therefore implement it
-more accurately.
-Another reason for these differences
 is in how each backend handles
@@
 in this situation.
-However, accuracy could be improved
-by increasing the representational range,
-though doing so may necessitate an increase
-in the number of evaluation points generated
+The SpiNNaker backend uses
+signed fixed point numbers
+with 16 digits before the decimal point,
+and 15 digits after the decimal point;
+accuracy could be improved
+by optimizing the backend's
+internal calculations to use as
+many digits as possible.
+For all backends, accuracy could be improved
+by increasing the representational range
+and increasing the number of evaluation points generated
 when solving for decoding weights.
@@
 acceptable ranges for the two-dimensional product model.
-Again, the more generic synaptic filtering model
-used in the reference and OpenCL backends
-is the likely cause of increased variability
-on this model.
-It is also likely that performance at the extremes
+Again, it is likely that performance at the extremes
 of the representational range
@@
 though we have not investigated this in detail.
+This benchmark also suggests that
+the reference and OpenCL backends
+have more variability than other backends,
+particularly the Brainstorm and distilled backends.
 
@@
 as compared to other backends.
-In this example, differences in synaptic filtering
+In this example, differences in how each backend
+implements synaptic filtering
 are more pronounced than in previous examples,
@@
 for the dynamics of the oscillation.
-This result indicates that the synaptic filtering model
-of SpiNNaker may also warrant closer examination
-for accuracy.
+Relatively large variability in the
+reference, OpenCL and SpiNNaker backends
+suggests that their synaptic filtering implementations
+should be examined for potential accuracy improvements.
 
@@
 may be responsible.
+We also plan to investigate
+why the reference and OpenCL backends
+have higher variability than other backends on
+the simple feedforward models.
 

### 2015-09-14 paper/rebuttals.txt
Incorporate feedback from Chris

@@
   connected network of 4000 leaky integrate-and-fire twice as fast as
-  an equivalent Matlab implementation, but around three times as slow
-  as a C implementation.  In all of these cases, none of the networks
+  an equivalent Matlab implementation, but around three times slower
+  than a C implementation. In all of these cases, none of the networks
   elicited activity that could be directly related to experimentally
@@
 
+Reviewer 1 noticed this effect as well.
+Our reply was as follows:
+
 We did not notice the slowdown upon initial submission,

### 2015-09-14 paper/paper.tex
Incorporate feedback from Chris

@@
 twice as fast as an equivalent Matlab implementation,
-but around three times as slow as
+but around three times slower than
 a C implementation.
@@
 spike-based transmission.
-However, a previous implementation
-of a Nengo SpiNNaker backend
-\citep{galluppi2012}
-used primarily spike-based communication,
-only making an explicit signal-to-spike
-encoding at the beginning
-of the network and an explicit
-spike-to-signal decoding
-at the end of a network.
-Neuromorphic hardware that
+However, neuromorphic hardware that
 can only communicate through spikes
@@
 through explicit encoding and decoding processes
-like the one used in \citealp{galluppi2012},
+on the chip, as was done in \citealp{galluppi2012},
 or by using Nengo on the host machine
 to explicitly generate spike patterns
-that are communicated to the device.
+that are communicated to the device,
+as was done in \citealp{choudhary2012}.
 However, these methods may introduce

### 2015-09-14 paper/rebuttals.txt
Final edits before submission

@@
 slow and error-prone. The tests creates a large number of
-small models and runs them for small amounts of time;
+small models and run them for small amounts of time;
 this results in the SpiNNaker boards' memory filling up with
-improperly freed resources. So, the real answer is more a
-time management one; we decided that getting the unit tests
+improperly freed resources. The real answer is a matter of
+time management; we decided that getting the unit tests
 running would take too much time for this paper.
@@
 put in the time to run the test suite with the SpiNNaker
-backend. Table 1 (now Table 2) now also gives results
+backend. Table 1 (Table 2 in the revised version) now gives results
 for the SpiNNaker backend, and the text has been updated
@@
 Good point. We used 'significant' colloquially here and
-have reworded this paragraph; it now reads:
+have therefore reworded the paragraph; it now reads:
 
@@
 However, it was not our intention to perform
-a detailed comparison of the affect of probes
+a detailed comparison of the effect of probes
 on runtimes, and we feel that including Figure 7
@@
 
-In terms of why the range -2 to 2 was chosen,
-this was because we have used oscillators of these frequencies
+We chose the range of -2 to 2
+because we have used oscillators of these frequencies
 in previous models. In line 219 we note that
@@
 Additionally, a paragraph explaining common failure cases
-is included in the main text in lines 311-321. It reads:
+is included in the main text in lines 309-319. It reads:
 
@@
   developers implement these new features.  The OpenCL backend has
-  significantly higher compliance in large part because it is
-  developed by the same group that develops the reference backend.
-  However, there are some notable features missing from some backends,
-  such as learning through plasticity rules applied to
-  neuron-to-neuron connections, and implementation differences, such
-  as one timestep delays on connections with no synaptic filter, that
-  may remain even when backends are brought up to date with the
-  reference implementation.  It is likely that tests will be rewritten
-  in the future to allow some implementation differences if they do
-  not affect simulation accuracy.
+  higher compliance in large part because it is developed by the same
+  group that develops the reference backend.  However, there are some
+  notable features missing from some backends, such as learning
+  through plasticity rules applied to neuron-to-neuron connections,
+  and implementation differences, such as one timestep delays on
+  connections with no synaptic filter, that may remain even when
+  backends are brought up to date with the reference implementation.
+  It is likely that tests will be rewritten in the future to allow
+  some implementation differences if they do not affect simulation
+  accuracy.
 
@@
 to discuss this issue, and to register our desire to collect
-efficiency information in future work. Lines 417-423 now read:
+efficiency information in future work. Lines 416-422 now read:
 
@@
   benchmarking neuromorphic systems is that new benchmarking
-  capabilities may take a long time to be standardized and developed.
-  If one wishes to add a new metric, such as power consumption, we
-  must first come to a consensus on a suitable interface to this
-  information through Nengo.  Once consensus is reached, it must be
-  implemented and tested on all backends before benchmarks can be
-  written using that quantity.  Despite this limitation, we believe
-  that it is possible to use Nengo to collect power consumption
-  information, and plan to implement efficiency comparisons in future
-  work.
+  capabilities may take a long time to be standardized and
+  developed. If one wishes to add a new metric, such as power
+  consumption (as was done in Stromatias et al., 2013), we must first
+  come to a consensus on a suitable interface to this information
+  through Nengo. Once consensus is reached, it must be implemented and
+  tested on all backends before benchmarks can be written using that
+  quantity. Despite this limitation, we believe that it is possible to
+  use Nengo to collect power consumption information, and plan to
+  implement energy efficiency comparisons in future work.
 
@@
 benchmarking SpiNNaker, FACETS, and Brian,
-and situating this study in that context in lines 19-35.
+and situating this study in that context on lines 19-35.
 They read:
@@
   Prior work benchmarking neural simulators and neuromorphic hardware
-  has focused on low-level neural performance.  For example,
-  \citet{sharp2013} showed that SpiNNaker can simulate a recurrent
-  network of leaky integrate-and-fire neurons with similar firing rate
-  and inter-spike intervals as the NEST neural simulator, but around
-  six times faster.  \citet{stromatias2013} showed that SpiNNaker's
+  has focused on low-level neural performance.  For example, Sharp and
+  Furber (2013) showed that SpiNNaker can simulate a recurrent network
+  of leaky integrate-and-fire neurons with similar firing rate and
+  inter-spike intervals as the NEST neural simulator, but around six
+  times faster.  Stromatias et al. (2013) showed that SpiNNaker's
   power consumption varies between 15 and 37 Watts (0.5--0.8 Watts per
-  chip) depending on the number of neurons being simulated.
-  \citet{goodman2008brian} showed that Brian simulated a randomly
-  connected network of 4000 leaky integrate-and-fire twice as fast as
-  an equivalent Matlab implementation, but around three times slower
-  than a C implementation. In all of these cases, none of the networks
+  chip) depending on the number of neurons being simulated.  Goodman
+  and Brette (2008) showed that Brian simulated a randomly connected
+  network of 4000 leaky integrate-and-fire twice as fast as an
+  equivalent Matlab implementation, but around three times slower than
+  a C implementation. In all of these cases, none of the networks
   elicited activity that could be directly related to experimentally
@@
 
-  In contrast, \citet{ehrlich2010} and \citet{bruderle2011} have
+  In contrast, Ehrlich et al. (2010) and Bruderle et al. (2011) have
   presented a set of benchmarks that target the FACETS neuromorphic
@@
   order of magnitude faster than the simulators that PyNN targets
-  \citep{bekolay2013}, and have recently implemented backends that
+  (Bekolay et al., 2013), and have recently implemented backends that
   target neuromorphic hardware.
@@
 would mean figuring out a standard for this and then implementing
-it across all backends) in lines 417-423. It reads:
+it across all backends) on lines 416-422. It reads:
 
@@
   benchmarking neuromorphic systems is that new benchmarking
-  capabilities may take a long time to be standardized and developed.
-  If one wishes to add a new metric, such as power consumption (as was
-  done in \citealp{stromatias2013}), we must first come to a consensus
-  on a suitable interface to this information through Nengo.  Once
-  consensus is reached, it must be implemented and tested on all
-  backends before benchmarks can be written using that quantity.
-  Despite this limitation, we believe that it is possible to use Nengo
-  to collect power consumption information, and plan to implement
-  energy efficiency comparisons in future work.
+  capabilities may take a long time to be standardized and
+  developed. If one wishes to add a new metric, such as power
+  consumption (as was done in Stromatias et al., 2013), we must first
+  come to a consensus on a suitable interface to this information
+  through Nengo. Once consensus is reached, it must be implemented and
+  tested on all backends before benchmarks can be written using that
+  quantity. Despite this limitation, we believe that it is possible to
+  use Nengo to collect power consumption information, and plan to
+  implement energy efficiency comparisons in future work.
 
@@
 account of how SpiNNaker uses decoded values to change the
-input currents to individual neurons, and a prior publication
-(Galluppi et al., 2012, which is now cited) describes a process
+input currents to individual neurons, and two prior publications
+(Galluppi et al., 2012 and Choudhary et al., 2012) describe processes
 to implement Nengo with primarily spike-based communication
-on SpiNNaker. We have added a paragraph to the Methods section
+on SpiNNaker and Neurogrid, respectively.
+We have added a paragraph to the Methods section
 with brief descriptions of how SpiNNaker handles currents,
 and how other neuromorphic hardware can be made to handle
-currents from Nengo as well in lines 285-297.
+currents from Nengo as well in lines 285-295.
 The paragraph reads:
@@
   Unlike software backends, considerable effort is taken to translate
-  a Nengo model into something that can run on a SpiNNaker board.
-  Fortunately, SpiNNaker can be reprogrammed as it is composed of a
-  large collection of chips, each with 18 ARM processing cores.  In
-  particular, this allows SpiNNaker to take advantage of Nengo's
+  a Nengo model into something that can run on a SpiNNaker
+  board. Fortunately, SpiNNaker can be reprogrammed as it is composed
+  of a large collection of chips, each with 18 ARM processing
+  cores. Notably, this allows SpiNNaker to take advantage of Nengo’s
   encoding and decoding capabilities, greatly reducing the amount of
-  RAM needed \citep{mundy2015}.  The SpiNNaker backends accomplishes
+  RAM needed (Mundy et al., 2015). The SpiNNaker backend accomplishes
   this by using decoded values to determine changes to the input
-  currents to each neuron, rather than using purely spike-based
-  transmission.  However, a previous implementation of a Nengo
-  SpiNNaker backend \citep{galluppi2012} used primarily spike-based
-  communication, only making an explicit signal-to-spike encoding at
-  the beginning of the network and an explicit spike-to-signal
-  decoding at the end of a network.  Neuromorphic hardware that can
-  only communicate through spikes can be made to interact with Nengo
-  through explicit encoding and decoding processes like the one used
-  in \citealp{galluppi2012}, or by using Nengo on the host machine to
-  explicitly generate spike patterns that are communicated to the
-  device.  However, these methods may introduce additional noise in
-  the simulation, resulting in inaccuracies.
+  currents of each neuron, rather than using purely spike-based
+  transmission. However, neuromorphic hardware that can only
+  communicate through spikes can be made to interact with Nengo
+  through explicit encoding and decoding processes on the chip, as was
+  done in Galluppi et al. (2012), or by using Nengo on the host
+  machine to explicitly generate spike patterns that are communicated
+  to the device, as was done in Choudhary et al. (2012). However,
+  these methods may introduce additional noise in the simulation,
+  resulting in inaccuracies.
 
@@
 fixtures. We have kept one reference in the Background section discussing
-the frontend interface, but have  reworded that it slightly;
-it now reads:
+the frontend interface, but have reworded it slightly; it now reads:
 
@@
 
-We have added an explicit mention of the size of Spaun on lines 401-402
+We have added an explicit mention of the size of Spaun on lines 400-401
 (since Spaun is built with Nengo and shows that it is possible
 to generate large networks). We have also added a short paragraph
-to the Test models subsection discussing larger models;
+to the Test Models subsection discussing larger models;
 see lines 255-259 which read:
@@
 
-Briefly, we do not have a satisfying explanation
-of why the reference backend shows higher variability than
+Unfortunately, we do not have a satisfying explanation
+for why the reference backend shows higher variability than
 the Brainstorm and distilled backends.
@@
 indicating that we will examine this result in the future
-(lines 398-399: "We also plan to investigate
+(lines 395-397: "We also plan to investigate
 why the reference and OpenCL backends
@@
 the SpiNNaker group to improve accuracy on these examples.
-The 1ms time step is not the issue here, however,
-as all of the backends tested use a 1ms time step.
+The 1 ms time step is not the issue here, however,
+as all of the backends tested use a 1 ms time step.
 
@@
   This benchmark also suggests that the reference and OpenCL backends
-  have more variability than other backends, particularly the
-  Brainstorm and distilled backends.
+  have more variability than the Brainstorm and distilled backends.
 
@@
 
-As noted in these captions, we have also now included the outliers.
+As noted in the revised captions, we have also now included the outliers.
 We were initially concerned that outliers would make the rest of the
@@
 This paragraph also includes a potential improvement:
-collecting power consumption information (lines 417-423).
+collecting power consumption information (lines 416-422).
 

### 2015-09-14 paper/paper.tex
Final edits before submission

@@
 a recurrent network of leaky integrate-and-fire neurons
-with similar firing rate and inter-spike intervals
+with similar firing rates and inter-spike intervals
 as the NEST neural simulator,
@@
 that accepts a network.
-Every test uses this test fixture rather than
+Every functional test uses this test fixture rather than
 an actual class so that
@@
 of chips, each with 18 ARM processing cores.
-In particular, this allows SpiNNaker
+Notably, this allows SpiNNaker
 to take advantage of Nengo's
@@
 \citep{mundy2015}.
-The SpiNNaker backends accomplishes this
+The SpiNNaker backend accomplishes this
 by using decoded values to determine
-changes to the input currents to each neuron,
+changes to the input currents of each neuron,
 rather than using purely
@@
 through explicit encoding and decoding processes
-on the chip, as was done in \citealp{galluppi2012},
+on the chip, as was done in \citet{galluppi2012},
 or by using Nengo on the host machine
@@
 that are communicated to the device,
-as was done in \citealp{choudhary2012}.
+as was done in \citet{choudhary2012}.
 However, these methods may introduce
@@
 The OpenCL backend has
-significantly higher compliance in large part
+higher compliance in large part
 because it is developed by the same
@@
 the reference and OpenCL backends
-have more variability than other backends,
-particularly the Brainstorm and distilled backends.
+have more variability than the Brainstorm and distilled backends.
 
@@
 the same as the distilled and Brainstorm backends,
-but there are a high proportion of model instances
-with less accuracy than the median,
-as compared to other backends.
+but model instances with less accuracy than the median
+perform poorly compared to other backends.
 In this example, differences in how each backend
@@
 available to us.
+Finally, we thank our two reviewers for
+their helpful feedback and recommendations.
 

### 2015-09-14 paper/rebuttals.txt
Minor rebuttal changes noticed in submission

@@
 
+Thank you for your feedback and helpful suggestions!
+This is definitely just an initial step,
+and we hope that we will be able to collect benchmark models
+from many different researchers.
+
 Reviewer 2
@@
 This is an excellent point that we really should have addressed
-in the initial submission. The paper that we cited in the section
+in the initial submission. The paper that we cited in section
 on the SpiNNaker backend (Mundy et al., 2015) gives a detailed
@@
   could be made significantly larger by increasing the number of
-  neurons used (i.e., adjusting the \texttt{n\_neurons} parameter on
-  ensembles), and increasing the dimensionality of the signals
-  represented in the model.  Additionally, existing tests of the
-  semantic pointer architecture within Nengo use significantly more
-  neurons than the models presented here, and could be adapted into
-  benchmarks.
+  neurons used (i.e., adjusting the n_neurons parameter on ensembles),
+  and increasing the dimensionality of the signals represented in the
+  model.  Additionally, existing tests of the semantic pointer
+  architecture within Nengo use significantly more neurons than the
+  models presented here, and could be adapted into benchmarks.
 
@@
 which have been filled in.
+
+Also thank you for all of your feedback!
+We feel that the manuscript is now much stronger
+thanks to the additions in response to your feedback.

### 2015-11-04 fnme/plots.py
Actually, use big vertical figures.

@@ -24,7 +24,7 @@ inkscape = "inkscape"
 # onecolumn = 3.34646  # from initial submission
 onecolumn = 4.685044  # after author proof
 twocolumn = 7.08661  # never used
-horizontal = True
+horizontal = False
 
 
 class RectElement(sg.FigureElement):

### 2015-11-04 paper/paper.tex
Make typographic corrections from typesetter

@@
 in under 20~lines of code
-can be seen in Appendix~A.
+can be seen in the Appendix.
 
@@
 are used in test scripts
-can be seen in Appendix~A.
+can be seen in the Appendix.
 
@@
 with the \texttt{analytics} fixture.
-See Appendix~A for a
+See the Appendix for a
 concrete example of using the
@@
 
-\paragraph{Compliance}
-is the number of tests that a particular backend
+\subsubsection{Compliance}
+
+Compliance is the number of tests that a particular backend
 passes successfully, relative to the reference
@@
 
-\paragraph{Accuracy}
-measures how well a particular backend
+\subsubsection{Accuracy}
+
+Accuracy measures how well a particular backend
 implements a desired model.
@@
 
-\paragraph{Speed}
-measures the amount of time it takes
+\subsubsection{Speed}
+
+Speed measures the amount of time it takes
 for a backend to run a model.
@@
 in order to benchmark a wide variety of cases
-(see Appendix~A for an example).
+(see the Appendix for an example).
 We test each model with parameters
@@
 
-\paragraph{1. Communication channel chain.}
+\subsubsection{Communication channel chain.}
+
 In this model,
@@
 
-\paragraph{2. Two-dimensional product.}
+\subsubsection{Two-dimensional product.}
+
 In this model,
@@
 
-\paragraph{3. Controlled oscillator.}
+\subsubsection{Controlled oscillator.}
+
 In this model,
@@
 
-\paragraph{4. Basal ganglia sequence.}
+\subsubsection{Basal ganglia sequence.}
+
 In this model, brain structures
@@
 
-\paragraph{1. Reference (\texttt{nengo}).}
+\subsubsection{Reference (\texttt{nengo}).}
+
 The reference backend is designed to run quickly
@@
 
-\paragraph{2. Distilled (\texttt{nengo\_distilled}).}
+\subsubsection{Distilled (\texttt{nengo\_distilled}).}
+
 The distilled backend is intended as a teaching tool,
@@
 
-\paragraph{3. OpenCL (\texttt{nengo\_ocl}).}
+\subsubsection{OpenCL (\texttt{nengo\_ocl}).}
+
 The OpenCL backend uses the Open Computing Language
@@
 
-\paragraph{4. Brainstorm software (\texttt{nengo\_brainstorm}).}
+\subsubsection{Brainstorm software (\texttt{nengo\_brainstorm}).}
+
 The Brainstorm backend is a software implementation
@@
 
-\paragraph{5. SpiNNaker hardware (\texttt{nengo\_spinnaker}).}
+\subsubsection{SpiNNaker hardware (\texttt{nengo\_spinnaker}).}
+
 The SpiNNaker backend \citep{mundy2015}
@@
 
-\section*{Appendix A: Chained Communication Channel model}
+\section*{Appendix: Chained Communication Channel model}
 
@@
          relative to real time; e.g., a value of two indicates that
-         the calling \texttt{run} for a number of seconds takes
+         calling \texttt{run} for a number of seconds takes
          the model two times that number of real seconds to complete the

### 2015-11-04 paper/rebuttals.txt
Removed references to private backend

@@
   model for improved accuracy, it is interesting to note that speed is
-  also impacted in this version of the model.  While the distilled and
-  Brainstorm backends are unaffected, both the SpiNNaker and OpenCL
+  also impacted in this version of the model.  While the distilled
+  backend is unaffected, both the SpiNNaker and OpenCL
   backends run faster when passthrough nodes are removed.  This result
@@
   implemented.  The reference backend implements three additional
-  neuron types, while OpenCL, Distilled, and Brainstorm implement one
+  neuron types, while OpenCL, and Distilled, implement one
   additional neuron type, and SpiNNaker only implements LIF neurons.
@@
   It should be noted that these test suites are being run on the
-  distilled, Brainstorm, and SpiNNaker backends for the first time in
+  distilled and SpiNNaker backends for the first time in
   this study.  In other words, these results are the first objective
@@
 > referenced and approximated, or the implementation could provide its
-> own statistics for specialized hardware. Perhaps the Brainstorm
-> backend’s main advantage is in power efficiency, and there should be
-> resulting statistics that can show that. Regardless of
+> own statistics for specialized hardware. Regardless of
 > implementation, the authors should at least mention that efficiency
@@
 > particular, in Figs. 1 and 2, why does the Nengo reference backend
-> show a significantly higher variability than the Brainstorm and
-> distilled backends? In Figs. 3 and 4, where do the deviations in the
+> show a significantly higher variability than the
+> distilled backend? In Figs. 3 and 4, where do the deviations in the
 > SpiNNaker backend come from (my first guess would be the employed
@@
 for why the reference backend shows higher variability than
-the Brainstorm and distilled backends.
+the distilled backend.
 We discuss this briefly in the additional details below
@@
 
-  The Brainstorm and distilled backends have the least variability and
+  The distilled backend has the least variability and
   the SpiNNaker backend has the most variability, though the median
@@
   This benchmark also suggests that the reference and OpenCL backends
-  have more variability than the Brainstorm and distilled backends.
+  have more variability than the distilled backend.
 

### 2015-11-04 fnme/benchmarks.py

@@ -1,8 +1,5 @@
 """A set of accuracy benchmarks.
 
-These mostly come from a set of benchmarks implemented for the
-nengo_brainstorms backend, adapted to be run using Nengo test suite.
-
 Contributors:
   - Terry Stewart (CNRG lab)
   - Trevor Bekolay (CNRG lab)

### 2015-11-04 fnme/conftest.py

@@ -7,7 +7,7 @@ import pytest
 
 import nengo
 from nengo.tests.conftest import *
-from nengo.utils.testing import Timer
+from nengo.utils.stdlib import Timer
 
 
 if nengo.__version__ == '2.0.1':

### 2015-11-04 make.py

@@ -51,7 +51,7 @@ def task_paper():
     def forsurecompile(fname, bibtex=True):
         pdf = CmdAction('pdflatex -interaction=nonstopmode %s.tex' % fname,
                         cwd=d)
-        bib = CmdAction('bibtex %s' % fname, cwd=d)
+        bib = CmdAction('bibtex paper', cwd=d)
         pdf_file = os.path.join(d, '%s.pdf' % fname)
         tex_file = os.path.join(d, '%s.tex' % fname)
         bib_file = os.path.join(d, '%s.bib' % fname)
@@ -60,6 +60,7 @@ def task_paper():
                 'actions': [pdf, bib, pdf, pdf] if bibtex else [pdf, pdf],
                 'targets': [pdf_file]}
     yield forsurecompile('paper')
+    yield forsurecompile('changes', bibtex=False)
 
 
 def task_compliance():
@@ -76,8 +77,6 @@ def task_compliance():
                     os.path.join(os.pardir, 'nengo_ocl'))
     yield run_tests('nengo_distilled', 'nengo_distilled/tests/test_nengo.py',
                     os.path.join(os.pardir, 'nengo_distilled'))
-    yield run_tests('nengo_brainstorm', 'nengo_brainstorm/tests/test_nengo.py',
-                    os.path.join(os.pardir, 'nef-chip-hardware'))
 
 
 def task_benchmarks():
@@ -85,7 +84,6 @@ def task_benchmarks():
     sims = [sim for sim in ('nengo',
                             'nengo_ocl',
                             'nengo_distilled',
-                            'nengo_brainstorm',
                             'nengo_spinnaker')
             if pkgutil.find_loader(sim)]
 
